---
title: 'Ecopath with Ecosim Simulation'
date: 'Updated on July 1, 2022'
output:
  html_document: 
    code_folding: hide
  word_document: default
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Simulation scenarios {.tabset}

Environmental drivers have been incorporated through either forcing function (producer) or egg production function. When applying forcing function, environmental drivers have been linked with phytoplankton. When applying egg production function, only AMO without lag and with lag of one year have been linked with menhaden-like species.

### Environmental drivers

- AMO0: Atlantic Multidecadal Oscillation without lag
- AMO1: Atlantic Multidecadal Oscillation with lag of 1 year
- PCP: precipitation (average value from VA, MD, CT, RI, and MA)
- PDSI: Palmer drought severity index (average value from VA, MD, CT, RI, and MA)
- SPLINE11: Primary producer spline 11
- SPLINE33: Primary producer spline 33
- SST: Kaplan sea surface temperature

### Cases

- case 0: base case 
- case 1: PCP 
- case 2: PCP+AMO0
- case 3: PCP+AMO1
- case 4: PDSI
- case 5: PDSI+AMO0
- case 6: PDSI+AMO1
- case 7: SPLINE11
- case 9: SPLINE11+AMO0
- case 10: SPLINE11+AMO1
- case 11: SPLINE33
- case 12: SPLINE33+AMO0
- case 13: SPLINE33+AMO1
- case 14: SST
- case 15: SST+AMO0
- case 16: SST+AMO1

## {-}

```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
devtools::load_all()

# Install required R packages -------------------------------------
required_pkg <- c(
  "here", "ggplot2", "ggcorrplot", "RColorBrewer",
  "tidyverse", "reshape2"
)

pkg_to_install <- required_pkg[!(required_pkg %in%
                                   installed.packages()[, "Package"])]
if (length(pkg_to_install)) install.packages(pkg_to_install)

lapply(required_pkg, library, character.only = TRUE)

```

## Biomass over time {.tabset}
```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}

ewe_year <- 1985:2017
# EwE functional groups
functional_groups = c(
  "StripedBass0",
  "StripedBass2_5",
  "StripedBass6",
  "AtlanticMenhaden0",
  "AtlanticMenhaden1",
  "AtlanticMenhaden2",
  "AtlanticMenhaden3",
  "AtlanticMenhaden4",
  "AtlanticMenhaden5",
  "AtlanticMenhaden6",
  "SpinyDogfish",
  "BluefishJuvenile",
  "BluefishAdult",
  "WeakfishJuvenile",
  "WeakfishAdult",
  "AtlanticHerring0_1",
  "AtlanticHerring2",
  "Anchovies",
  "Benthos",
  "Zooplankton",
  "Phytoplankton",
  "Detritus"
)

scenario_code <- paste0(
  "ecosim_", 
  c(
    "base_run", 
    "forcing_pcp", "forcing_pcp_egg_amo0", "forcing_pcp_egg_amo1",
    "forcing_pdsi", "forcing_pdsi_egg_amo0", "forcing_pdsi_egg_amo1",
    "forcing_spline11", "forcing_spline11_egg_amo0", "forcing_spline11_egg_amo1",
    "forcing_spline33", "forcing_spline33_egg_amo0", "forcing_spline33_egg_amo1",
    "forcing_sst", "forcing_sst_egg_amo0", "forcing_sst_egg_amo1"
  ))

scenario_name <- c(
  "Base Case", 
  "PCP", 
  "PCP+AMO0",
  "PCP+AMO1",
  "PDSI", 
  "PDSI+AMO0",
  "PDSI+AMO1",
  "SPLINE11", 
  "SPLINE11+AMO0",
  "SPLINE11+AMO1",
  "SPLINE33",
  "SPLINE33+AMO0",
  "SPLINE33+AMO1",
  "SST", 
  "SST+AMO0",
  "SST+AMO1"
)

labels <- c(
  "Striped Bass 0", "Striped Bass 2-5", "Striped Bass 6+",
  "Atlantic Menhaden 0", "Atlantic Menhaden 1",
  "Atlantic Menhaden 2", "Atlantic Menhaden 3",
  "Atlantic Menhaden 4", "Atlantic Menhaden 5",
  "Atlantic Menhaden 6+",
  "Spiny Dogfish", "Bluefish juv", "Bluefish adult",
  "Weakfish juv", "Weakfish adult",
  "Atlantic Herring 0-1", "Atlantic Herring 2+",
  "Anchovies", "Benthos", "Zooplkanton", "Phytoplankton", "Detritus"
)

for (id in 1:length(scenario_code)){
  
  ewe_temp <- read_ewe_output(
    file_path = here::here("data", "ewe", "7ages_newsim_newF", "ewe7ages_ecosim_newF", scenario_code[id]),
    file_names = "biomass_monthly.csv",
    skip_nrows = 8,
    plot = FALSE,
    figure_titles = NULL,
    functional_groups = functional_groups,
    figure_colors = NULL
  )

  time_id <- seq(1, nrow(ewe_temp[[1]]), by = 12)

  ewe_output <- list(ewe_temp[[1]][time_id, ])
  ewe_output[[1]]$Year <- ewe_year
  
  names(ewe_output[[1]])[2:ncol(ewe_output[[1]])] <- labels
  ewe_output_melt <- reshape2::melt(ewe_output[[1]], id.vars = "Year")
  ewe_output_melt$Scenario <- scenario_name[id]
  
  if (id==1) {
    ewe_data <- ewe_output_melt
  } else{
    ewe_data <- rbind(ewe_data, ewe_output_melt)
  }
  
}
```

### Biomass trends from cases that only use forcing function
```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
subscenarios <- paste0(
  "ecosim_", 
  c(
    "base_run", 
    "forcing_pcp",
    "forcing_pdsi", 
    "forcing_spline11", 
    "forcing_spline33", 
    "forcing_sst"
  ))


subdata <- ewe_data[which(ewe_data$Scenario %in% scenario_name[scenario_code %in% subscenarios]), ]
biomass <- ggplot(subdata, aes(x = Year, y = value, color = Scenario)) +
  geom_line() +
  labs(
    title = "Comparison between scenarios",
    x = "Year",
    y = "Biomass (million mt)"
  ) +
  theme_bw()

biomass + facet_wrap(~variable, scales = "free_y") + scale_color_brewer(palette="Dark2")
```

### Total biomass of menhaden-like species from cases that only use forcing function
```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
ss_biomass <- subdata[grep("Atlantic Menhaden", subdata$variable), ]
ss_biomass <- aggregate(value~Year+Scenario, ss_biomass, sum)

total_biomass <- ggplot(ss_biomass, aes(x = Year, y = value, color = Scenario)) +
  geom_line() +
  labs(
    title = "Comparison between scenarios",
    x = "Year",
    y = "Total Biomass (million mt)"
  ) +
  theme_bw()

total_biomass + scale_color_brewer(palette="Dark2")

```

```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
source(here::here("Rscript", "load_indices.R"))
year_id <- seq(1, nrow(amo_unsmooth_lag1), by = 12)

amo <- amo_unsmooth_lag1[year_id, ]
pcp <- precipitation[year_id, ]
pdsi <- palmer_drought_severity_index[year_id, ]
sst <- kaplan_sst[year_id, ]

indices_name <- c("AMO", "PCP", "PDSI", "SST")

lm_results <- matrix(NA, nrow = length(subscenarios), ncol= length(indices_name))
rownames(lm_results) <- scenario_name[scenario_code %in% subscenarios]
colnames(lm_results) <- indices_name

cpm_results <- matrix(NA, nrow=1, ncol = length(subscenarios))
rownames(cpm_results) <- "ChangePoint"
colnames(cpm_results) <- scenario_name[scenario_code %in% subscenarios]

for (i in 1:length(subscenarios)){

  biomass_temp <- subdata[grep("Atlantic Menhaden", subdata$variable), ]
  biomass_temp <- biomass_temp[which(biomass_temp$Scenario == scenario_name[scenario_code %in% subscenarios[i]]), ]
  
  total_biomass <- aggregate(value~Year, biomass_temp, sum)$value
  
  temp_data <- data.frame(
    Biomass = total_biomass,
    AMO = amo$scaled_value,
    PCP = pcp$scaled_value, 
    PDSI = pdsi$scaled_value,
    SST = sst$scaled_value
  )
  
  change_dection <- cpm::detectChangePointBatch(total_biomass, cpmType = "Mann-Whitney", alpha = 0.05)
  cpm_results[1, i] <- change_dection$changePoint
  
  for (j in 1:length(indices_name)){
    lm_results[i, j] <- paste0(round(summary(lm(temp_data$Biomass ~ temp_data[,j+1]))$coefficients[2, 1], digits = 2), 
                             if(summary(lm(temp_data$Biomass ~ temp_data[,j+1]))$coefficients[2, 4] <= 0.05) {"*"})
  }
  
  
}
```

### Slope of linear regression model from cases that only use forcing function
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
knitr::kable(lm_results, caption = "Slope of linear regression model from cases that only use forcing function")

knitr::kable(cpm_results, caption = "Change point detection using CPM package")

```

### Biomass trends from cases that use forcing function and AMO index through egg production
```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
subscenarios <- paste0(
  "ecosim_", 
  c(
    "base_run",
    "forcing_pcp_egg_amo1",
    "forcing_pdsi_egg_amo1",
    "forcing_spline11_egg_amo1",
    "forcing_spline33_egg_amo1",
    "forcing_sst_egg_amo1"
  ))
subdata <- ewe_data[which(ewe_data$Scenario %in% scenario_name[scenario_code %in% subscenarios]), ]
biomass <- ggplot(subdata, aes(x = Year, y = value, color = Scenario)) +
  geom_line() +
  labs(
    title = "Comparison between scenarios",
    x = "Year",
    y = "Biomass (million mt)"
  ) +
  theme_bw()
 
biomass + facet_wrap(~variable, scales = "free_y") + scale_color_brewer(palette="Dark2")

```

### Total biomass of menhaden-like species from cases that use forcing function and AMO index through egg production
```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
ss_biomass <- subdata[grep("Atlantic Menhaden", subdata$variable), ]
ss_biomass <- aggregate(value~Year+Scenario, ss_biomass, sum)

total_biomass <- ggplot(ss_biomass, aes(x = Year, y = value, color = Scenario)) +
  geom_line() +
  labs(
    title = "Comparison between scenarios",
    x = "Year",
    y = "Total Biomass (million mt)"
  ) +
  theme_bw()

total_biomass + scale_color_brewer(palette="Dark2")

```

```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
lm_results <- matrix(NA, nrow = length(subscenarios), ncol= length(indices_name))
rownames(lm_results) <- scenario_name[scenario_code %in% subscenarios]
colnames(lm_results) <- indices_name

cpm_results <- matrix(NA, nrow=1, ncol = length(subscenarios))
rownames(cpm_results) <- "ChangePoint"
colnames(cpm_results) <- scenario_name[scenario_code %in% subscenarios]

for (i in 1:length(subscenarios)){

  biomass_temp <- subdata[grep("Atlantic Menhaden", subdata$variable), ]
  biomass_temp <- biomass_temp[which(biomass_temp$Scenario == scenario_name[scenario_code %in% subscenarios[i]]), ]
  
  total_biomass <- aggregate(value~Year, biomass_temp, sum)$value
  
  temp_data <- data.frame(
    Biomass = total_biomass,
    AMO = amo$scaled_value,
    PCP = pcp$scaled_value, 
    PDSI = pdsi$scaled_value,
    SST = sst$scaled_value
  )
  
  change_dection <- cpm::detectChangePointBatch(total_biomass, cpmType = "Mann-Whitney", alpha = 0.05)
  cpm_results[1, i] <- change_dection$changePoint
  
  for (j in 1:length(indices_name)){
    lm_results[i, j] <- paste0(round(summary(lm(temp_data$Biomass ~ temp_data[,j+1]))$coefficients[2, 1], digits = 2), 
                             if(summary(lm(temp_data$Biomass ~ temp_data[,j+1]))$coefficients[2, 4] <= 0.05) {"*"})
  }
  
  
}
```

### Slope of linear regression model from cases that use forcing function and AMO index through egg production
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
knitr::kable(lm_results, caption = "Slope of linear regression model from cases that use forcing function and AMO index through egg production")

knitr::kable(cpm_results, caption = "Change point detection using CPM package")

```

## {-}

## Sinple-species stock assessment input data simulation {.tabset}
```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
library(RColorBrewer)
library(ggplot2)
library(tidyverse)
library(reshape2)
library(here)
set.seed(999)

options(digits = 2)

# specify working directories ---------------------------------------------

project_path <- here::here()
# ewe_output_path <- file.path(project_path, "data", "ewe", "7ages_newsim", "ewe7ages_ecosim_new", "ecosim_base_run")
# ewe_output_path <- file.path(project_path, "data", "ewe", "7ages_newsim", "ewe7ages_ecosim_new", "ecosim_forcing_pdsi_egg_amo1")
ewe_output_path <- file.path(project_path, "data", "ewe", "7ages_newsim_newF", "ewe7ages_ecosim_newF", "ecosim_forcing_pdsi_egg_amo1")
menhadenSA_output_path <- file.path(project_path, "data", "AtlanticMenhadenSA")

# read Atlantic menhaden Beaufort Assessment Model output data --------

menhadenSA_output <- dget(file.path(menhadenSA_output_path, "am019.rdat"))

years <- 1985:2017
ages <- 0:6

# fishery selectivity
fishery_sel <- IFA4EBFM::logistic(
  pattern = "double_logistic",
  x = ages,
  slope_asc = 3.1,
  location_asc = 1.8,
  slope_desc = 0.88,
  location_desc = 0.01
) # CRS 1972 selectivity

# F-at-age
phase1_nyear <- 12
set.seed(9999)
f_full <- c(
  seq(0.25, 0.7, length = phase1_nyear),
  seq(0.7, 0.15, length = length(years) - phase1_nyear)
) *
  exp(rnorm(length(years), mean = 0, sd = 0.2))
fatage <- matrix(NA, nrow = length(f_full), ncol = length(fishery_sel))
rownames(fatage) <- years
colnames(fatage) <- paste0("menhaden", ages)
for (i in 1:length(f_full)) {
  fatage[i, ] <- f_full[i] * fishery_sel
}

write.csv(fatage, file.path(project_path, "data", "ewe", "7ages_newsim_newF", "fatage.csv"))


```

### Biomass-at-age
```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}

skip_nrows <- 8
species <- 4:10
species_labels <- paste0("age", ages)
species_vec <- paste0("X", species)

# Load biomass data
temp <- scan(file.path(ewe_output_path, "biomass_annual.csv"), what = "", sep = "\n")
data <- temp[-c(1:skip_nrows)]
data <- read.table(
  text = as.character(data),
  sep = ",",
  col.names = read.table(text = temp[skip_nrows], sep = ",")
)

data <- data[, c("year.group", species_vec)]
data[, species_vec] <- data[, species_vec] * 1000000  # biomass in mt
colnames(data) <- c("year", species_labels)

#data[, species_labels] <- data[, species_labels] / rowSums(data[, species_labels])
baa <- reshape2::melt(data, id.vars = c("year"))
colnames(baa) <- c("Year", "Age", "Biomass")
  
p <- ggplot(data=baa, aes(x=Age, fill=Age, y=Biomass)) +
      geom_bar(position='dodge', stat='identity') +
      facet_wrap(~Year) +
      labs(
        title = "Biomass-at-age",
        x = "Age",
        y = "Proportion"
      )+
      theme_bw()+
      theme(axis.text.x = element_text(angle = 45))
print(p)
```

### Catch
```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}

# Create fishery ----------------------------------------------------------

fishery_sample_num <- cbind(
  menhadenSA_output$t.series$acomp.cRs.n[which(menhadenSA_output$t.series$year %in% years)],
  menhadenSA_output$t.series$acomp.cBs.n[which(menhadenSA_output$t.series$year %in% years)],
  menhadenSA_output$t.$acomp.cBn.n[which(menhadenSA_output$t.series$year %in% years)],
  menhadenSA_output$t.series$acomp.cRn.n[which(menhadenSA_output$t.series$year %in% years)]
)
fishery_sample_num[fishery_sample_num==-99999] <- 0

fishery <- create_fishery(
  file_path = file.path(ewe_output_path, "catch_annual.csv"),
  skip_nrows = 8,
  species = 4:10,
  species_labels = paste0("age", ages),
  years = years,
  fleet_num = 1,
  selectivity = NULL,
  CV = rep(0.05, length(years)),
  sample_num = apply(fishery_sample_num, 1, sum),
  waa_path = file.path(ewe_output_path, "weight_annual.csv")
)

# Total catch in biomass
om <- data.frame (
  Year = years, 
  Catch = fishery$om_total_catch_biomass,
  Model = "OM"
)

obs <- data.frame (
  Year = years, 
  Catch = fishery$obs_total_catch_biomass$fleet1,
  Model = "OBS"
)

year_id <- which(menhadenSA_output$t.series$year %in% years)
bam <- data.frame (
  Year = years, 
  Catch = (menhadenSA_output$t.series$L.cBs.ob[year_id] + menhadenSA_output$t.series$L.cBn.ob[year_id] + menhadenSA_output$t.series$L.cRs.ob[year_id] + menhadenSA_output$t.series$L.cRn.ob[year_id]) * 1000,
  Model = "BAM"
)

#data <- rbind(om, obs, bam)
data <- rbind(om, obs)
p <- ggplot(data, aes(x = Year, y = Catch, color = Model)) +
  geom_line() +
  labs(
    title = "Comparison between models",
    x = "Year",
    y = "Total Catch (mt)"
  ) +
  theme_bw()
p

```

### Catch-at-age
```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
om <- fishery$om_caa_abundance/rowSums(fishery$om_caa_abundance)
om$Year <- years
om$Model <- "OM"
om <- reshape2::melt(om, id.vars = c("Year", "Model"))
colnames(om) <- c("Year", "Model", "Age", "Catch")

obs <- fishery$obs_caa_prop$fleet1
obs$Year <- years
obs$Model <- "OBS"
obs <- reshape2::melt(obs, id.vars = c("Year", "Model"))
colnames(obs) <- c("Year", "Model", "Age", "Catch")

data <- list(om=om, obs=obs)
## OM catch-at-age
p <- ggplot(data=data$om, aes(x=Age, fill=Age, y=Catch)) +
      geom_bar(position='dodge', stat='identity') +
      facet_wrap(~Year) +
      labs(
        title = "OM catch-at-age",
        x = "Age",
        y = "Proportion"
      )+
      theme_bw()+
      theme(axis.text.x = element_text(angle = 45)) 

p 

## Observed catch-at-age
p <- ggplot(data=data$obs, aes(x=Age, fill=Age, y=Catch)) +
      geom_bar(position='dodge', stat='identity') +
      facet_wrap(~Year) +
      labs(
        title = "Observed catch-at-age",
        x = "Age",
        y = "Proportion"
      )+
      theme_bw()+
      theme(axis.text.x = element_text(angle = 45))

p

```

```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
# Create survey ----------------------------------------------------------

# selectivity settings
survey_num <- 2

survey_name <- c("survey1", "survey2")

# set up survey time
# Need to check Table 26 from BAM assessment: Length cutoffs used to distinguish age-0 from age-1+ Atlantic menhaden at different regions.

survey1_year <- 1990:2017 # Adult Index (survey1): age 1+ fish; September - January; Time of the year when menhaden were most abundant in this region

survey2_year <- 1985:2017 # Adult Index (survey2): age 1+ fish; March - May

survey_time <- list(
  survey1 = data.frame(
    year = survey1_year,
    month = rep(10, length(survey1_year)) # Oct 15
  ),
  survey2 = data.frame(
    year = survey2_year,
    month = rep(4, length(survey2_year)) # April 15
  )
)

# set up survey selectivity
# survey1_sel <- IFA4EBFM::logistic(
#   pattern = "double_logistic",
#   x = ages,
#   slope_asc = 2.2,
#   location_asc = 3.0,
#   slope_desc = 3.0,
#   location_desc = 3.5
# )
# 
# survey1_sel <- IFA4EBFM::logistic(
#   pattern = "simple_logistic",
#   x = ages,
#   slope_asc = 2.2,
#   location_asc = 3.0
# )

survey1_sel <- IFA4EBFM::logistic(
  pattern = "double_logistic",
  x = ages,
  slope_asc = 4.3,
  location_asc = 2.3,
  slope_desc = 3.5,
  location_desc = 2.3
)

survey2_sel <- IFA4EBFM::logistic(
  pattern = "double_logistic",
  x = ages,
  slope_asc = 4.3,
  location_asc = 2.3,
  slope_desc = 3.5,
  location_desc = 2.3
)


survey_selectivity <- list(
  survey1 = as.data.frame(
    matrix(rep(survey1_sel, times = length(years)), ncol = length(ages), byrow = TRUE),
    row.names = years
  ),
  survey2 = as.data.frame(
    matrix(rep(survey2_sel, times = length(years)), ncol = length(ages), byrow = TRUE),
    row.names = years,
  )
)

survey_selectivity <- lapply(survey_selectivity, setNames, paste("age", ages))

# set up catchability
survey_catchability <- list(
  survey1 = menhadenSA_output$t.series$q.nad[which(menhadenSA_output$t.series$year %in% years)],
  survey2 = menhadenSA_output$t.series$q.mad[which(menhadenSA_output$t.series$year %in% years)]
)

survey_catchability <- lapply(survey_catchability, setNames, years)

# set up CV
# survey_CV <- list(
#   survey1 = menhadenSA_output$t.series$cv.U.nad[which(menhadenSA_output$t.series$year %in% years)],
#   survey2 = menhadenSA_output$t.series$cv.U.mad[which(menhadenSA_output$t.series$year %in% years)]
# )

survey_CV <- list(
  survey1 = rep(0.1, length(years)),
  survey2 = rep(0.1, length(years))
)

survey_CV <- lapply(survey_CV, setNames, years)

# set up sample number
survey_sample_num <- list(
  survey1 = menhadenSA_output$t.series$lcomp.nad.nfish[which(menhadenSA_output$t.series$year %in% years)],
  #survey2 = menhadenSA_output$t.series$lcomp.mad.nfish[which(menhadenSA_output$t.series$year %in% years)]
  survey2 = rep(1000, length= length(years))
)
survey_sample_num <- lapply(survey_sample_num, setNames, years)

for (i in 1:length(survey_sample_num)) {
  survey_sample_num[[i]][survey_sample_num[[i]] == -99999] <- NA
}

# set up age-length population structure
length_bin <- seq(10.0, 600, 10) / 10 # in cm
mid_length_bin <- seq(15, 605, 10) / 10 # in cm
nbin <- length(length_bin)
bin_width <- 1

length_CV <- list(
  survey1 = 0.12,
  survey2 = 0.17
)

# Create survey
survey <- IFA4EBFM::create_survey(
  file_path = file.path(ewe_output_path, "biomass_monthly.csv"),
  skip_nrows = 8,
  species = 4:10,
  species_labels = paste0("age", ages),
  years = years,
  survey_num = survey_num,
  survey_time = survey_time,
  selectivity = survey_selectivity,
  catchability = survey_catchability,
  CV = survey_CV,
  sample_num = survey_sample_num,
  waa_path = file.path(ewe_output_path, "weight_monthly.csv"),
  length_bin = length_bin,
  mid_length_bin = mid_length_bin,
  nbin = nbin,
  bin_width = bin_width,
  length_CV = length_CV
)
```
### Survey selectivity patterns
```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
plot(0:6, as.numeric(survey_selectivity$survey1[1, ]), 
     type="o", pch=1, col=1, lty=1,
     xlab = "Age", ylab = "Selectivity")
lines(0:6, as.numeric(survey_selectivity$survey2[1, ]), pch=2, col=2, lty=2, type="o")
legend("topright",
       names(survey_selectivity),
       pch= 1:2,
       col = 1:2, 
       lty=1:2,
       bty="n"
       )

```

### Survey index over time
```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}

om <- data.frame(matrix(ncol=4, nrow=0))
for (i in 1:length(survey$om_abundance_index)){
  temp <- data.frame(
  Year = as.numeric(names(survey$om_abundance_index[[i]])), 
  Index = survey$om_abundance_index[[i]],
  Model = "OM",
  Survey = names(survey$om_abundance_index)[i]
)
  om <- rbind(om, temp)
}

obs <- data.frame(matrix(ncol=4, nrow=0))
for (i in 1:length(survey$obs_abundance_index)){
  temp <- data.frame(
  Year = as.numeric(names(survey$obs_abundance_index[[i]])), 
  Index = survey$obs_abundance_index[[i]],
  Model = "OBS",
  Survey = names(survey$obs_abundance_index)[i]
)
  obs <- rbind(obs, temp)
}

data <- rbind(om, obs)
p <- ggplot(data, aes(x = Year, y = Index, color = Model)) +
  geom_line() +
  facet_wrap(~Survey, scales = "free_y") +
  labs(
    title = "Comparison between models",
    x = "Year",
    y = "Abundance Index"
  ) +
  theme_bw()
p
```

### Survey length composition
```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
## Survey 1
obs <- as.data.frame(survey$obs_lencomp_proportion_ss3[[1]])
obs$Year <- as.numeric(row.names(survey$obs_lencomp_proportion_ss3[[1]]))
obs$Model <- "OBS"
obs$Survey <- names(survey$obs_lencomp_proportion_ss3)[1]

obs <- na.omit(obs)

obs <- reshape2::melt(obs, id.vars = c("Year", "Model", "Survey"))
colnames(obs) <- c("Year", "Model", "Survey", "Length_Bin", "Value")

obs$Length_Bin <- as.numeric(as.character(obs$Length_Bin))
p <- ggplot(data=obs, aes(x=Length_Bin, fill=Length_Bin, y=Value)) +
  geom_bar(position='dodge', stat='identity') +
  facet_wrap(~Year) +
  labs(
    title = names(survey$obs_lencomp_proportion_ss3)[1],
    x = "Length Bins (cm)",
    y = "Proportion"
  )+
  theme_bw()
p

## Survey 2
obs <- as.data.frame(survey$obs_lencomp_proportion_ss3[[2]])
obs$Year <- as.numeric(row.names(survey$obs_lencomp_proportion_ss3[[2]]))
obs$Model <- "OBS"
obs$Survey <- names(survey$obs_lencomp_proportion_ss3)[2]

obs <- na.omit(obs)

obs <- reshape2::melt(obs, id.vars = c("Year", "Model", "Survey"))
colnames(obs) <- c("Year", "Model", "Survey", "Length_Bin", "Value")

obs$Length_Bin <- as.numeric(as.character(obs$Length_Bin))
p <- ggplot(data=obs, aes(x=Length_Bin, fill=Length_Bin, y=Value)) +
  geom_bar(position='dodge', stat='identity') +
  facet_wrap(~Year) +
  labs(
    title = names(survey$obs_lencomp_proportion_ss3)[2],
    x = "Length Bins (cm)",
    y = "Proportion"
  )+
  theme_bw()
p

```

```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
biodata <- create_biodata(nsex=1, narea=1, ages=ages, years=years,
                          length_bin=length_bin, mid_length_bin=mid_length_bin,
                          nbin=nbin, bin_width=bin_width, length_CV=length_CV,
                          annual_weight_path=file.path(ewe_output_path, "weight_annual.csv"),
                          monthly_weight_path=file.path(ewe_output_path, "weight_monthly.csv"),
                          species=4:10,
                          species_labels=paste0("age", ages),
                          skip_nrows=8,
                          lw_a=0.01, lw_b=3,
                          k=0.331,
                          t0 = -0.1,
                          winf = 0.237,
                          maturity_at_age=c(0.0, 0.1, 0.5, 0.9, 1.0, 1.0, 1.0), # From both BAM and EwE
                          natural_mortality_at_age=c(1.76, 1.31, 1.03, 0.9, 0.81, 0.76, 0.72) # From both BAM and EwE
)

sa_data <- list(
    fishery = fishery,
    survey = survey,
    biodata = biodata
)
```

## {-}

## Stock Synthesis 3 results {.tabset}
```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
# Install required R packages -------------------------------------
devtools::load_all()
required_pkg <- c(
  "devtools", "here"
)

pkg_to_install <- required_pkg[!(required_pkg %in%
  installed.packages()[, "Package"])]
if (length(pkg_to_install)) install.packages(pkg_to_install)

lapply(required_pkg, library, character.only = TRUE)

devtools::install_github("r4ss/r4ss",
  ref = "c53f82fcfb3f54296d79ba3a4163990150981285"
)
library(r4ss)

# Case 0: default stock assessment run ----------------------------
# Load simulated input data
source(here::here("Rscript", "load_indices.R"))
file_path <- here::here("data", "data_rich")
originalwd <- getwd()

depletion <- FALSE
depletion_ratio <- 0.8 # tried values between 0.3 - 0.8

model_year <- 1985:2012
projection_year <- 2013:2017

generate_ss3(
  file_path = file_path,
  r0 = 12, steepness = 0.5, sigmar = 0.25,
  projection_f = 0.75, projection_catch = NULL,
  sa_data = sa_data, model_year = model_year,
  projection_year = projection_year,
  use_depletion = FALSE, depletion_ratio = NULL, 
  initial_equilibrium_catch = TRUE
)

# Run SS3 ----------------------------------------------------------

setwd(file_path)
system(paste(file.path(file_path, "ss_win.exe"), file.path(file_path, "data.ss"), sep = " "), show.output.on.console = TRUE)

# get FMSY
ss3list <- SS_output(
  dir = file_path,
  verbose = TRUE,
  printstats = TRUE
)

fmsy <- ss3list$derived_quants$Value[ss3list$derived_quants$Label == "annF_MSY"]

# Re-run SS3 with projection_f = fmsy
generate_ss3(
  file_path = file_path,
  r0 = 12, steepness = 0.5, sigmar = 0.25,
  projection_f = fmsy, projection_catch = NULL,
  sa_data = sa_data, model_year = model_year,
  projection_year = projection_year,
  use_depletion = FALSE, depletion_ratio = NULL,
  initial_equilibrium_catch = TRUE
)

system(paste(file.path(file_path, "ss_win.exe"), file.path(file_path, "data.ss"), sep = " "), show.output.on.console = TRUE)
on.exit(setwd(originalwd), add = TRUE)
# plot r4ss -------------------------------------------------------

# read the model output and print diagnostic messages
ss3list <- SS_output(
  dir = file_path,
  verbose = TRUE,
  printstats = TRUE
)

# plots the results
SS_plots(ss3list)
```

### Compare "true" values from OM and SS3 results
```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
# Compare SS3 estimate with EwE "true" values ---------------------
# Comparisons
functional_groups <- c(
  "StripedBass0",
  "StripedBass2_5",
  "StripedBass6",
  "AtlanticMenhaden0",
  "AtlanticMenhaden1",
  "AtlanticMenhaden2",
  "AtlanticMenhaden3",
  "AtlanticMenhaden4",
  "AtlanticMenhaden5",
  "AtlanticMenhaden6",
  "SpinyDogfish",
  "BluefishJuvenile",
  "BluefishAdult",
  "WeakfishJuvenile",
  "WeakfishAdult",
  "AtlanticHerring0_1",
  "AtlanticHerring2",
  "Anchovies",
  "Benthos",
  "Zooplankton",
  "Phytoplankton",
  "Detritus"
)

age_name <- paste0("AtlanticMenhaden", 0:6)

# Biomass
biomass <- read_ewe_output(
  file_path = ewe_output_path,
  file_names = "biomass_monthly.csv",
  skip_nrows = 8,
  plot = FALSE,
  figure_titles = NULL,
  functional_groups = functional_groups,
  figure_colors = NULL
)

time_id <- seq(1, nrow(biomass[[1]]), by = 12)
biomass_ewe <- apply(biomass[[1]][, age_name], 1, sum) * 1000000

par(mfrow = c(2, 2))
model_year_id <- which(ss3list$timeseries$Yr %in% model_year)
projection_year_id <- which(ss3list$timeseries$Yr %in% projection_year)
ylim <- range(biomass_ewe[time_id], ss3list$timeseries$Bio_all)
plot(c(model_year, projection_year),
  biomass_ewe[time_id],
  xlab = "Year", ylab = "Biomass (mt)",
  ylim = ylim,
  pch = 16
)
lines(model_year, ss3list$timeseries$Bio_all[model_year_id], lty = 1)
#par(new = TRUE)
#plot(model_year, ss3list$timeseries$Bio_all[model_year_id], lty = 1, type = "l", axes = FALSE, xlab = "", ylab = "")
lines(projection_year,
  ss3list$timeseries$Bio_all[projection_year_id],
  lty = 2
)
#axis(side = 4, at = pretty(range(ss3list$timeseries$Bio_all[model_year_id])))
legend("topleft",
  c("EWE", "SS3 Estimation", "SS3 projection"),
  bty = "n",
  pch = c(16, NA, NA),
  lty = c(NA, 1, 2)
)
cor(biomass_ewe[time_id], c(ss3list$timeseries$Bio_all[model_year_id], ss3list$timeseries$Bio_all[projection_year_id]))

# Abundance
waa <- read_ewe_output(
  file_path = ewe_output_path,
  file_names = "weight_monthly.csv",
  skip_nrows = 8,
  plot = FALSE,
  figure_titles = NULL,
  functional_groups = functional_groups,
  figure_colors = NULL
)

abundance_ewe <- apply(biomass[[1]][, age_name] * 1000000 / waa[[1]][, age_name], 1, sum)[time_id]

ylim <- range(abundance_ewe, ss3list$timeseries$`SmryNum_SX:1_GP:1` * 1000)
plot(c(model_year, projection_year),
  abundance_ewe,
  xlab = "Year", ylab = "Abundance",
  ylim = ylim,
  pch = 16
)
lines(model_year, ss3list$timeseries$`SmryNum_SX:1_GP:1`[model_year_id] * 1000, lty = 1)
#par(new = TRUE)
#plot(model_year, ss3list$timeseries$`SmryNum_SX:1_GP:1`[model_year_id] * 1000, lty = 1, type = "l", axes = FALSE, xlab = "", ylab = "")
#axis(side = 4, at = pretty(range(ss3list$timeseries$`SmryNum_SX:1_GP:1`[model_year_id] * 1000)))
lines(projection_year,
  ss3list$timeseries$`SmryNum_SX:1_GP:1`[projection_year_id] * 1000,
  lty = 2
)
legend("topright",
  c("EWE", "SS3 Estimation", "SS3 projection"),
  bty = "n",
  pch = c(16, NA, NA),
  lty = c(NA, 1, 2)
)

cor(abundance_ewe, c(ss3list$timeseries$`SmryNum_SX:1_GP:1`[model_year_id] * 1000, ss3list$timeseries$`SmryNum_SX:1_GP:1`[projection_year_id] * 1000))
# Recruitment
waa <- read_ewe_output(
  file_path = ewe_output_path,
  file_names = "weight_monthly.csv",
  skip_nrows = 8,
  plot = FALSE,
  figure_titles = NULL,
  functional_groups = functional_groups,
  figure_colors = NULL
)

recruit_ewe <- biomass[[1]][, "AtlanticMenhaden0"][time_id] * 1000000 / waa[[1]][, "AtlanticMenhaden0"][time_id]

recruit_ss3 <- data.frame(
  year = c(model_year, projection_year),
  recruit = ss3list$natage$`1`[which(ss3list$natage$`Beg/Mid` == "B" & ss3list$natage$Yr %in% c(model_year, projection_year))] * 1000
)


ylim <- range(recruit_ewe, recruit_ss3$recruit)
plot(c(model_year, projection_year),
  recruit_ewe,
  xlab = "Year", ylab = "Abundance of age-0 fish",
  ylim = ylim,
  pch = 16
)
lines(model_year, recruit_ss3$recruit[recruit_ss3$year %in% model_year],
     lty = 1)
# par(new = TRUE)
# plot(model_year, recruit_ss3$recruit[recruit_ss3$year %in% model_year],
#   lty = 1, type = "l", axes = FALSE, xlab = "", ylab = ""
# )
# axis(side = 4, at = pretty(range(recruit_ss3$recruit[recruit_ss3$year %in% model_year])))
lines(projection_year,
  recruit_ss3$recruit[recruit_ss3$year %in% projection_year],
  lty = 2
)
legend("topright",
  c("EWE", "SS3 Estimation", "SS3 projection"),
  bty = "n",
  pch = c(16, NA, NA),
  lty = c(NA, 1, 2)
)

# Mortality
# mortality <- read.csv(file = here::here("data", "ewe", "7ages", "updated_f.csv"))
# mortality_ewe <- apply(mortality[seq(1, nrow(mortality), by=12), grep("AtlanticMenhaden", colnames(mortality))], 1, max)

mortality <- read.csv(file = here::here("data", "ewe", "7ages_newsim_newF", "fatage.csv"))
mortality_ewe <- apply(mortality[, 2:ncol(mortality)], 1, max)
# mortality_ewe <- apply(mortality[, 2:ncol(mortality)], 1, mean)

ylim <- range(mortality_ewe, ss3list$timeseries$`F:_1`)
plot(c(model_year, projection_year),
  mortality_ewe,
  xlab = "Year", ylab = "Mortality",
  ylim = ylim,
  pch = 16
)
lines(model_year, ss3list$timeseries$`F:_1`[model_year_id],
     lty = 1)
# par(new = TRUE)
# plot(model_year, ss3list$timeseries$`F:_1`[model_year_id],
#   lty = 1, type = "l", , axes = FALSE, xlab = "", ylab = ""
# )
# axis(side = 4, at = pretty(range(ss3list$timeseries$`F:_1`[model_year_id])))
lines(projection_year,
  ss3list$timeseries$`F:_1`[projection_year_id],
  lty = 2
)
legend("topright",
  c("EWE F", "SS3 F", "SS3 FMSY"),
  bty = "n",
  pch = c(16, NA, NA),
  lty = c(NA, 1, 2)
)
```

### Linear regression models
```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
# Linear regression models from cases 1 - 4 using "true" values from EwE------------------------

# use abundance instead of biomass
biomass_ewe <- apply(biomass[[1]][, age_name] * 1000000 / waa[[1]][, age_name], 1, sum)

lm_slope <- data.frame(
  case = "True indices",
  amo = NA,
  pcp = NA,
  bassB = NA,
  price = NA
)

year_id <- seq(1, nrow(amo_unsmooth_lag1), by = 12)
index_year <- c(model_year, projection_year)

amo <- amo_unsmooth_lag1[year_id, ]
amo_lm <- lm(biomass_ewe[time_id] ~ amo$raw_value)
amo_fit <- fitted(amo_lm)
lm_slope$amo <- paste0(
  round(summary(amo_lm)$coefficients[2, 1], digits = 2),
  if (summary(amo_lm)$coefficients[2, 4] <= 0.05) {
    "*"
  }
)

pcp <- precipitation[year_id, ]
pcp_lm <- lm(biomass_ewe[time_id] ~ pcp$raw_value)
pcp_fit <- fitted(pcp_lm)
lm_slope$pcp <- paste0(
  round(summary(pcp_lm)$coefficients[2, 1], digits = 2),
  if (summary(pcp_lm)$coefficients[2, 4] <= 0.05) {
    "*"
  }
)

bassB <- bass_bio[bass_bio$Year %in% index_year, ]
bassB_lm <- lm(biomass_ewe[time_id] ~ bassB$bass_bio)
bassB_fit <- fitted(bassB_lm)
lm_slope$bassB <- paste0(
  round(summary(bassB_lm)$coefficients[2, 1], digits = 2),
  if (summary(bassB_lm)$coefficients[2, 4] <= 0.05) {
    "*"
  }
)

sub_menhadenP <- menhaden_price$Inflation.Adjust.Price.Per.MT[menhaden_price$Year %in% index_year]
price_lm <- lm(biomass_ewe[time_id] ~ sub_menhadenP)
price_fit <- fitted(price_lm)
lm_slope$price <- paste0(
  round(summary(price_lm)$coefficients[2, 1], digits = 2),
  if (summary(price_lm)$coefficients[2, 4] <= 0.05) {
    "*"
  }
)

par(mfrow = c(2, 2))

plot(amo$raw_value, biomass_ewe[time_id],
  xlab = "AMO raw values",
  ylab = "Menhaden-like species B from OM"
)
lines(amo$raw_value, amo_fit, lty = 2, col = "blue")

plot(pcp$raw_value, biomass_ewe[time_id],
  xlab = "Precipitation raw values",
  ylab = "Menhaden-like species B from OM"
)
lines(pcp$raw_value, pcp_fit, lty = 2, col = "blue")

plot(bassB$bass_bio, biomass_ewe[time_id],
  xlab = "Biomass of Striped bass",
  ylab = "Menhaden-like species B from OM"
)
lines(bassB$bass_bio, bassB_fit, lty = 2, col = "blue")

plot(sub_menhadenP, biomass_ewe[time_id],
  xlab = "Menhaden price",
  ylab = "Menhaden-like species B from OM"
)
lines(sub_menhadenP, price_fit, lty = 2, col = "blue")

knitr::kable(lm_slope)
```


```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
# Projection: cases 1 - 4 ---------------------------

lm_slope <- data.frame(
  case = 0.2,
  projection_year = 1:length(projection_year),
  amo = NA,
  pcp = NA,
  bassB = NA,
  price = NA
)

for (projection_year_id in 1:length(projection_year)) {

  # abundance
  if (projection_year_id == 1) {
    menhaden_b <- ss3list$timeseries$`SmryNum_SX:1_GP:1`[model_year_id]
  } else {
    menhaden_b <- c(ss3list$timeseries$`SmryNum_SX:1_GP:1`[model_year_id], ss3list$timeseries$`SmryNum_SX:1_GP:1`[1:(projection_year_id - 1)])
  }

  # biomass
  # if (projection_year_id ==1) {
  #   menhaden_b <- ss3list$timeseries$Bio_all[model_year_id]
  # } else {
  #   menhaden_b <- c(ss3list$timeseries$Bio_all[model_year_id], ss3list$timeseries$Bio_all[1:(projection_year_id-1)])
  # }


  year_id <- seq(1, nrow(amo_unsmooth_lag1), by = 12)[1:(length(model_year) + projection_year_id - 1)]

  if (projection_year_id == 1) {
    index_year <- model_year
  } else {
    index_year <- c(model_year, projection_year[1:(projection_year_id - 1)])
  }


  # Linear regression model -----------------------------------------

  amo <- amo_unsmooth_lag1[year_id, ]
  amo_lm <- lm(menhaden_b ~ amo$raw_value)
  summary(amo_lm)
  amo_fit <- fitted(amo_lm)
  lm_slope$amo[projection_year_id] <- paste0(
    round(summary(amo_lm)$coefficients[2, 1], digits = 2),
    if (summary(amo_lm)$coefficients[2, 4] <= 0.05) {
      "*"
    }
  )

  pcp <- precipitation[year_id, ]
  pcp_lm <- lm(menhaden_b ~ pcp$raw_value)
  summary(pcp_lm)
  pcp_fit <- fitted(pcp_lm)
  lm_slope$pcp[projection_year_id] <- paste0(
    round(summary(pcp_lm)$coefficients[2, 1], digits = 2),
    if (summary(pcp_lm)$coefficients[2, 4] <= 0.05) {
      "*"
    }
  )

  bassB <- bass_bio[bass_bio$Year %in% index_year, ]
  bassB_lm <- lm(menhaden_b ~ bassB$bass_bio)
  summary(bassB_lm)
  bassB_fit <- fitted(bassB_lm)
  lm_slope$bassB[projection_year_id] <- paste0(
    round(summary(bassB_lm)$coefficients[2, 1], digits = 2),
    if (summary(bassB_lm)$coefficients[2, 4] <= 0.05) {
      "*"
    }
  )

  sub_menhaden_b <- menhaden_b[index_year %in% menhaden_price$Year]
  sub_menhadenP <- menhaden_price$Inflation.Adjust.Price.Per.MT[menhaden_price$Year %in% index_year]
  price_lm <- lm(sub_menhaden_b ~ sub_menhadenP)
  summary(price_lm)
  price_fit <- fitted(price_lm)
  lm_slope$price[projection_year_id] <- paste0(
    round(summary(price_lm)$coefficients[2, 1], digits = 2),
    if (summary(price_lm)$coefficients[2, 4] <= 0.05) {
      "*"
    }
  )

  if (projection_year_id == length(projection_year)) {
    par(mfrow = c(2, 2))

    plot(amo$raw_value, menhaden_b,
      xlab = "AMO raw values",
      ylab = "Biomass of menhaden-like species"
    )
    lines(amo$raw_value, amo_fit, lty = 2, col = "blue")

    plot(pcp$raw_value, menhaden_b,
      xlab = "Precipitation raw values",
      ylab = "Biomass of menhaden-like species"
    )
    lines(pcp$raw_value, pcp_fit, lty = 2, col = "blue")

    plot(bassB$bass_bio, menhaden_b,
      xlab = "Biomass of Striped bass",
      ylab = "Biomass of menhaden-like species"
    )
    lines(bassB$bass_bio, bassB_fit, lty = 2, col = "blue")

    plot(sub_menhadenP, sub_menhaden_b,
      xlab = "Menhaden price",
      ylab = "Biomass of menhaden-like species"
    )
    lines(sub_menhadenP, price_fit, lty = 2, col = "blue")
  }


  # status of indicators --------------------------------------------

  amo_soi <- calc_soi(
    indicator_data = amo$raw_value,
    slope = coef(amo_lm)[2]
  )

  pcp_soi <- calc_soi(
    indicator_data = pcp$raw_value,
    slope = coef(pcp_lm)[2]
  )

  bassB_soi <- calc_soi(
    indicator_data = bassB$bass_bio,
    slope = coef(bassB_lm)[2]
  )

  price_soi <- calc_soi(
    indicator_data = sub_menhadenP,
    slope = coef(price_lm)[2]
  )

  if (projection_year_id == 1) {
    scaled_data <- data.frame(
      year = model_year,
      projection_year_id = projection_year_id,
      amo = scale(amo$raw_value)[, 1],
      pcp = scale(pcp$raw_value)[, 1],
      bassB = scale(bassB$bass_bio)[, 1],
      price = scale(sub_menhadenP)[, 1],
      menhadenB = scale(menhaden_b)[, 1]
    )

    soi_data <- data.frame(
      year = model_year,
      projection_year_id = projection_year_id,
      amo = amo_soi,
      pcp = pcp_soi,
      bass_b = bassB_soi,
      price = price_soi
    )
  } else {
    scaled_data <- rbind(
      scaled_data,
      data.frame(
        year = index_year,
        projection_year_id = projection_year_id,
        amo = scale(amo$raw_value)[, 1],
        pcp = scale(pcp$raw_value)[, 1],
        bassB = scale(bassB$bass_bio)[, 1],
        price = scale(sub_menhadenP)[, 1],
        menhadenB = scale(menhaden_b)[, 1]
      )
    )

    soi_data <- rbind(
      soi_data,
      data.frame(
        year = index_year,
        projection_year_id = projection_year_id,
        amo = amo_soi,
        pcp = pcp_soi,
        bass_b = bassB_soi,
        price = price_soi
      )
    )
  }



  # Adjusted FMSY ----------------------------------------------------

  if (projection_year_id == 1) {
    Bt_BMSY <- ss3list$Kobe$B.Bmsy[length(model_year)]
  } else {
    Bt_BMSY <- ss3list$Kobe$B.Bmsy[length(model_year) + projection_year_id - 1]
  }

  ss3_fmsy <- rnorm(1000, ss3list$derived_quants$Value[ss3list$derived_quants$Label == "annF_MSY"], 0.5)
  ss3_Bt_BMSY <- rep(Bt_BMSY, 1000)

  ss3_fmsy[ss3_fmsy < 0] <- 0.1
  amo_fmsy <- adjust_projection_jabba(
    FMSY = ss3_fmsy,
    soi = tail(amo_soi, n = 1),
    Bt_BMSY = ss3_Bt_BMSY
  )
  pcp_fmsy <- adjust_projection_jabba(
    FMSY = ss3_fmsy,
    soi = tail(pcp_soi, n = 1),
    Bt_BMSY = ss3_Bt_BMSY
  )
  bassB_fmsy <- adjust_projection_jabba(
    FMSY = ss3_fmsy,
    soi = tail(bassB_soi, n = 1),
    Bt_BMSY = ss3_Bt_BMSY
  )
  price_fmsy <- adjust_projection_jabba(
    FMSY = ss3_fmsy,
    soi = tail(price_soi, n = 1),
    Bt_BMSY = ss3_Bt_BMSY
  )

  if (projection_year_id == 1) {
    fmsy_data <- data.frame(
      iter = 1:length(amo_fmsy),
      projection_year_id = projection_year_id,
      ss3 = ss3_fmsy,
      amo = amo_fmsy,
      pcp = pcp_fmsy,
      bassB = bassB_fmsy,
      price = price_fmsy
    )
  } else {
    fmsy_data <- rbind(
      fmsy_data,
      data.frame(
        iter = 1:length(amo_fmsy),
        projection_year_id = projection_year_id,
        ss3 = ss3_fmsy,
        amo = amo_fmsy,
        pcp = pcp_fmsy,
        bassB = bassB_fmsy,
        price = price_fmsy
      )
    )
  }
}



scaled_data_melt <- reshape2::melt(
  scaled_data,
  id = c("year", "projection_year_id")
)
scaled_data_melt$projection_year_id <- as.factor(scaled_data_melt$projection_year_id)
```


```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
soi_data_melt <- reshape2::melt(
  soi_data,
  id = c("year", "projection_year_id")
)
soi_data_melt$projection_year_id <- as.factor(soi_data_melt$projection_year_id)

```

### F adjustment
```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
fmsy_data_melt <- reshape2::melt(
  fmsy_data,
  id = c("iter", "projection_year_id")
)
fmsy_data_melt$projection_year_id <- as.factor(fmsy_data_melt$projection_year_id)

fmsy_data_melt_median <- aggregate(value ~ projection_year_id + variable, data = fmsy_data_melt, median)
fmsy_data_melt_median$projection_year_id <- as.numeric(fmsy_data_melt_median$projection_year_id)

p <- ggplot(fmsy_data_melt, aes(x = variable, y = value, color = projection_year_id)) +
  geom_boxplot() +
  labs(
    title = "FMSY from SS3 and adjusted FMSY",
    x = "",
    y = "FMSY"
  ) +
  theme_bw()

p
```

## {-}
