---
title: 'Data-poor stock assessment'
date: 'Updated on May 11, 2022'
output:
  html_document: 
    code_folding: hide
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Depletion-Based Stock Reduction Analysis(DB-SRA) from DLMtool

- Website: [https://github.com/Blue-Matter/DLMtool](https://github.com/Blue-Matter/DLMtool)

```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
devtools::load_all()

# Install required R packages -------------------------------------
required_pkg <- c("DLMtool", "here") ## version 6.0.3

pkg_to_install <- required_pkg[!(required_pkg %in%
  installed.packages()[, "Package"])]
if (length(pkg_to_install)) install.packages(pkg_to_install)

lapply(required_pkg, library, character.only = TRUE)
```

## Case 0: stock assessment base run

  - Case 0.1
    - Depletion relative to unfished: 0.27 (assume catch is proportional to biomass and use $catch_{2012}/catch_{1985}$)
    - BMSY relative to unfished: 0.3 (based on fecundity target value from Beaufort Stock Assessment report)
  
```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
# Load simulated input data
source(here::here("Rscript", "simulation.R"))
source(here::here("Rscript", "load_indices.R"))

# Load EwE biomass----------------------------
model_year <- 1985:2012
projection_year <- 2013:2017

functional_groups <- c(
  "StripedBass0",
  "StripedBass2_5",
  "StripedBass6",
  "AtlanticMenhaden0",
  "AtlanticMenhaden1",
  "AtlanticMenhaden2",
  "AtlanticMenhaden3",
  "AtlanticMenhaden4",
  "AtlanticMenhaden5",
  "AtlanticMenhaden6",
  "SpinyDogfish",
  "BluefishJuvenile",
  "BluefishAdult",
  "WeakfishJuvenile",
  "WeakfishAdult",
  "AtlanticHerring0_1",
  "AtlanticHerring2",
  "Anchovies",
  "Benthos",
  "Zooplankton",
  "Phytoplankton",
  "Detritus"
)

age_name <- paste0("AtlanticMenhaden", 0:6)

biomass <- read_ewe_output(
  file_path = here::here("data", "ewe", "7ages", "ecosim_with_environmental_driver", "amo_pcp"),
  file_names = "biomass_monthly.csv",
  skip_nrows = 8,
  plot = FALSE,
  figure_titles = NULL,
  functional_groups = functional_groups,
  figure_colors = NULL
)

time_id <- seq(1, nrow(biomass[[1]]), by = 12)[1:length(model_year)]
biomass_ewe <- apply(biomass[[1]][, age_name], 1, sum)[time_id] * 1000000


# Case 0.1: default stock assessment run ----------------------------
sensitivity_run <- FALSE
sensitivity_plot <- FALSE
## DB-SRA is a method designed for determining a catch limit
## and management reference points for data-limited fisheries
## where catches are known from the beginning of exploitation.
## However, the catch data from the menhaden-like species case is not
## from the beginning of the exploitation.

# Populate the input data object

# Create a blank DLM object
ss_case0 <- new("Data")
# Change default area from 2 to 1
ss_case0@nareas <- 1
# Name of the case
ss_case0@Name <- "case0"
# Catch data
data_id <- as.numeric(names(sa_data$fishery$obs_total_catch_biomass$fleet1)) %in% model_year
ss_case0@Cat <- matrix(sa_data$fishery$obs_total_catch_biomass$fleet1[data_id],
  nrow = 1
)
# State units of catch
ss_case0@Units <- sa_data$fishery$units_info$units_biomass
# Years
ss_case0@Year <- model_year
# Depletion relative to unfished
# Use Catch 2015/Catch1985 will cause
ss_case0@Dep <- tail(ss_case0@Cat[1, ], n = 1) / ss_case0@Cat[1, 1] # 0.27

# VB maximum growth rate
ss_case0@vbK <- sa_data$biodata$k
# VB theoretical age at zero length
# default from EwE: -0.1
# https://www.researchgate.net/publication/267193103_Ecopath_with_Ecosim_A_User's_Guide#pf66
ss_case0@vbt0 <- sa_data$biodata$t0
# VB maximum length
# ss_case0@vbLinf <- (sa_data$biodata$winf * 1000 / sa_data$biodata$lw_a)^(1 / sa_data$biodata$lw_b)
ss_case0@vbLinf <- 500 # mm from FishBase
# Ratio of FMSY/M
# Q: Is it possible to find the ratio of FMSY to M
# for pelagic species in the Northwestern Atlantic Ocean?
# EwE FMSY values
fmsy <- c(
  0.092402786, 0.344614655, 1.101458788, 0.722086847,
  1.569404483, 0.988227546, 0.72328496
)

fmsy_m <- fmsy / sa_data$biodata$natural_mortality_matrix[1, ]

ss_case0@FMSY_M <- mean(fmsy_m) # 0.92

# BMSY relative to unfished
# Dick and MacCall (2011): use 0.4 if target biomass is 40% of unfished biomass
ss_case0@BMSY_B0 <- 0.3 # BAM FEC30% target

# Length at 50% maturity
age_maturity50 <- 2
ss_case0@L50 <- ss_case0@vbLinf *
  (1 - exp(-ss_case0@vbK *
    (age_maturity50 - ss_case0@vbt0)))

# Run DBSRA, DBSRA_40 and DBSRA4010
## DBSRA: Base Version. TAC is calculated assumed MSY harvest rate
## multiplied by the estimated current abundance (estimated B0 x Depletion)

## DBSRA_40: Same as the Base Version but assumes 40 percent current
## depletion (Bcurrent/B0 = 0.4), which is more or less the most
## optimistic state for a stock (i.e. very close to BMSY/B0 for many stocks).

## DBSRA4010: Base version paired with the 40-10 rule that linearly
## throttles back the TAC when depletion is below 0.4 down to zero at
## 10 percent of unfished biomass.

dbsra <- DLMtool::DBSRA(1, ss_case0, plot = TRUE)
# dbsra40 <- DLMtool::DBSRA_40(1, ss_case0, plot = TRUE)
# dbsra4010 <- DLMtool::DBSRA4010(1, ss_case0, plot = TRUE)

# Sensitivity runs
if (sensitivity_run) {
  altValue_list <- list(
    samples = 1:100,
    dep = seq(0.1, 0.9, by = 0.1),
    fmsy_m = c(0.1, 0.5, 1, 1.5, 2),
    bmsy_b0 = seq(0.1, 0.9, by = 0.1)
  )

  altValue_data <- do.call(expand.grid, altValue_list)
  altValue_data$dbsra_tac <-
    altValue_data$dbsra40_tac <-
    altValue_data$dbsra4010_tac <- NA

  id <- seq(1, nrow(altValue_data), by = 100)
  for (i in 1:length(id)) {
    ss_case <- ss_case0
    ss_case@Dep <- altValue_data$dep[id[i]]
    ss_case@FMSY_M <- altValue_data$fmsy_m[id[i]]
    ss_case@BMSY_B0 <- altValue_data$bmsy_b0[id[i]]

    altValue_data$dbsra_tac[id[i]:(id[i] + 99)] <- DBSRA(1, ss_case, plot = FALSE)@TAC
    altValue_data$dbsra40_tac[id[i]:(id[i] + 99)] <- DBSRA_40(1, ss_case, plot = FALSE)@TAC
    altValue_data$dbsra4010_tac[id[i]:(id[i] + 99)] <- DBSRA4010(1, ss_case, plot = FALSE)@TAC
  }
  save(altValue_data, file = here::here("Rscript", "data_poor_sensitivity_run.RData"))
} else {
  load(here::here("Rscript", "data_poor_sensitivity_run.RData"))
}

if (sensitivity_plot) {
  plot_dbsra <- ggplot(data = altValue_data, aes(x = dep, y = dbsra_tac, group = dep)) +
    geom_boxplot(aes(fill = dep)) +
    facet_grid(fmsy_m ~ bmsy_b0, labeller = label_both) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45))
  plot_dbsra

  plot_dbsra40 <- ggplot(data = altValue_data, aes(x = dep, y = dbsra40_tac, group = dep)) +
    geom_boxplot(aes(fill = dep)) +
    facet_grid(fmsy_m ~ bmsy_b0, labeller = label_both) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45))
  plot_dbsra40

  plot_dbsra4010 <- ggplot(data = altValue_data, aes(x = dep, y = dbsra4010_tac, group = dep)) +
    geom_boxplot(aes(fill = dep)) +
    facet_grid(fmsy_m ~ bmsy_b0, labeller = label_both) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45))
  plot_dbsra4010
}


# Projection: case 0.1 --------------------------------------------------
projection_output <- list()
for (i in 1:length(projection_year)) {
  ss_case <- ss_case0
  year <- model_year[1]:(projection_year[i] - 1)
  data_id <- as.numeric(names(sa_data$fishery$obs_total_catch_biomass$fleet1)) %in% year
  ss_case@Cat <- matrix(sa_data$fishery$obs_total_catch_biomass$fleet1[data_id],
    nrow = 1
  )
  ss_case@Year <- year
  #ss_case@Dep <- tail(ss_case@Cat[1, ], n = 1) / ss_case@Cat[1, 1]
  ss_case@Dep <- ss_case0@Dep
  projection_output[[i]] <- DLMtool::DBSRA_(
    x = 1,
    Data = ss_case,
    depo = NULL, # Optional fixed depletion (single value)
    hcr = NULL # Optional harvest control rule for throttling catch as a function of B/B0.
  )
}

# plot figures
par(mfrow=c(1,2))
ylim <- range(projection_output[[1]]$C_hist, unlist(sapply(projection_output, "[", "TAC")))
plot(c(model_year, projection_year),
  c(projection_output[[1]]$C_hist, rep(NA, length(projection_year))),
  type = "l",
  ylim = ylim,
  xlab = "Year", ylab = "Catch (mt)"
)

for (i in 1:length(projection_year)) {
  boxplot(projection_output[[i]]$TAC,
    add = TRUE,
    at = projection_year[i],
    col = "grey",
    width = 1,
    outline = TRUE,
    axes = FALSE
  )
}

catch_year <- projection_year[1:length(projection_year) - 1]
points(catch_year, sa_data$fishery$obs_total_catch_biomass$fleet1[names(sa_data$fishery$obs_total_catch_biomass$fleet1) %in% catch_year],
  pch = 16, col = "blue"
)

legend("top",
  c("Observed Catch", "Observed Catch for TAC estimates", "TAC"),
  lty = c(1, NA, NA),
  pch = c(NA, 16, NA),
  col = c("black", "blue", NA),
  fill = c(NA, NA, "gray"),
  border = c(NA, NA, "black"),
  bty = "n",
  title = "Case 0.1"
)

# plot biomass


dbsraB <- apply(projection_output[[1]]$Btrend, 2, median)
ylim <- range(biomass_ewe, dbsraB)
plot(model_year,
  biomass_ewe,
  xlab = "Year", ylab = "Biomass (mt)",
  ylim = ylim,
  pch = 16
)
lines(model_year, dbsraB)
legend("bottomright",
  c("EWE", "DBSRA"),
  bty = "n",
  pch = c(16, NA),
  lty = c(NA, 1),
  title = "Case 0.1"
)
```

- Case 0.2
    - Depletion relative to unfished: 0.9 based on ballpark values from EwE
    - $B_{MSY}$ relative to unfished: 0.3 (based on fecundity target value from Beaufort Stock Assessment report)
    
```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
# Case 0.2 ---------------------------
ss_case0@Dep <- 0.9

msy <- c(
 5.783313499, 5.83166065, 4.462390283, 4.322232771, 3.622124216, 4.401786498, 3.455276984
)

b0 <- 2000000

bmsy <- c(
 1.170854865, 1.180642591, 0.90342859, 0.875053021, 0.733313468, 0.891159071, 0.699534845
)*1000000

# BMSY relative to unfished
# Dick and MacCall (2011): use 0.4 if target biomass is 40% of unfished biomass
ss_case0@BMSY_B0 <- mean(bmsy/b0)

dbsra <- DLMtool::DBSRA(1, ss_case0, plot = TRUE)

# Projection: case 0.2 --------------------------------------------------
projection_output2 <- list()
for (i in 1:length(projection_year)) {
  ss_case <- ss_case0
  year <- model_year[1]:(projection_year[i] - 1)
  data_id <- as.numeric(names(sa_data$fishery$obs_total_catch_biomass$fleet1)) %in% year
  ss_case@Cat <- matrix(sa_data$fishery$obs_total_catch_biomass$fleet1[data_id],
    nrow = 1
  )
  ss_case@Year <- year
  #ss_case@Dep <- tail(ss_case@Cat[1, ], n = 1) / ss_case@Cat[1, 1]
  ss_case@Dep <- ss_case0@Dep
  projection_output2[[i]] <- DLMtool::DBSRA_(
    x = 1,
    Data = ss_case,
    depo = NULL, # Optional fixed depletion (single value)
    hcr = NULL # Optional harvest control rule for throttling catch as a function of B/B0.
  )
}

# plot figures
par(mfrow=c(1,2))
ylim <- range(projection_output2[[1]]$C_hist, unlist(sapply(projection_output2, "[", "TAC")))
plot(c(model_year, projection_year),
  c(projection_output2[[1]]$C_hist, rep(NA, length(projection_year))),
  type = "l",
  ylim = ylim,
  xlab = "Year", ylab = "Catch (mt)"
)

for (i in 1:length(projection_year)) {
  boxplot(projection_output2[[i]]$TAC,
    add = TRUE,
    at = projection_year[i],
    col = "grey",
    width = 1,
    outline = TRUE,
    axes = FALSE
  )
}

catch_year <- projection_year[1:length(projection_year) - 1]
points(catch_year, sa_data$fishery$obs_total_catch_biomass$fleet1[names(sa_data$fishery$obs_total_catch_biomass$fleet1) %in% catch_year],
  pch = 16, col = "blue"
)

legend("top",
  c("Observed Catch", "Observed Catch for TAC estimates", "TAC"),
  lty = c(1, NA, NA),
  pch = c(NA, 16, NA),
  col = c("black", "blue", NA),
  fill = c(NA, NA, "gray"),
  border = c(NA, NA, "black"),
  bty = "n",
  title = "Case 0.2"
)

# plot biomass
dbsraB <- apply(projection_output2[[1]]$Btrend, 2, median)
ylim <- range(biomass_ewe, dbsraB)
plot(model_year,
  biomass_ewe,
  xlab = "Year", ylab = "Biomass (mt)",
  ylim = ylim,
  pch = 16
)
lines(model_year, dbsraB)
legend("bottomright",
  c("EWE", "DBSRA"),
  bty = "n",
  pch = c(16, NA),
  lty = c(NA, 1),
  title = "Case 0.2"
)
```

## Cases 1-4 are based on the settings from case 0.1
    - Case 1: Link Atlantic Multidecadal Oscillation Index with menhaden biomass estimates and adjust projections: AMO is an indicator of climate conditions and would affect recruitment variability of menhaden-like species
    - Case 2: Link precipitation index with menhaden biomass estimates and adjust projections: precipitation alters availability of high-salinity habitat and may affect menhaden-like species through nutrient loading
    - Case 3: Link biomass of Striped bass from the EwE with menhaden biomass estimates and adjust projections because bass is a major predator
    - Case 4: Link dollars of menhaden with menhaden biomass estimates and adjust projections 

- Linear regression models from case 1 - 4
  - Using scaled or raw AMO and precipitation values do not make a difference. Here we used raw environmental values
  - The quantity of economic data for Atlantic menhaden is low. Here we used economic data for menhaden from New England, Middle Atlantic, and South Atlantic regions
  
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
# Projection: case 1 - include an index ---------------------------
menhaden_b <- apply(projection_output[[1]]$Btrend, 2, median)
year_id <- seq(1, nrow(amo_unsmooth_lag1), by = 12)[1:length(model_year)]

par(mfrow = c(2, 2))

amo_unsmooth_lag1 <- amo_unsmooth_lag1[year_id, ]
amo_lm <- lm(menhaden_b ~ amo_unsmooth_lag1$raw_value)
summary(amo_lm)
amo_fit <- fitted(amo_lm)

plot(amo_unsmooth_lag1$raw_value, menhaden_b,
  xlab = "AMO raw values",
  ylab = "Biomass of menhaden-like species"
)
lines(amo_unsmooth_lag1$raw_value, amo_fit, lty = 2, col = "blue")

# amo_lm_scaled <- lm(menhaden_b ~ amo_unsmooth_lag1$scaled_value)
# summary(amo_lm_scaled)
# amo_fit_scaled <- fitted(amo_lm_scaled)

# plot(amo_unsmooth_lag1$scaled_value, menhaden_b,
#      xlab = "AMO scaled values",
#      ylab = "Biomass of menhaden-like species"
# )
# lines(amo_unsmooth_lag1$scaled_value, amo_fit_scaled, lty = 2, col = "blue")

pcp <- precipitation[year_id, ]
pcp_lm <- lm(menhaden_b ~ pcp$raw_value)
summary(pcp_lm)
pcp_fit <- fitted(pcp_lm)

plot(pcp$raw_value, menhaden_b,
     xlab = "Precipitation raw values",
     ylab = "Biomass of menhaden-like species"
)
lines(pcp$raw_value, pcp_fit, lty = 2, col = "blue")

bass_bio <- bass_bio[bass_bio$Year %in% model_year, ]
bassB_lm <- lm(menhaden_b ~ bass_bio$bass_bio)
summary(bassB_lm)
bassB_fit <- fitted(bassB_lm)

plot(bass_bio$bass_bio, menhaden_b,
     xlab = "Biomass of Striped bass",
     ylab = "Biomass of menhaden-like species"
)
lines(bass_bio$bass_bio, bassB_fit, lty = 2, col = "blue")
# bassB_rlm <- MASS::rlm(menhaden_b ~ bass_b)
# summary(MASS::rlm(menhaden_b ~ bass_b, resid = bassB_rlm$residuals, weight = bassB_rlm$weights))

# sub_menhaden_b <- menhaden_b[model_year %in% atlantic_menhaden_dollars$Year]
# sub_atlantic_menhaden_dollars <- atlantic_menhaden_dollars$Dollars[atlantic_menhaden_dollars$Year %in% model_year]
# dollars_lm <- lm(sub_menhaden_b ~ sub_atlantic_menhaden_dollars)
# summary(dollars_lm)
# dollars_fit <- fitted(dollars_lm)
#
# plot(sub_atlantic_menhaden_dollars, sub_menhaden_b,
#      xlab = "Atlantic menhaden dollars",
#      ylab = "Biomass of menhaden-like species"
# )
# lines(sub_atlantic_menhaden_dollars, dollars_fit, lty = 2, col = "blue")

sub_menhaden_b <- menhaden_b[model_year %in% menhaden_dollars$Year]
sub_menhaden_dollars <- menhaden_dollars$Dollars[menhaden_dollars$Year %in% model_year]
dollars_lm <- lm(sub_menhaden_b ~ sub_menhaden_dollars)
summary(dollars_lm)
dollars_fit <- fitted(dollars_lm)

plot(sub_menhaden_dollars, sub_menhaden_b,
     xlab = "Menhaden dollars",
     ylab = "Biomass of menhaden-like species"
)
lines(sub_menhaden_dollars, dollars_fit, lty = 2, col = "blue")
```

## Status of indicators from cases 1 - 4
```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
# status of indicators --------------------------------------------


IS <- function(indicator_data, slope) {
  min_val <- min(indicator_data)
  max_val <- max(indicator_data)

  if (slope > 0) IS <- (indicator_data - min_val) / (max_val - min_val)
  if (slope < 0) IS <- 1 - (indicator_data - min_val) / (max_val - min_val)

  return(IS)
}

amo_IS <- IS(
  indicator_data = amo_unsmooth_lag1$raw_value,
  slope = coef(amo_lm)[2]
)

pcp_IS <- IS(
  indicator_data = pcp$raw_value,
  slope = coef(pcp_lm)[2]
)

bassB_IS <- IS(
  indicator_data = bass_bio$bass_bio,
  slope = coef(bassB_lm)[2]
)

dollars_IS <- IS(
  indicator_data = sub_menhaden_dollars,
  slope = coef(dollars_lm)[2]
)

par(mfrow = c(1, 2))

scaled_data <- data.frame(
  menhaden_b = scale(menhaden_b)[,1],
  amo = scale(amo_unsmooth_lag1$raw_value)[,1],
  pcp = scale(pcp$raw_value)[,1],
  bass_b = scale(bass_bio$bass_bio)[,1],
  dollars = scale(sub_menhaden_dollars)[,1]
)

plot(model_year, scaled_data$amo,
     ylim = range(scaled_data),
     type = "l", lty = 1,
     xlab = "Year", ylab = "Scaled Indices")
lines(model_year, scaled_data$pcp, lty = 2, col = 2)
lines(model_year, scaled_data$bass_b, lty=3, col = 3)
lines(model_year, scaled_data$dollars, lty = 4, col= 4)
lines(model_year, scaled_data$menhaden_b, lty = 5, col= 5)
legend("bottomright",
       c(
         "AMO",
         "Precipitation",
         "Striped bass biomass",
         "Menhaden dollars",
         "Menhaden-like species biomass"
       ),
       lty = 1:5,
       col = 1:5,
       bty = "n"
)


plot(model_year, amo_IS,
     type = "l", lty = 1,
     xlab = "Year", ylab = "Status of Indicators"
)
lines(model_year, pcp_IS, lty = 2, col = 2)
lines(model_year, bassB_IS, lty=3, col = 3)
lines(model_year, dollars_IS, lty = 4, col= 4)
legend("bottomright",
       c(
         "AMO",
         "Precipitation",
         "Striped bass biomass",
         "Menhaden dollars"
       ),
       lty = 1:4,
       col = 1:4,
       bty = "n"
)
```

## Adjusted TAC in 2013 from cases 1 - 4
```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
# Adjust TAC based on estimated TAC, IS, and Bt/BMSY values
adjust_tac <- function(tac, IS, Bt_BMSY) {
  tac_lower <- min(tac)
  tac_upper <- max(tac)
  adjust_tac <- c()

  for (i in 1:length(tac)) {
    if (Bt_BMSY[i] > 1) adjust_tac[i] <- tac_lower + IS * (tac_upper - tac_lower)
    if (Bt_BMSY[i] <= 1 & Bt_BMSY[i] > 0.5) adjust_tac[i] <- IS * Bt_BMSY[i] * tac[i]
    if (Bt_BMSY[i] <= 0.5) adjust_tac[i] <- 0
  }

  return(adjust_tac)
}



Bt_BMSY <- projection_output[[1]]$Bt_Kstore / projection_output[[1]]$BMSY_K_Mstore

amo_tac <- adjust_tac(
  tac = projection_output[[1]]$TAC,
  IS = tail(amo_IS, n = 1),
  Bt_BMSY = Bt_BMSY
)
pcp_tac <- adjust_tac(
  tac = projection_output[[1]]$TAC,
  IS = tail(pcp_IS, n = 1),
  Bt_BMSY = Bt_BMSY
)
bassB_tac <- adjust_tac(
  tac = projection_output[[1]]$TAC,
  IS = tail(bassB_IS, n = 1),
  Bt_BMSY = Bt_BMSY
)
dollars_tac <- adjust_tac(
  tac = projection_output[[1]]$TAC,
  IS = tail(dollars_IS, n = 1),
  Bt_BMSY = Bt_BMSY
)

ylim <- range(projection_output[[1]]$TAC,
              bassB_tac, amo_tac,
              pcp_tac, dollars_tac)
plot(projection_output[[1]]$TAC,
  type = "l", lty = 1,
  ylim = ylim,
  xlab = "Iterations", ylab = "TAC"
)

lines(amo_tac, lty = 2, col = 2)
lines(pcp_tac, lty = 3, col = 3)
lines(bassB_tac, lty = 4, col = 4)
lines(dollars_tac, lty = 5, col = 5)

legend("topleft",
  c("DB-SRA TAC",
    "Adjusted TAC 1",
    "Adjusted TAC 2",
    "Adjusted TAC 3",
    "Adjusted TAC 4"),
  lty = 1:5,
  col = 1:5,
  bty = "n"
)


boxplot(projection_output[[1]]$TAC,
        bassB_tac,
        amo_tac,
        pcp_tac,
        dollars_tac,

  names = c("DB-SRA TAC",
            "TAC 1",
            "TAC 2",
            "TAC 3",
            "TAC 4"
            ),
  ylab = "TAC"
)




```
