---
title: 'Data-moderate stock assessment'
date: 'Updated on May 12, 2022'
output:
  html_document: 
    code_folding: hide
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Just Another Bayesian Biomass Assessment (JABBA)

- Website: [https://github.com/jabbamodel/JABBA](https://github.com/jabbamodel/JABBA)
- Version: commit d73313debf9326f2be920846ee361b3dcca8c22d

```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
devtools::load_all()

# Install required R packages -------------------------------------
required_pkg <- c(
  "devtools", "here", "gplots",
  "coda", "rjags", "R2jags",
  "fitdistrplus", "reshape",
  "ggplot2", "reshape2"
)

pkg_to_install <- required_pkg[!(required_pkg %in%
  installed.packages()[, "Package"])]
if (length(pkg_to_install)) install.packages(pkg_to_install)

lapply(required_pkg, library, character.only = TRUE)

devtools::install_github("jabbamodel/JABBA",
  ref = "d73313debf9326f2be920846ee361b3dcca8c22d"
)

library(JABBA)

```

## Case 0: stock assessment base run

  - Case 0.1: K = 6500000, r = 0.6 with large CV 
  - Case 0.2: K = 4000000, r = 0.8 with small CV (update input values based on known ballpark values from EwE)
  
```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
# Load simulated input data
source(here::here("Rscript", "simulation.R"))
source(here::here("Rscript", "load_indices.R"))


# Load EwE biomass data
functional_groups <- c(
  "StripedBass0",
  "StripedBass2_5",
  "StripedBass6",
  "AtlanticMenhaden0",
  "AtlanticMenhaden1",
  "AtlanticMenhaden2",
  "AtlanticMenhaden3",
  "AtlanticMenhaden4",
  "AtlanticMenhaden5",
  "AtlanticMenhaden6",
  "SpinyDogfish",
  "BluefishJuvenile",
  "BluefishAdult",
  "WeakfishJuvenile",
  "WeakfishAdult",
  "AtlanticHerring0_1",
  "AtlanticHerring2",
  "Anchovies",
  "Benthos",
  "Zooplankton",
  "Phytoplankton",
  "Detritus"
)

age_name <- paste0("AtlanticMenhaden", 0:6)

biomass <- read_ewe_output(
  file_path = here::here("data", "ewe", "7ages", "ecosim_with_environmental_driver", "amo_pcp"),
  file_names = "biomass_monthly.csv",
  skip_nrows = 8,
  plot = FALSE,
  figure_titles = NULL,
  functional_groups = functional_groups,
  figure_colors = NULL
)

time_id <- seq(1, nrow(biomass[[1]]), by = 12)
biomass_ewe <- apply(biomass[[1]][, age_name], 1, sum) * 1000000
# Set up JABBA base case assessment

model_year <- 1985:2012
projection_year <- 2013:2017
output_dir <- here::here("data", "data_moderate")

# case 0.1: K and r with large CV
ss_case01_input <- generate_jabba(
  assessment_name = "case01",
  output_dir = output_dir,
  sa_data = sa_data,
  model_year = model_year,
  projection_year = projection_year
)

ss_case01 <- JABBA::fit_jabba(
  jbinput = ss_case01_input,
  save.jabba = TRUE,
  save.all = TRUE,
  save.prj = TRUE,
  output.dir = output_dir,
  save.csvs = T
)


# Plot figures using JABBA
JABBA::jabba_plots(jabba = ss_case01, output.dir = output_dir)
# plot with CIs (80% for projections)
# JABBA::jbplot_prj(ss_case01, type = "BBmsy", output.dir = output_dir)
# JABBA::jbplot_prj(ss_case01, type = "BB0", output.dir = output_dir)
# JABBA::jbplot_prj(ss_case01, type = "FFmsy", output.dir = output_dir)

# case 0.2: K and r with small CV and update K based on true biomass from EwE
ss_case02_input <- ss_case01_input
ss_case02_input$settings$assessment <- "case02"
ss_case02_input$jagsdata$K.pr <- c(4000000, sqrt(log(0.3^2 + 1)))
ss_case02_input$jagsdata$r.pr <- c(0.8, 0.1)

ss_case02 <- JABBA::fit_jabba(
  jbinput = ss_case02_input,
  save.jabba = TRUE,
  save.all = TRUE,
  save.prj = TRUE,
  output.dir = output_dir,
  save.csvs = T
)

# Plot figures using JABBA
JABBA::jabba_plots(jabba = ss_case02, output.dir = output_dir)
# plot with CIs (80% for projections)
# JABBA::jbplot_prj(ss_case01, type = "BBmsy")
# JABBA::jbplot_prj(ss_case01, type = "BB0")
# JABBA::jbplot_prj(ss_case01, type = "FFmsy")

# Plot figures for cases 0.1 and 0.2 ----------------------------------------------------

fmsy01 <- rep(ss_case01$posteriors$Hmsy, times = (length(projection_year) + 1) * length(ss_case01_input$jagsdata$TAC[1, ]))
ss_case01$prj_posterior$f <- ss_case01$prj_posterior$harvest * fmsy01

fmsy02 <- rep(ss_case01$posteriors$Hmsy, times = (length(projection_year) + 1) * length(ss_case01_input$jagsdata$TAC[1, ]))
ss_case02$prj_posterior$f <- ss_case02$prj_posterior$harvest * fmsy02

bmsy01 <- rep(ss_case01$posteriors$SBmsy, times = (length(projection_year) + 1) * length(ss_case01_input$jagsdata$TAC[1, ]))
ss_case01$prj_posterior$biomass <- ss_case01$prj_posterior$stock * bmsy01

bmsy02 <- rep(ss_case02$posteriors$SBmsy, times = (length(projection_year) + 1) * length(ss_case02_input$jagsdata$TAC[1, ]))
ss_case02$prj_posterior$biomass <- ss_case02$prj_posterior$stock * bmsy02

# plot biomass over time
par(mfrow = c(1, 2))
ylim <- range(
  biomass_ewe[time_id],
  ss_case01$timeseries[, "mu", "B"],
  ss_case02$timeseries[, "mu", "B"]
)
plot(c(model_year, projection_year),
  biomass_ewe[time_id],
  xlab = "Year", ylab = "Biomass (mt)",
  ylim = ylim,
  pch = 16
)
lines(model_year, ss_case01$timeseries[, "mu", "B"])
lines(model_year, ss_case02$timeseries[, "mu", "B"], col = 2, lty = 2)
legend("bottomright",
  c("EWE", "JABBA case 0.1", "JABBA case 0.2"),
  bty = "n",
  pch = c(16, NA, NA),
  lty = c(NA, 1, 2),
  col = c(1, 1, 2)
)

ylim <- range(
  biomass_ewe[time_id],
  ss_case01$timeseries[, , "B"],
  ss_case02$timeseries[, , "B"]
)
plot(c(model_year, projection_year),
  biomass_ewe[time_id],
  xlab = "Year", ylab = "Biomass (mt)",
  ylim = ylim,
  pch = 16
)

lines(model_year, ss_case01$timeseries[, "mu", "B"])
lines(model_year, ss_case01$timeseries[, "lci", "B"], lty = 2)
lines(model_year, ss_case01$timeseries[, "uci", "B"], lty = 2)

lines(model_year, ss_case02$timeseries[, "mu", "B"], col = 2)
lines(model_year, ss_case02$timeseries[, "lci", "B"], lty = 2, col = 2)
lines(model_year, ss_case02$timeseries[, "uci", "B"], lty = 2, col = 2)

# Plot biomass based on last year of catch
for (i in 1:length(projection_year)) {
  subdata_id <- (ss_case02$prj_posterior$year == projection_year[i]) & (ss_case02$prj_posterior$tac %in% tail(ss_case02_input$data$catch$Total, n = 1))

  boxplot(ss_case02$prj_posterior$biomass[subdata_id],
    add = TRUE,
    at = projection_year[i],
    col = "red",
    width = 1,
    outline = TRUE,
    axes = FALSE
  )
}

# mortality
mortality <- read_ewe_output(
  file_path = here::here("data", "ewe", "7ages", "ecosim_with_environmental_driver", "amo_pcp"),
  file_names = "mortality_monthly.csv",
  skip_nrows = 8,
  plot = FALSE,
  figure_titles = NULL,
  functional_groups = functional_groups,
  figure_colors = NULL
)
mortality_ewe <- apply(mortality[[1]][, age_name], 1, max)

mortality <- read.csv(file = here::here("data", "ewe", "7ages", "updated_faa.csv"))
mortality_ewe <- apply(mortality[, 2:ncol(mortality)], 1, max)

par(mfrow = c(1, 1), mar = c(4, 4, 1, 4))
plot(c(model_year, projection_year),
  #mortality_ewe[time_id],
  mortality_ewe,
  xlab = "Year", ylab = "EwE Apical F",
  pch = 16
)
par(new = TRUE)
ylim <- range(ss_case01$timeseries[, "mu", "F"], ss_case02$timeseries[, "mu", "F"])
plot(model_year, ss_case01$timeseries[, "mu", "F"],
  type = "l", axes = FALSE, lty = 1,
  bty = "n", xlab = "", ylab = ""
)
lines(model_year, ss_case02$timeseries[, "mu", "F"], lty = 2, col = 2)
axis(side = 4, at = pretty(ylim))
mtext("JABBA F", side = 4, line = 2)
legend("topright",
  c("EWE", "JABBA case 0.1", "JABBA case 0.2"),
  bty = "n",
  pch = c(16, NA, NA),
  lty = c(NA, 1, 2),
  col = c(1, 1, 2)
)
```


## Cases 1-4 are based on the settings from case 0.2
    - Case 1: Link Atlantic Multidecadal Oscillation Index with menhaden biomass estimates and adjust projections: AMO is an indicator of climate conditions and would affect recruitment variability of menhaden-like species
    - Case 2: Link precipitation index with menhaden biomass estimates and adjust projections: precipitation alters availability of high-salinity habitat and may affect menhaden-like species through nutrient loading
    - Case 3: Link biomass of Striped bass from the EwE with menhaden biomass estimates and adjust projections because bass is a major predator
    - Case 4: Link dollars of menhaden with menhaden biomass estimates and adjust projections 

- Linear regression models from case 1 - 4
  - Using scaled or raw AMO and precipitation values do not make a difference. Here we used raw environmental values
  - The quantity of economic data for Atlantic menhaden is low. Here we used economic data for menhaden from New England, Middle Atlantic, and South Atlantic regions
  
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
# Projection: case 1 - include an index ---------------------------
menhaden_b <- ss_case02$timeseries[, "mu", "B"]
year_id <- seq(1, nrow(amo_unsmooth_lag1), by = 12)[1:length(model_year)]

par(mfrow = c(2, 2))

amo_unsmooth_lag1 <- amo_unsmooth_lag1[year_id, ]
amo_lm <- lm(menhaden_b ~ amo_unsmooth_lag1$raw_value)
summary(amo_lm)
amo_fit <- fitted(amo_lm)

plot(amo_unsmooth_lag1$raw_value, menhaden_b,
     xlab = "AMO raw values",
     ylab = "Biomass of menhaden-like species"
)
lines(amo_unsmooth_lag1$raw_value, amo_fit, lty = 2, col = "blue")

pcp <- precipitation[year_id, ]
pcp_lm <- lm(menhaden_b ~ pcp$raw_value)
summary(pcp_lm)
pcp_fit <- fitted(pcp_lm)

plot(pcp$raw_value, menhaden_b,
     xlab = "Precipitation raw values",
     ylab = "Biomass of menhaden-like species"
)
lines(pcp$raw_value, pcp_fit, lty = 2, col = "blue")

bass_bio <- bass_bio[bass_bio$Year %in% model_year, ]
bassB_lm <- lm(menhaden_b ~ bass_bio$bass_bio)
summary(bassB_lm)
bassB_fit <- fitted(bassB_lm)

plot(bass_bio$bass_bio, menhaden_b,
     xlab = "Biomass of Striped bass",
     ylab = "Biomass of menhaden-like species"
)
lines(bass_bio$bass_bio, bassB_fit, lty = 2, col = "blue")
# bassB_rlm <- MASS::rlm(menhaden_b ~ bass_b)
# summary(MASS::rlm(menhaden_b ~ bass_b, resid = bassB_rlm$residuals, weight = bassB_rlm$weights))

# sub_menhaden_b <- menhaden_b[model_year %in% atlantic_menhaden_dollars$Year]
# sub_atlantic_menhaden_dollars <- atlantic_menhaden_dollars$Dollars[atlantic_menhaden_dollars$Year %in% model_year]
# dollars_lm <- lm(sub_menhaden_b ~ sub_atlantic_menhaden_dollars)
# summary(dollars_lm)
# dollars_fit <- fitted(dollars_lm)
#
# plot(sub_atlantic_menhaden_dollars, sub_menhaden_b,
#      xlab = "Atlantic menhaden dollars",
#      ylab = "Biomass of menhaden-like species"
# )
# lines(sub_atlantic_menhaden_dollars, dollars_fit, lty = 2, col = "blue")

sub_menhaden_b <- menhaden_b[model_year %in% menhaden_dollars$Year]
sub_menhaden_dollars <- menhaden_dollars$Dollars[menhaden_dollars$Year %in% model_year]
dollars_lm <- lm(sub_menhaden_b ~ sub_menhaden_dollars)
summary(dollars_lm)
dollars_fit <- fitted(dollars_lm)

plot(sub_menhaden_dollars, sub_menhaden_b,
     xlab = "Menhaden dollars",
     ylab = "Biomass of menhaden-like species"
)
lines(sub_menhaden_dollars, dollars_fit, lty = 2, col = "blue")

# status of indicators --------------------------------------------

amo_soi <- calc_soi(
  indicator_data = amo_unsmooth_lag1$raw_value,
  slope = coef(amo_lm)[2]
)

pcp_soi <- calc_soi(
  indicator_data = pcp$raw_value,
  slope = coef(pcp_lm)[2]
)

bassB_soi <- calc_soi(
  indicator_data = bass_bio$bass_bio,
  slope = coef(bassB_lm)[2]
)

dollars_soi <- calc_soi(
  indicator_data = sub_menhaden_dollars,
  slope = coef(dollars_lm)[2]
)

scaled_data <- data.frame(
  year = model_year,
  amo = scale(amo_unsmooth_lag1$raw_value)[,1],
  pcp = scale(pcp$raw_value)[,1],
  bassB = scale(bass_bio$bass_bio)[,1],
  dollars = scale(sub_menhaden_dollars)[,1],
  menhadenB = scale(menhaden_b)[,1]
)

scaled_data_melt <- reshape2::melt(
  scaled_data,
  id = "year"
)

ggplot(scaled_data_melt, aes(x = year, y = value, color = variable)) +
  geom_line() +
  facet_wrap(~variable, scales = "free_y") +
  labs(
    title = "Scaled Indices",
    x = "Year",
    y = "Scaled Indices"
  ) +
  theme_bw()

soi_data <- data.frame(
  year = model_year,
  amo = amo_soi,
  pcp = pcp_soi,
  bass_b = bassB_soi,
  dollars = dollars_soi
)

soi_data_melt <- reshape2::melt(
  soi_data,
  id = "year"
)

ggplot(soi_data_melt, aes(x = year, y = value, color = variable)) +
  geom_line() +
  facet_wrap(~variable, scales = "free_y") +
  labs(
    title = "Status of Indicators",
    x = "Year",
    y = "Status of Indicators"
  ) +
  theme_bw()

```

## Adjusted FMSY for cases 1 - 4
```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
# Adjust FMSY based on estimated FMSY, soi, and Bt/BMSY values -------

# 2012 Bt_BMSY
Bt_BMSY <- ss_case02$posteriors$BtoBmsy[, length(model_year)]

amo_fmsy <- adjust_projection_jabba(
  FMSY = ss_case02$refpts_posterior$Fmsy,
  soi = tail(amo_soi, n = 1),
  Bt_BMSY = Bt_BMSY
)
pcp_fmsy <- adjust_projection_jabba(
  FMSY = ss_case02$refpts_posterior$Fmsy,
  soi = tail(pcp_soi, n = 1),
  Bt_BMSY = Bt_BMSY
)
bassB_fmsy <- adjust_projection_jabba(
  FMSY = ss_case02$refpts_posterior$Fmsy,
  soi = tail(bassB_soi, n = 1),
  Bt_BMSY = Bt_BMSY
)
dollars_fmsy <- adjust_projection_jabba(
  FMSY = ss_case02$refpts_posterior$Fmsy,
  soi = tail(dollars_soi, n = 1),
  Bt_BMSY = Bt_BMSY
)

fmsy_data <- data.frame(
  iter = 1:length(amo_fmsy),
  JABBA = ss_case02$refpts_posterior$Fmsy,
  amo = amo_fmsy,
  pcp = pcp_fmsy,
  bassB = bassB_fmsy,
  dollars = dollars_fmsy
)

fmsy_data_melt <- reshape2::melt(
  fmsy_data,
  id = "iter"
)

ggplot(fmsy_data_melt, aes(x = iter, y = value, color = variable)) +
  geom_line() +
  facet_wrap(~variable) +
  labs(
    title = "FMSY",
    x = "Iteration",
    y = "FMSY"
  ) +
  theme_bw()

ggplot(fmsy_data_melt, aes(x=variable, y = value, fill = variable)) +
  geom_boxplot()+
  labs(
    title = "FMSY",
    x = "",
    y = "FMSY"
  ) +
  theme_bw()


```
