---
title: 'Data-moderate stock assessment'
date: 'Updated on June 21, 2022'
output:
  html_document: 
  code_folding: hide
word_document: default
---
  
  ```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Just Another Bayesian Biomass Assessment (JABBA)

- Website: [https://github.com/jabbamodel/JABBA](https://github.com/jabbamodel/JABBA)
- Version: commit d73313debf9326f2be920846ee361b3dcca8c22d

```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
devtools::load_all()

# Install required R packages -------------------------------------
required_pkg <- c(
  "devtools", "here", "gplots",
  "coda", "rjags", "R2jags",
  "fitdistrplus", "reshape",
  "ggplot2", "reshape2"
)

pkg_to_install <- required_pkg[!(required_pkg %in%
                                   installed.packages()[, "Package"])]
if (length(pkg_to_install)) install.packages(pkg_to_install)

lapply(required_pkg, library, character.only = TRUE)

devtools::install_github("jabbamodel/JABBA",
                         ref = "d73313debf9326f2be920846ee361b3dcca8c22d"
)

library(JABBA)

```

## Case 0: stock assessment base run
- Case 0: K = 4000000, r = 0.8 with small CV (update input values based on known ballpark values from EwE)

```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
# Load simulated input data
source(here::here("Rscript", "simulation.R"))
source(here::here("Rscript", "load_indices.R"))

# Load EwE biomass data
functional_groups <- c(
  "StripedBass0",
  "StripedBass2_5",
  "StripedBass6",
  "AtlanticMenhaden0",
  "AtlanticMenhaden1",
  "AtlanticMenhaden2",
  "AtlanticMenhaden3",
  "AtlanticMenhaden4",
  "AtlanticMenhaden5",
  "AtlanticMenhaden6",
  "SpinyDogfish",
  "BluefishJuvenile",
  "BluefishAdult",
  "WeakfishJuvenile",
  "WeakfishAdult",
  "AtlanticHerring0_1",
  "AtlanticHerring2",
  "Anchovies",
  "Benthos",
  "Zooplankton",
  "Phytoplankton",
  "Detritus"
)

age_name <- paste0("AtlanticMenhaden", 0:6)

biomass <- read_ewe_output(
  file_path = here::here("data", "ewe", "7ages", "ecosim_with_environmental_driver", "amo_pcp"),
  file_names = "biomass_monthly.csv",
  skip_nrows = 8,
  plot = FALSE,
  figure_titles = NULL,
  functional_groups = functional_groups,
  figure_colors = NULL
)

time_id <- seq(1, nrow(biomass[[1]]), by = 12)
biomass_ewe <- apply(biomass[[1]][, age_name], 1, sum) * 1000000
# Set up JABBA base case assessment

model_year <- 1985:2012
projection_year <- 2013:2017
output_dir <- here::here("data", "data_moderate")

# case 0.1: K and r with large CV
ss_case0_input <- generate_jabba(
  assessment_name = "case0",
  output_dir = output_dir,
  sa_data = sa_data,
  model_year = model_year,
  projection_year = projection_year
)

ss_case0_input$jagsdata$K.pr <- c(4000000, sqrt(log(0.3^2 + 1)))
ss_case0_input$jagsdata$r.pr <- c(0.8, 0.1)

ss_case0 <- JABBA::fit_jabba(
  jbinput = ss_case0_input,
  save.jabba = TRUE,
  save.all = TRUE,
  save.prj = TRUE,
  output.dir = output_dir,
  save.csvs = T
)

# Plot figures using JABBA
JABBA::jabba_plots(jabba = ss_case0, output.dir = output_dir)
# # plot with CIs (80% for projections)
# JABBA::jbplot_prj(ss_case0, type = "BBmsy", output.dir = output_dir)
# JABBA::jbplot_prj(ss_case0, type = "BB0", output.dir = output_dir)
# JABBA::jbplot_prj(ss_case0, type = "FFmsy", output.dir = output_dir)

# Plot figures for cases 0.1 and 0.2 ----------------------------------------------------

fmsy0 <- rep(ss_case0$posteriors$Hmsy, times = (length(projection_year) + 1) * length(ss_case0_input$jagsdata$TAC[1, ]))
ss_case0$prj_posterior$f <- ss_case0$prj_posterior$harvest * fmsy0

bmsy0 <- rep(ss_case0$posteriors$SBmsy, times = (length(projection_year) + 1) * length(ss_case0_input$jagsdata$TAC[1, ]))
ss_case0$prj_posterior$biomass <- ss_case0$prj_posterior$stock * bmsy0

# plot biomass over time
par(mfrow = c(1, 2))
ylim <- range(
  biomass_ewe[time_id],
  ss_case0$timeseries[, "mu", "B"]
)
plot(c(model_year, projection_year),
     biomass_ewe[time_id],
     xlab = "Year", ylab = "Biomass (mt)",
     ylim = ylim,
     pch = 16
)
lines(model_year, ss_case0$timeseries[, "mu", "B"])
legend("bottomright",
       c("EWE", "JABBA case 0"),
       bty = "n",
       pch = c(16, NA, NA),
       lty = c(NA, 1, 2),
       col = c(1, 1, 2)
)

ylim <- range(
  biomass_ewe[time_id],
  ss_case0$timeseries[, , "B"]
)
plot(c(model_year, projection_year),
     biomass_ewe[time_id],
     xlab = "Year", ylab = "Biomass (mt)",
     ylim = ylim,
     pch = 16
)

lines(model_year, ss_case0$timeseries[, "mu", "B"])
lines(model_year, ss_case0$timeseries[, "lci", "B"], lty = 2)
lines(model_year, ss_case0$timeseries[, "uci", "B"], lty = 2)

# Plot biomass based on last year of catch
for (i in 1:length(projection_year)) {
  subdata_id <- (ss_case0$prj_posterior$year == projection_year[i]) & (ss_case0$prj_posterior$tac %in% tail(ss_case0_input$data$catch$Total, n = 1))
  
  boxplot(ss_case0$prj_posterior$biomass[subdata_id],
          add = TRUE,
          at = projection_year[i],
          col = "gray",
          width = 1,
          outline = TRUE,
          axes = FALSE
  )
}

# mortality
mortality <- read_ewe_output(
  file_path = here::here("data", "ewe", "7ages", "ecosim_with_environmental_driver", "amo_pcp"),
  file_names = "mortality_monthly.csv",
  skip_nrows = 8,
  plot = FALSE,
  figure_titles = NULL,
  functional_groups = functional_groups,
  figure_colors = NULL
)
mortality_ewe <- apply(mortality[[1]][, age_name], 1, max)

mortality <- read.csv(file = here::here("data", "ewe", "7ages", "updated_faa.csv"))
mortality_ewe_apical <- apply(mortality[, 2:ncol(mortality)], 1, max)
mortality_ewe_average <- apply(mortality[, 2:ncol(mortality)], 1, mean)

par(mfrow = c(1, 1))
ylim <- range(mortality_ewe_apical, 
              mortality_ewe_average,
              ss_case0$timeseries[, "mu", "F"])
plot(c(model_year, projection_year),
     #mortality_ewe[time_id],
     mortality_ewe_apical,
     type = "o",
     xlab = "Year", ylab = "F",
     pch = 1,
     col = 1,
     lty = 1,
     ylim = ylim
)
lines(c(model_year, projection_year), mortality_ewe_average, 
      pch = 2, type = "o", lty = 2, col = 2)
lines(model_year, ss_case0$timeseries[, "mu", "F"], lty = 3, col =3)
legend("topright",
       c("EwE Apical F", "EwE Average F", "JABBA F"),
       bty = "n",
       pch = c(1, 2, NA),
       lty = 1:3,
       col = 1:3
)
```


## Cases 1-4 are based on the settings from case 0
- Case 1: Link Atlantic Multidecadal Oscillation Index with menhaden biomass estimates and adjust projections: AMO is an indicator of climate conditions and would affect recruitment variability of menhaden-like species
- Case 2: Link precipitation index with menhaden biomass estimates and adjust projections: precipitation alters availability of high-salinity habitat and may affect menhaden-like species through nutrient loading
- Case 3: Link biomass of Striped bass from the EwE with menhaden biomass estimates and adjust projections because bass is a major predator
- Case 4: Link price of menhaden with menhaden biomass estimates and adjust projections 

- Linear regression models from case 1 - 4
- True biomass of menhaden-like species as functions of AMO, precipitation, biomass of striped bass, and price of menhaden

### Status of indicators (SOI)

- If stock-indicator relationship is positive, $SOI_{y} = \frac{I_{y}-I_{y}^{min}}{I_{y}^{max}-I_{y}^{min}}$
  
  - If stock-indicator relationship is negative, $SOI_{y} = 1-\frac{I_{y}-I_{y}^{min}}{I_{y}^{max}-I_{y}^{min}}$
  
  where $I_{y}$ represents indicator value in year y. $I_{y}^{min}$ and $I_{y}^{max}$ represent the minimum and maximum values of $I$ from the time series.

```{r,  echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}

lm_slope <- data.frame(
  case = "True indices",
  amo = NA,
  pcp = NA,
  bassB = NA,
  price = NA
)

year_id <- seq(1, nrow(amo_unsmooth_lag1), by = 12)
index_year <- c(model_year, projection_year)

amo <- amo_unsmooth_lag1[year_id, ]
amo_lm <- lm(biomass_ewe[time_id] ~ amo$raw_value)
amo_fit <- fitted(amo_lm)
lm_slope$amo <- paste0(
  round(summary(amo_lm)$coefficients[2, 1], digits = 2),
  if(summary(amo_lm)$coefficients[2, 4] <= 0.05) {"*"})

pcp <- precipitation[year_id, ]
pcp_lm <- lm(biomass_ewe[time_id] ~ pcp$raw_value)
pcp_fit <- fitted(pcp_lm)
lm_slope$pcp <- paste0(
  round(summary(pcp_lm)$coefficients[2, 1], digits = 2),
  if(summary(pcp_lm)$coefficients[2, 4] <= 0.05) {"*"})

bassB <- bass_bio[bass_bio$Year %in% index_year, ]
bassB_lm <- lm(biomass_ewe[time_id] ~ bassB$bass_bio)
bassB_fit <- fitted(bassB_lm)
lm_slope$bassB <- paste0(
  round(summary(bassB_lm)$coefficients[2, 1], digits = 2),
  if(summary(bassB_lm)$coefficients[2, 4] <= 0.05) {"*"})

sub_menhadenP <- menhaden_price$Inflation.Adjust.Price.Per.MT[menhaden_price$Year %in% index_year]
price_lm <- lm(biomass_ewe[time_id] ~ sub_menhadenP)
price_fit <- fitted(price_lm)
lm_slope$price <- paste0(
  round(summary(price_lm)$coefficients[2, 1], digits = 2),
  if(summary(price_lm)$coefficients[2, 4] <= 0.05) {"*"})

par(mfrow = c(2, 2))

plot(amo$raw_value, biomass_ewe[time_id],
     xlab = "AMO raw values",
     ylab = "Biomass of menhaden-like species from OM"
)
lines(amo$raw_value, amo_fit, lty = 2, col = "blue")

plot(pcp$raw_value, biomass_ewe[time_id],
     xlab = "Precipitation raw values",
     ylab = "Biomass of menhaden-like species from OM"
)
lines(pcp$raw_value, pcp_fit, lty = 2, col = "blue")

plot(bassB$bass_bio, biomass_ewe[time_id],
     xlab = "Biomass of Striped bass",
     ylab = "Biomass of menhaden-like species from OM"
)
lines(bassB$bass_bio, bassB_fit, lty = 2, col = "blue")

plot(sub_menhadenP, biomass_ewe[time_id],
     xlab = "Menhaden price",
     ylab = "Biomass of menhaden-like species from OM"
)
lines(sub_menhadenP, price_fit, lty = 2, col = "blue")

knitr::kable(lm_slope)
```

- Using scaled or raw AMO and precipitation values do not make a difference. Here we used raw environmental values
- The quantity of economic data for Atlantic menhaden is low. Here we used economic data for menhaden from New England, Middle Atlantic, and South Atlantic regions

### Adjust projection

- If $\frac{B2012_{i}}{BMSY} > 1$, $F^{'}_{i} = FMSY^{min} + SOI2012 \times (FMSY^{max}-FMSY^{min})$

- If $\frac{B2012_{i}}{BMSY} \le 1$ and $\frac{B2012_{i}}{BMSY} > 0.5$, $F^{'}_{i} = SOI2012 \times \frac{B2012_{i}}{BMSY} \times FMSY_{i}$
  
- If $\frac{B2012_{i}}{BMSY} \le 0.5$, $F^{'}_{i} = 0$

where $i$ represents individual iterations


```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}

# Projection: cases 1 - 4 ---------------------------

lm_slope <- data.frame(
  case = 0,
  projection_year = projection_year,
  amo = NA,
  pcp = NA,
  bassB = NA,
  price = NA
)

for (projection_year_id in 1:length(projection_year)){
  
  menhaden_b <- ss_case0$timeseries[, "mu", "B"]
  
  year_id <- seq(1, nrow(amo_unsmooth_lag1), by = 12)[1:length(model_year)]
  
  index_year = model_year
  
  
  # Linear regression model -----------------------------------------
  
  amo <- amo_unsmooth_lag1[year_id, ]
  amo_lm <- lm(menhaden_b ~ amo$raw_value)
  summary(amo_lm)
  amo_fit <- fitted(amo_lm)
  lm_slope$amo[projection_year_id] <- paste0(
    round(summary(amo_lm)$coefficients[2, 1], digits = 2),
    if(summary(amo_lm)$coefficients[2, 4] <= 0.05) {"*"})
  
  pcp <- precipitation[year_id, ]
  pcp_lm <- lm(menhaden_b ~ pcp$raw_value)
  summary(pcp_lm)
  pcp_fit <- fitted(pcp_lm)
  lm_slope$pcp[projection_year_id] <- paste0(
    round(summary(pcp_lm)$coefficients[2, 1], digits = 2),
    if(summary(pcp_lm)$coefficients[2, 4] <= 0.05) {"*"})
  
  bassB <- bass_bio[bass_bio$Year %in% index_year, ]
  bassB_lm <- lm(menhaden_b ~ bassB$bass_bio)
  summary(bassB_lm)
  bassB_fit <- fitted(bassB_lm)
  lm_slope$bassB[projection_year_id] <- paste0(
    round(summary(bassB_lm)$coefficients[2, 1], digits = 2),
    if(summary(bassB_lm)$coefficients[2, 4] <= 0.05) {"*"})
  
  sub_menhaden_b <- menhaden_b[index_year %in% menhaden_price$Year]
  sub_menhadenP <- menhaden_price$Inflation.Adjust.Price.Per.MT[menhaden_price$Year %in% index_year]
  price_lm <- lm(sub_menhaden_b ~ sub_menhadenP)
  summary(price_lm)
  price_fit <- fitted(price_lm)
  lm_slope$price[projection_year_id] <- paste0(
    round(summary(price_lm)$coefficients[2, 1], digits = 2),
    if(summary(price_lm)$coefficients[2, 4] <= 0.05) {"*"})
  
  if (projection_year_id == length(projection_year)){
    
    par(mfrow = c(2, 2))
    
    plot(amo$raw_value, menhaden_b,
         xlab = "AMO raw values",
         ylab = "Biomass of menhaden-like species"
    )
    lines(amo$raw_value, amo_fit, lty = 2, col = "blue")
    
    plot(pcp$raw_value, menhaden_b,
         xlab = "Precipitation raw values",
         ylab = "Biomass of menhaden-like species"
    )
    lines(pcp$raw_value, pcp_fit, lty = 2, col = "blue")
    
    plot(bassB$bass_bio, menhaden_b,
         xlab = "Biomass of Striped bass",
         ylab = "Biomass of menhaden-like species"
    )
    lines(bassB$bass_bio, bassB_fit, lty = 2, col = "blue")
    
    plot(sub_menhadenP, sub_menhaden_b,
         xlab = "Menhaden price",
         ylab = "Biomass of menhaden-like species"
    )
    lines(sub_menhadenP, price_fit, lty = 2, col = "blue")
    
  }
  
  
  # status of indicators --------------------------------------------
  
  amo_soi <- calc_soi(
    indicator_data = amo$raw_value,
    slope = coef(amo_lm)[2]
  )
  
  pcp_soi <- calc_soi(
    indicator_data = pcp$raw_value,
    slope = coef(pcp_lm)[2]
  )
  
  bassB_soi <- calc_soi(
    indicator_data = bassB$bass_bio,
    slope = coef(bassB_lm)[2]
  )
  
  price_soi <- calc_soi(
    indicator_data = sub_menhadenP,
    slope = coef(price_lm)[2]
  )
  
  if (projection_year_id == 1) {
    scaled_data <- data.frame(
      year = model_year,
      projection_year_id = projection_year[projection_year_id],
      amo = scale(amo$raw_value)[,1],
      pcp = scale(pcp$raw_value)[,1],
      bassB = scale(bassB$bass_bio)[,1],
      price = scale(sub_menhadenP)[,1],
      menhadenB = scale(menhaden_b)[,1]
    )
    
    soi_data <- data.frame(
      year = model_year,
      projection_year_id = projection_year[projection_year_id],
      amo = amo_soi,
      pcp = pcp_soi,
      bass_b = bassB_soi,
      price = price_soi
    )
  } else{
    scaled_data <- rbind(
      scaled_data,
      data.frame(
        year = index_year,
        projection_year_id = projection_year[projection_year_id],
        amo = scale(amo$raw_value)[,1],
        pcp = scale(pcp$raw_value)[,1],
        bassB = scale(bassB$bass_bio)[,1],
        price = scale(sub_menhadenP)[,1],
        menhadenB = scale(menhaden_b)[,1]
      )
    )
    
    soi_data <- rbind(
      soi_data,
      data.frame(
        year = index_year,
        projection_year_id = projection_year[projection_year_id],
        amo = amo_soi,
        pcp = pcp_soi,
        bass_b = bassB_soi,
        price = price_soi
      )
    )
  }
  
  
  
  # Adjusted FMSY ----------------------------------------------------
  Bt_BMSY <- ss_case0$posteriors$BtoBmsy[, length(model_year)]
  
  amo_fmsy <- adjust_projection_jabba(
    FMSY = ss_case0$refpts_posterior$Fmsy,
    soi = tail(amo_soi, n = 1),
    Bt_BMSY = Bt_BMSY
  )
  pcp_fmsy <- adjust_projection_jabba(
    FMSY = ss_case0$refpts_posterior$Fmsy,
    soi = tail(pcp_soi, n = 1),
    Bt_BMSY = Bt_BMSY
  )
  bassB_fmsy <- adjust_projection_jabba(
    FMSY = ss_case0$refpts_posterior$Fmsy,
    soi = tail(bassB_soi, n = 1),
    Bt_BMSY = Bt_BMSY
  )
  price_fmsy <- adjust_projection_jabba(
    FMSY = ss_case0$refpts_posterior$Fmsy,
    soi = tail(price_soi, n = 1),
    Bt_BMSY = Bt_BMSY
  )
  
  if (projection_year_id == 1){
    fmsy_data <- data.frame(
      iter = 1:length(amo_fmsy),
      projection_year_id = projection_year[projection_year_id],
      JABBA = ss_case0$refpts_posterior$Fmsy,
      amo = amo_fmsy,
      pcp = pcp_fmsy,
      bassB = bassB_fmsy,
      price = price_fmsy
    )
  } else {
    fmsy_data <- rbind(
      fmsy_data,
      data.frame(
        iter = 1:length(amo_fmsy),
        projection_year_id = projection_year[projection_year_id],
        JABBA = ss_case0$refpts_posterior$Fmsy,
        amo = amo_fmsy,
        pcp = pcp_fmsy,
        bassB = bassB_fmsy,
        price = price_fmsy
      )
    )
  }
  
  
}

soi_data_melt <- reshape2::melt(
  soi_data,
  id = c("year", "projection_year_id")
)
soi_data_melt$projection_year_id <- as.factor(soi_data_melt$projection_year_id)

ggplot(soi_data_melt[soi_data_melt$projection_year_id==projection_year[1], ], aes(x = year, y = value)) +
  geom_line() +
  facet_wrap(~variable, scales = "free_y") +
  labs(
    title = "Status of Indicators",
    x = "Year",
    y = "Status of Indicators"
  ) +
  theme_bw()

fmsy_data_melt <- reshape2::melt(
  fmsy_data,
  id = c("iter", "projection_year_id")
)
fmsy_data_melt$projection_year_id <- as.factor(fmsy_data_melt$projection_year_id)

# ggplot(fmsy_data_melt, aes(x = iter, y = value, color = projection_year_id)) +
#   geom_line() +
#   facet_wrap(~variable) +
#   labs(
#     title = "FMSY",
#     x = "Iteration",
#     y = "FMSY"
#   ) +
#   theme_bw()

ggplot(fmsy_data_melt, aes(x=variable, y = value, color = projection_year_id)) +
  geom_boxplot()+
  labs(
    title = "FMSY",
    x = "",
    y = "FMSY"
  ) +
  theme_bw()

fmsy_data_melt_median <- aggregate(value ~ projection_year_id+variable, data = fmsy_data_melt, median)
fmsy_data_melt_median$projection_year_id <- as.numeric(as.character(fmsy_data_melt_median$projection_year_id))
ggplot(fmsy_data_melt_median, aes(x = projection_year_id, y = value, color = variable)) +
  geom_line() +
  labs(
    title = "Median FMSY from JABBA and adjusted FMSY",
    x = "",
    y = "FMSY"
  ) +
  theme_bw()

```

- Slope values from linear regression models

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
knitr::kable(lm_slope)
```

- Adjust catch input and project biomass based on FMSY*B
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}

B2013 <- ss_case0$posteriors$BtoBmsy[, (length(model_year)+1)] * ss_case0$posteriors$SBmsy[,1]

variable <- unique(fmsy_data_melt$variable)

Bt <- rep(B2013, times= length(variable))

tac_data_melt <- fmsy_data_melt
names(tac_data_melt)[names(tac_data_melt) == "value"] <- "fmsy"
tac_data_melt$tac <- adjust_projection_catcheco_jabba(fmsy_melted = fmsy_data_melt, Bt = Bt)
tac_data_melt_median <- aggregate(tac ~ variable, data = tac_data_melt, median)

ss_case0_input$jagsdata$nTAC <- length(variable)
ss_case0_input$jagsdata$TAC <- matrix(rep(tac_data_melt_median$tac, times =5), 
                                      ncol = length(variable), byrow = T)
ss_case0_input$settings$TAC.implementation <- 2013
ss_case0 <- JABBA::fit_jabba(
  jbinput = ss_case0_input,
  save.jabba = TRUE,
  save.all = TRUE,
  save.prj = TRUE,
  output.dir = output_dir,
  save.csvs = T
)

biomass_projection <- ss_case0$prj_posterior
biomass_projection <- biomass_projection[(biomass_projection$year %in% projection_year), ]
Bmsy <- rep(ss_case0$posteriors$SBmsy[, 1], 
            times= length(unique(biomass_projection$tac))*length(unique(biomass_projection$year)))
biomass_projection$biomass <- biomass_projection$stock*Bmsy
biomass_projection$year <- as.factor(biomass_projection$year)
biomass_projection$tac <- as.factor(biomass_projection$tac)

biomass_projection <- merge(biomass_projection, tac_data_melt_median, by="tac")

ggplot(biomass_projection, aes(x=year, y = biomass, color = year)) +
  geom_boxplot()+
  facet_wrap(~variable)+
  labs(
    title = " Estimated biomass based on catch=FMSY*B",
    x = "",
    y = "Biomass"
  ) +
  theme_bw()

```

- Adjust catch input and project biomass based on 0.5*FMSY*B
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
tac_data_melt_median <- aggregate(tac ~ variable, data = tac_data_melt, median)
tac_data_melt_median$tac <- tac_data_melt_median$tac/2

ss_case0_input$jagsdata$nTAC <- length(variable)
ss_case0_input$jagsdata$TAC <- matrix(rep(tac_data_melt_median$tac, times =5), 
                                      ncol = length(variable), byrow = T)
ss_case0_input$settings$TAC.implementation <- 2013
ss_case0 <- JABBA::fit_jabba(
  jbinput = ss_case0_input,
  save.jabba = TRUE,
  save.all = TRUE,
  save.prj = TRUE,
  output.dir = output_dir,
  save.csvs = T
)

biomass_projection <- ss_case0$prj_posterior
biomass_projection <- biomass_projection[(biomass_projection$year %in% projection_year), ]
Bmsy <- rep(ss_case0$posteriors$SBmsy[, 1], 
            times= length(unique(biomass_projection$tac))*length(unique(biomass_projection$year)))
biomass_projection$biomass <- biomass_projection$stock*Bmsy
biomass_projection$year <- as.factor(biomass_projection$year)
biomass_projection$tac <- as.factor(biomass_projection$tac)

biomass_projection <- merge(biomass_projection, tac_data_melt_median, by="tac")

ggplot(biomass_projection, aes(x=year, y = biomass, color = year)) +
  geom_boxplot()+
  facet_wrap(~variable)+
  labs(
    title = " Estimated biomass based on catch=0.5*FMSY*B",
    x = "",
    y = "Biomass"
  ) +
  theme_bw()
```
- Adjust catch input and project biomass based on 0.25*FMSY*B
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
tac_data_melt_median <- aggregate(tac ~ variable, data = tac_data_melt, median)
tac_data_melt_median$tac <- tac_data_melt_median$tac*0.25

ss_case0_input$jagsdata$nTAC <- length(variable)
ss_case0_input$jagsdata$TAC <- matrix(rep(tac_data_melt_median$tac, times =5), 
                                      ncol = length(variable), byrow = T)
ss_case0_input$settings$TAC.implementation <- 2013
ss_case0 <- JABBA::fit_jabba(
  jbinput = ss_case0_input,
  save.jabba = TRUE,
  save.all = TRUE,
  save.prj = TRUE,
  output.dir = output_dir,
  save.csvs = T
)

biomass_projection <- ss_case0$prj_posterior
biomass_projection <- biomass_projection[(biomass_projection$year %in% projection_year), ]
Bmsy <- rep(ss_case0$posteriors$SBmsy[, 1], 
            times= length(unique(biomass_projection$tac))*length(unique(biomass_projection$year)))
biomass_projection$biomass <- biomass_projection$stock*Bmsy
biomass_projection$year <- as.factor(biomass_projection$year)
biomass_projection$tac <- as.factor(biomass_projection$tac)

biomass_projection <- merge(biomass_projection, tac_data_melt_median, by="tac")

ggplot(biomass_projection, aes(x=year, y = biomass, color = year)) +
  geom_boxplot()+
  facet_wrap(~variable)+
  labs(
    title = " Estimated biomass based on catch=0.25*FMSY*B",
    x = "",
    y = "Biomass"
  ) +
  theme_bw()
```
