---
title: 'Catchability pattern exploration'
date: "Updated on `r format(Sys.time(), '%b %d, %Y')`"
output:
  html_document: 
    code_folding: hide
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = FALSE, echo = TRUE) # Skip the vignette when eval = FALSE
```

## Density-dependent catchability pattern

- Create a density-dependent catchability pattern that follows a powered relationship ([Wilber and Bence, 2006](https://doi.org/10.1139/f06-111)) where catchability declined with increasing biomass of menhaden-like species

- $q_t = \alpha B_t^{-\beta}$ and $F_{t, a} = q_t E_t$

where $q_t$ denotes fishery catchability ($effort^{-1}$), $\alpha$ and $\beta$ represent parameters for density-dependent catchability. Medium values of $\alpha$ and $\beta$ can be 90 and 0.49 respectively ([Wilber and Bence, 2006](https://doi.org/10.1139/f06-111)). $F_{t,a}$ and $E_t$ represent instantaneous fishing mortality rate by age and year ($year^{-1}$) and fishery effort respectively.

```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
devtools::load_all()

required_pkg <- c(
  "devtools", "here", "reshape",
  "ggplot2", "reshape2",
  "RColorBrewer", "scales", "fmsb", 
  "PBSadmb"
)

pkg_to_install <- required_pkg[!(required_pkg %in%
  installed.packages()[, "Package"])]
if (length(pkg_to_install)) install.packages(pkg_to_install)

lapply(required_pkg, library, character.only = TRUE)

library(JABBA)

```

## Simulation based on default catchability from the EwE OM

```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}

# Run simulation_newEcosim.R and get fishing mortality rate
source(here::here("Rscript", "simulation_newEcosim.R"))

# Load biomass from the operating model
om_output_path <- here::here("data", "ewe", "7ages_newsim_final", "ewe7ages_ecosim_final", "ecosim_forcing_pdsi_egg_amo1")

functional_groups <- c(
  "StripedBass0",
  "StripedBass2_5",
  "StripedBass6",
  "AtlanticMenhaden0",
  "AtlanticMenhaden1",
  "AtlanticMenhaden2",
  "AtlanticMenhaden3",
  "AtlanticMenhaden4",
  "AtlanticMenhaden5",
  "AtlanticMenhaden6",
  "SpinyDogfish",
  "BluefishJuvenile",
  "BluefishAdult",
  "WeakfishJuvenile",
  "WeakfishAdult",
  "AtlanticHerring0_1",
  "AtlanticHerring2",
  "Anchovies",
  "Benthos",
  "Zooplankton",
  "Phytoplankton",
  "Detritus"
)

age_name <- paste0("AtlanticMenhaden", 0:6)

biomass <- read_ewe_output(
  file_path = om_output_path,
  file_names = "biomass_monthly.csv",
  skip_nrows = 8,
  plot = FALSE,
  figure_titles = NULL,
  functional_groups = functional_groups,
  figure_colors = NULL
)

biomass_om <- apply(biomass[[1]][seq(1, nrow(biomass[[1]]), by = 12), age_name], 1, sum) * 1000000

# Load fishing mortality rate
file_path <- here::here("data", "ewe", "7ages_newsim_final")

Fta <- read.csv(file.path(file_path, "fatage.csv"))
colnames(Fta)[1] <- "year"

Ft_year <- read.csv(file.path(file_path, "f_full_year.csv"))
colnames(Ft_year) <- c("year", "Ft")
Ft_year$year <- Fta$year

Ft_month <- read.csv(file.path(file_path, "f_full_month.csv"))
colnames(Ft_month) <- c("year", "Ft")
Ft_month$year <- rep(Ft_year$year, each = 12)
Ft_month$month <- rep(1:12, times = nrow(Ft_year))

# Load catchability from the operating model 
qta_om <- read.csv(file.path(file_path, "qatage.csv")) 

# Calculate effort using fishing mortality rate and catchality from the operating model
Eta_om <- Fta[, grep("menhaden", colnames(Fta))] / qta_om[seq(1, nrow(qta_om), by = 12), grep("menhaden", colnames(qta_om))]

Et_om <- apply(Eta_om, 1, sum)

om_data <- data.frame(
  "Year" = Ft_year$year,
  "Fishing_Mortality_Rate" = Ft_year$Ft,
  "Effort" = Et_om,
  "Catchability" = Ft_year$Ft/Et_om, 
  "Biomass" = biomass_om
)

om_data_reshape <- reshape2::melt(
  om_data,
  id = c("Year")
)

om_figure <- ggplot(om_data_reshape, aes(Year, value, col = variable)) +             
  geom_line() +
  facet_wrap(~variable, scales = "free_y") +
  labs(
    title = "Simulation based on default catchablity from the EwE OM",
    x = "Year",
    y = "Values"
  ) 
om_figure

bq_om_figure <- ggplot(om_data, aes(Biomass, Catchability)) +             
  geom_line() +
  labs(
    title = "Catchability V.S. Biomass",
    x = "Biomass",
    y = "Catchability"
  ) 
bq_om_figure

```

```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
om_data_lagged <- data.frame(
  "Year" = om_data$Year[2:nrow(om_data)],
  "Fishing_Mortality_Rate" = om_data$Fishing_Mortality_Rate[1:(nrow(om_data)-1)],
  "Effort" = om_data$Effort[1:(nrow(om_data)-1)],
  "Catchability" = om_data$Catchability[1:(nrow(om_data)-1)], 
  "Biomass" = om_data$Biomass[2:nrow(om_data)]
)

fb_om_figure <- ggplot(om_data_lagged, aes(x = Fishing_Mortality_Rate, y = Biomass)) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red")+
  labs(
    title = "Lagged biomass v.s. fishing mortality rate",
    x = "Fishing mortality rate",
    y = "Biomass"
  ) 

fb_om_figure

model_linear <- lm(formula = Biomass ~ Fishing_Mortality_Rate, data = om_data_lagged)
summary(model_linear) # get model results and p values
```

## Simulation based on density-dependent catchability
```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}

# Simulate density-dependent catchability
alpha <- c(90)
beta <- c(0.49)

qt_dd <- alpha*biomass_om^(-beta)

dd_data <- data.frame(
  "Year" = Ft_year$year,
  "Fishing_Mortality_Rate" = Ft_year$Ft,
  "Effort" = Ft_year$Ft/qt_dd,
  "Catchability" = qt_dd, 
  "Biomass" = biomass_om
)

dd_data_reshape <- reshape2::melt(
  dd_data,
  id = c("Year")
)

dd_figure <- ggplot(dd_data_reshape, aes(Year, value, col = variable)) +             
  geom_line() +
  facet_wrap(~variable, scales = "free_y") +
  labs(
    title = "Simulation based on density-dependent catchablity",
    x = "Year",
    y = "Values"
  ) 
dd_figure

bq_dd_figure <- ggplot(dd_data, aes(Biomass, Catchability)) +             
  geom_line() +
  labs(
    title = "Catchability V.S. Biomass",
    x = "Biomass",
    y = "Catchability"
  ) 
bq_dd_figure

```

## I think effort is still confounded by fishing mortality?

We can plot effort from both constant catchability (the OM) and density-dependent 
catchability below:  

```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}

eff_data <- rbind(
  data.frame(dd_data_reshape[dd_data_reshape$variable == "Effort", ], 
    Catch_type = "DD"),
  data.frame(om_data_reshape[om_data_reshape$variable == "Effort", ], 
    Catch_type = "OM")
  )

eff_figure <- ggplot(eff_data, aes(Year, value, col = Catch_type)) +             
  geom_line() +
  #facet_grid(~Catch_type, scales = "fixed") +
  labs(
    x = "Year",
    y = "Effort"
  ) 
eff_figure

```

The scale is different but the trends still appear similar - I think this is 
because effort is still mostly following the trend from fishing mortality. There 
are a few reasons this may make sense, or not. I don't think there should be a 
relationship between fishing mortality and biomass, at least in the 
same period, since fishing mortality is exogenous (by definition?).  

There might be a relationship between lagged mortality and biomass, if for example 
fishing more in this period affects biomass in the next period. However, this 
relationship seems to be positive (am I misreading this?), which also seems to 
imply more fishing results in more future fish. I would be worried any relationship 
here is spurious.  

An alternative is to look at catch per unit effort, and control for fishing 
mortality. This could follow if we were examining a fishery where catches are 
exogenously set by management, and harvesters always fulfill the total allowable 
catch, as a simplifying starting assumption.  

The first plot below is then catch per unit effort, with total catches per year 
taken from the EwE operating model. Notably, catches are not 1:1 with fishing mortality, 
but rather they already move with biomass, which is surprising (there's already 
some kind of catchability set in the OM?).  

The second plot assumes we can observe true fishing mortality, and is fishing 
mortality per unit effort. By definition, we can then recover catchability.  

```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}

project_path <- here::here()
ewe_output_path <- file.path(project_path, "data", "ewe", "7ages_newsim_final", 
  "ewe7ages_ecosim_final", "ecosim_forcing_pdsi_egg_amo1")

# grab total catch from ewe
temp_cat <- scan(file.path(ewe_output_path, "catch_annual.csv"), what = "", 
  sep = "\n")
skip_nrows <- 8
data <- temp_cat[-c(1:skip_nrows)]
data <- read.table(
  text = as.character(data),
  sep = ",",
  col.names = read.table(text = temp_cat[skip_nrows], sep = ",")
  )
data_years <- 1985:2017
species = 4:10
species_vec <- paste0("X", species)
data <- data[which(data$year.group %in% data_years), 
  c("year.group", species_vec)]
data[, species_vec] <- data[, species_vec] * 1000000 # biomass in mt
ages <- 0:6
species_labels = paste0("age", ages)
colnames(data) <- c("year", species_labels)
catch_age <- data[, species_labels] # biomass in mt
row.names(catch_age) <- data_years
total_catch <- apply(catch_age, 1, sum)
names(total_catch) <- data_years
total_catch <- cbind(Year=data$year, total_catch)

eff_data <- merge(eff_data, total_catch, by = c("Year"))
eff_data$eff_norm <- eff_data$total_catch/eff_data$value

par(mfrow = c(1, 2))

catch_figure <- ggplot(eff_data, aes(Year, eff_norm, col = Catch_type)) +             
  geom_line() +
  #facet_grid(~Catch_type, scales = "fixed") +
  labs(
    x = "Year",
    y = "CPUE"
  ) 
catch_figure

om_data <- merge(om_data, total_catch, by = c("Year"))
dd_data <- merge(dd_data, total_catch, by = c("Year"))
om_data$CPUE <- om_data$Fishing_Mortality_Rate/om_data$Effort
dd_data$CPUE <- dd_data$Fishing_Mortality_Rate/dd_data$Effort

om_dd_data <- rbind(
  data.frame(dd_data, 
    Catch_type = "DD"),
  data.frame(om_data, 
    Catch_type = "OM")
  )

fmort_figure <- ggplot(om_dd_data, aes(Year, CPUE, col=Catch_type)) +             
  geom_line() +
  #facet_grid(~Catch_type, scales = "fixed") +
  labs(
    x = "Year",
    y = "FPUE"
  ) 
fmort_figure

```

Then we plot the relationship between each indicator (lagged) and biomass, where the 
first is fishing mortality per unit effort and the second catch per unit effort.

```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}

model_year <- 1985:2012
projection_year <- 2013:2017
index_year <- c(model_year, projection_year)
lag = 1
biomass_lag_id <- (1+lag):length(index_year)
index_lag_id <- 1:(length(index_year)-lag)
time_id <- seq(1, nrow(biomass[[1]]), by = 12)
biomass_ewe <- apply(biomass[[1]][, age_name], 1, sum) * 1000000

effort <- dd_data$CPUE
effort_lm <- lm(biomass_ewe[time_id][biomass_lag_id] ~ effort[index_lag_id])
effort_fit <- fitted(effort_lm)

fmort_effort_soi <- calc_soi(
    indicator_data = effort,
    slope = coef(effort_lm)[2]
  )

par(mfrow = c(2, 2))
  
plot(effort[index_lag_id], biomass_ewe[time_id][biomass_lag_id],
     xlab = "Fishing mortality per unit effort of menhaden-like species from OM",
     ylab = "Biomass of menhaden-like species from OM"
)
abline(effort_lm)

effort <- eff_data$eff_norm[eff_data$Catch_type == "DD"]
effort_lm <- lm(biomass_ewe[time_id][biomass_lag_id] ~ effort[index_lag_id])
effort_fit <- fitted(effort_lm)

plot(effort[index_lag_id], biomass_ewe[time_id][biomass_lag_id],
     xlab = "Catch per unit effort of menhaden-like species from OM",
     ylab = "Biomass of menhaden-like species from OM"
)
abline(effort_lm)

catch_effort_soi <- calc_soi(
    indicator_data = effort,
    slope = coef(effort_lm)[2]
  )

effort <- eff_data$total_catch[eff_data$Catch_type == "DD"]
effort_lm <- lm(biomass_ewe[time_id][biomass_lag_id] ~ effort[index_lag_id])
effort_fit <- fitted(effort_lm)

plot(effort[index_lag_id], biomass_ewe[time_id][biomass_lag_id],
     xlab = "Catch of menhaden-like species from OM",
     ylab = "Biomass of menhaden-like species from OM"
)
abline(effort_lm)

```

Notably, for the catch per unit effort, the relationship with biomass is positive. Catches tend 
to increase with biomass, and catches largely dominate the trend (compared to 
catchability). Then, when catches are low, biomass is relatively smaller, and 
future biomass is also smaller on average. I would guess that specifying catchability 
likely doesn't affect the indicator in the this plot, which is largely driven by 
catches (which is a function of biomass?).  

For fishing mortality, the relationship with biomass is negative. This is due 
to the functional form we have specified for catchability, which decreases as 
biomass increases. Because biomass tends to move positively with lagged biomass,
when when catchability is good, biomass is (relatively) low, and we can expect 
future biomass to also be smaller on average.  

Below, we plot lagged indicators on biomass estimates from JABBA, as well as the 
status of indicators over years and FMSY benchmarks.

```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}

file_path <- here::here("data", "ewe", "7ages_newsim_final", "ewe7ages_ecosim_final", "ecosim_forcing_pdsi_egg_amo1")
source(here::here("Rscript", "load_indices_catcha.R"))

lm_slope <- data.frame(
  case = "PDSI+AMO1 Case",
  projection_year = 1:length(projection_year),
  effort_fm = NA,
  effort_c = NA
)

model_year <- 1985:2012
projection_year <- 2013:2017
output_dir <- here::here("data", "data_moderate")

## Use effort data
year_id <- seq(1, nrow(amo_unsmooth_lag1), by = 12)
effort <- apply(ewe_faa[, grep("menhaden", colnames(ewe_faa))] / ewe_catchability[year_id, grep("menhaden", colnames(ewe_catchability))], 1, sum)

ss_case0_input <- generate_jabba(
  assessment_name = "case0",
  output_dir = output_dir,
  sa_data = sa_data,
  model_year = model_year,
  projection_year = projection_year,
  effort_data = effort[1:length(model_year)]
)

# k_init <- max(sa_data$fishery$obs_total_catch_biomass$fleet1) * 10
k_init <- 3500000
ss_case0_input$jagsdata$K.pr <- c(k_init, 0.1)
ss_case0_input$jagsdata$r.pr <- c(0.6, 0.1)
ss_case0_input$jagsdata$psi.pr <- c(0.7, 0.1)

set.seed(999)
ss_case0 <- JABBA::fit_jabba(
  jbinput = ss_case0_input,
  save.jabba = TRUE,
  save.all = TRUE,
  save.prj = TRUE,
  output.dir = output_dir,
  save.csvs = T
)

ss_case0$estimates

for (projection_year_id in 1:length(projection_year)){
  
  menhaden_b <- ss_case0$timeseries[, "mu", "B"]
  
  year_id <- seq(1, nrow(amo_unsmooth_lag1), by = 12)[1:length(model_year)]
  
  index_year = model_year
  
  
  # Linear regression model -----------------------------------------
  
  lag = 1
  biomass_lag_id <- (1+lag):length(index_year)
  index_lag_id <- 1:(length(index_year)-lag)
  
  effort_fm <- dd_data$CPUE
  effort_fm_lm <- lm(menhaden_b[biomass_lag_id] ~ effort_fm[index_lag_id])
  effort_fit <- fitted(effort_fm_lm)
  lm_slope$effort_fm <- paste0(
    round(summary(effort_fm_lm)$coefficients[2, 1], digits = 2),
    if (summary(effort_fm_lm)$coefficients[2, 4] <= 0.05) {
      "*"
    }
  )
  
  effort_c <- eff_data$eff_norm[eff_data$Catch_type == "DD"]
  effort_c_lm <- lm(menhaden_b[biomass_lag_id] ~ effort_c[index_lag_id])
  effort_fit <- fitted(effort_c_lm)
  lm_slope$effort_c <- paste0(
    round(summary(effort_c_lm)$coefficients[2, 1], digits = 2),
    if (summary(effort_c_lm)$coefficients[2, 4] <= 0.05) {
      "*"
    }
  )
  
  if (projection_year_id == length(projection_year)){
    
    par(mfrow = c(1, 2))
    
    plot(effort_fm[index_lag_id], menhaden_b[biomass_lag_id],
         xlab = "Fishing mortality per unit effort",
         ylab = "Biomass of menhaden-like species"
    )
    abline(effort_fm_lm)
    
    plot(effort_c[index_lag_id], menhaden_b[biomass_lag_id],
         xlab = "Catch per unit effort",
         ylab = "Biomass of menhaden-like species"
    )
    abline(effort_c_lm)
    
  }
    
  # status of indicators --------------------------------------------
  
  effort_fm_soi <- calc_soi(
    indicator_data = effort_fm,
    slope = coef(effort_fm_lm)[2]
  )
  
  effort_c_soi <- calc_soi(
    indicator_data = effort_c,
    slope = coef(effort_c_lm)[2]
  )
  
  if (projection_year_id == 1) {
    soi_data <- data.frame(
      year = model_year,
      projection_year_id = projection_year_id,
      effort_fm = effort_fm_soi[1:28],
      effort_c = effort_c_soi[1:28]
    )
  } else {
    soi_data <- rbind(
      soi_data,
      data.frame(
            year = model_year,
            projection_year_id = projection_year_id,
            effort_fm = effort_fm_soi[1:28],
            effort_c = effort_c_soi[1:28]
      )
    )
  }
    
  # Adjusted FMSY ----------------------------------------------------
  Bt_BMSY <- as.matrix(ss_case0$posteriors$BtoBmsy[, length(model_year)])
  
  effort_fm_fmsy <- adjust_projection_jabba(
    FMSY = ss_case0$refpts_posterior$Fmsy,
    soi = tail(effort_fm_soi, n = 1),
    Bt_BMSY = Bt_BMSY
  )

  effort_c_fmsy <- adjust_projection_jabba(
    FMSY = ss_case0$refpts_posterior$Fmsy,
    soi = tail(effort_c_soi, n = 1),
    Bt_BMSY = Bt_BMSY
  )
  
  if (projection_year_id == 1){
    fmsy_data <- data.frame(
      iter = 1:length(effort_fm_fmsy),
      projection_year_id = projection_year[projection_year_id],
      JABBA = ss_case0$refpts_posterior$Fmsy,
      effort_fm = effort_fm_fmsy,
      effort_c = effort_c_fmsy
    )
  } else {
    fmsy_data <- rbind(
      fmsy_data,
      data.frame(
        iter = 1:length(effort_fm_fmsy),
        projection_year_id = projection_year[projection_year_id],
        JABBA = ss_case0$refpts_posterior$Fmsy,
        effort_fm = effort_fm_fmsy,
        effort_c = effort_c_fmsy
      )
    )
  }
  
}

soi_data_melt <- reshape2::melt(
  soi_data,
  id = c("year", "projection_year_id")
)

soi_data_melt$projection_year_id <- as.factor(projection_year)

ggplot(soi_data_melt[soi_data_melt$projection_year_id==projection_year[1], ], aes(x = year, y = value)) +
  geom_line() +
  facet_wrap(~variable, scales = "free_y") +
  labs(
    title = "Status of Indicators",
    x = "Year",
    y = "Status of Indicators"
  ) +
  theme_bw()
    
fmsy_data_melt <- reshape2::melt(
  fmsy_data,
  id = c("iter", "projection_year_id")
)
fmsy_data_melt$projection_year_id <- as.factor(fmsy_data_melt$projection_year_id)

ggplot(fmsy_data_melt, aes(x=variable, y = value, color = projection_year_id)) +
  geom_boxplot()+
  labs(
    title = "FMSY",
    x = "",
    y = "FMSY"
  ) +
  theme_bw()

fmsy_data_melt_median <- aggregate(value ~ projection_year_id+variable, data = fmsy_data_melt, median)
fmsy_data_melt_median$projection_year_id <- as.numeric(as.character(fmsy_data_melt_median$projection_year_id))
ggplot(fmsy_data_melt_median, aes(x = projection_year_id, y = value, color = variable)) +
  geom_line() +
  labs(
    title = "Median FMSY from JABBA and adjusted FMSY",
    x = "",
    y = "FMSY"
  ) +
  theme_bw()

(lm_slope)

```

I think, for me, the benefit of using fishing mortality is that there's a well-
defined mechanism that I can see drive the results: catchability is a function 
of biomass, so it should tell us something about future biomass as long as we can
recover it.  

I think catch per unit effort would work as well here, but I don't see a need to use catchability anymore, 
or at least it appears there's already some sort of catchability implicit in EwE? As far 
as I can see it's all -9999 as inputs into EwE so I'm not quite sure what's going on here yet.
But to the extent catches increase with biomass, there's a relationship there to exploit. 
The story would then be if fishers catch more for the same mortality when biomass is larger,
because it's easier to catch fish conditional on the same time spent, fuel consumed, etc.

I think with previous indicators like price, it could work but I'm not following 
the mechanism where prices have some relationship with biomass in the EwE OM. Although 
I'm sure I miss a lot of things so I apologize in advance!

```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}

B2013 <- ss_case0$posteriors$BtoBmsy[, (length(model_year) + 1)] * ss_case0$posteriors$SBmsy[,1]

variable <- unique(fmsy_data_melt$variable)

Bt <- rep(B2013, times= length(variable))

tac_data_melt <- fmsy_data_melt
names(tac_data_melt)[names(tac_data_melt) == "value"] <- "fmsy"
tac_data_melt$tac <- adjust_projection_catcheco_jabba(fmsy_melted = fmsy_data_melt, Bt = Bt)
tac_data_melt_median <- aggregate(tac ~ variable, data = tac_data_melt, median)

ss_case0_input$jagsdata$nTAC <- length(variable)
ss_case0_input$jagsdata$TAC <- matrix(rep(tac_data_melt_median$tac, times =5), 
                                      ncol = length(variable), byrow = T)
ss_case0_input$settings$TAC.implementation <- 2013
ss_case0 <- JABBA::fit_jabba(
  jbinput = ss_case0_input,
  save.jabba = TRUE,
  save.all = TRUE,
  save.prj = TRUE,
  output.dir = output_dir,
  save.csvs = T
)

biomass_projection <- ss_case0$prj_posterior
biomass_projection <- biomass_projection[(biomass_projection$year %in% projection_year), ]
Bmsy <- rep(ss_case0$posteriors$SBmsy[, 1], 
            times= length(unique(biomass_projection$tac))*length(unique(biomass_projection$year)))
biomass_projection$biomass <- biomass_projection$stock*Bmsy
biomass_projection$year <- as.factor(biomass_projection$year)
biomass_projection$tac <- as.factor(biomass_projection$tac)

biomass_projection <- merge(biomass_projection, tac_data_melt_median, by="tac")

ggplot(biomass_projection, aes(x=year, y = biomass, color = year)) +
  geom_boxplot()+
  facet_wrap(~variable)+
  labs(
    title = " Estimated biomass based on catch=FMSY*B",
    x = "",
    y = "Biomass"
  ) +
  theme_bw()

```
