---
title: 'Data-poor stock assessment with new EwE OM'
date: 'Updated on July 19, 2022'
output:
  html_document: 
    code_folding: hide
  word_document: default
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Depletion-Based Stock Reduction Analysis(DB-SRA) from DLMtool

- Website: [https://github.com/Blue-Matter/DLMtool](https://github.com/Blue-Matter/DLMtool)

```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
devtools::load_all()

# Install required R packages -------------------------------------
required_pkg <- c("DLMtool", "here", "ggplot2", "reshape2") ## DLMtool: version 6.0.3

pkg_to_install <- required_pkg[!(required_pkg %in%
                                   installed.packages()[, "Package"])]
if (length(pkg_to_install)) install.packages(pkg_to_install)

lapply(required_pkg, library, character.only = TRUE)
```

## Case 0: stock assessment base run

- Case 0.1

```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
# Load simulated input data
source(here::here("Rscript", "simulation_newEcosim.R"))
source(here::here("Rscript", "load_indices.R"))

# Load EwE biomass----------------------------
model_year <- 1985:2012
projection_year <- 2013:2017

functional_groups <- c(
  "StripedBass0",
  "StripedBass2_5",
  "StripedBass6",
  "AtlanticMenhaden0",
  "AtlanticMenhaden1",
  "AtlanticMenhaden2",
  "AtlanticMenhaden3",
  "AtlanticMenhaden4",
  "AtlanticMenhaden5",
  "AtlanticMenhaden6",
  "SpinyDogfish",
  "BluefishJuvenile",
  "BluefishAdult",
  "WeakfishJuvenile",
  "WeakfishAdult",
  "AtlanticHerring0_1",
  "AtlanticHerring2",
  "Anchovies",
  "Benthos",
  "Zooplankton",
  "Phytoplankton",
  "Detritus"
)

age_name <- paste0("AtlanticMenhaden", 0:6)

biomass <- read_ewe_output(
  file_path = here::here("data", "ewe", "7ages_newsim_final", "ewe7ages_ecosim_final", "ecosim_forcing_pdsi_egg_amo1"),
  file_names = "biomass_monthly.csv",
  skip_nrows = 8,
  plot = FALSE,
  figure_titles = NULL,
  functional_groups = functional_groups,
  figure_colors = NULL
)

time_id <- seq(1, nrow(biomass[[1]]), by = 12)
biomass_ewe <- apply(biomass[[1]][, age_name], 1, sum)[time_id] * 1000000


# Case 0.1: default stock assessment run ----------------------------
sensitivity_run <- FALSE
sensitivity_plot <- FALSE
## DB-SRA is a method designed for determining a catch limit
## and management reference points for data-limited fisheries
## where catches are known from the beginning of exploitation.
## However, the catch data from the menhaden-like species case is not
## from the beginning of the exploitation.

# Populate the input data object

# Create a blank DLM object
ss_case0 <- new("Data")
# Change default area from 2 to 1
ss_case0@nareas <- 1
# Name of the case
ss_case0@Name <- "case0"
# Catch data
data_id <- as.numeric(names(sa_data$fishery$obs_total_catch_biomass$fleet1)) %in% model_year
ss_case0@Cat <- matrix(sa_data$fishery$obs_total_catch_biomass$fleet1[data_id],
                       nrow = 1
)
# State units of catch
ss_case0@Units <- sa_data$fishery$units_info$units_biomass
# Years
ss_case0@Year <- model_year
# Depletion relative to unfished
ss_case0@Dep <-  tail(ss_case0@Cat[1, ], n = 1) / max(ss_case0@Cat[1, ])

# VB maximum growth rate
ss_case0@vbK <- sa_data$biodata$k
# VB theoretical age at zero length
# default from EwE: -0.1
# https://www.researchgate.net/publication/267193103_Ecopath_with_Ecosim_A_User's_Guide#pf66
ss_case0@vbt0 <- sa_data$biodata$t0
# VB maximum length
# ss_case0@vbLinf <- (sa_data$biodata$winf * 1000 / sa_data$biodata$lw_a)^(1 / sa_data$biodata$lw_b)
ss_case0@vbLinf <- 500 # mm from FishBase
# Ratio of FMSY/M
# Q: Is it possible to find the ratio of FMSY to M
# for pelagic species in the Northwestern Atlantic Ocean?
# EwE FMSY values
fmsy <- c(
  0.092402786, 0.344614655, 1.101458788, 0.722086847,
  1.569404483, 0.988227546, 0.72328496
)

fmsy_m <- fmsy / sa_data$biodata$natural_mortality_matrix[1, ]

ss_case0@FMSY_M <- mean(fmsy_m) 

#ss_case0@Mort <- 0.67 #sa_data$biodata$natural_mortality_matrix[1, ]/(1-exp(-ss_case0@vbK*(1:7-ss_case0@vbt0)))^(-3*0.305)

# BMSY relative to unfished
# Dick and MacCall (2011): use 0.4 if target biomass is 40% of unfished biomass
ss_case0@BMSY_B0 <- 0.3 # BAM FEC30% target

# Length at 50% maturity
age_maturity50 <- 2
ss_case0@L50 <- ss_case0@vbLinf *
  (1 - exp(-ss_case0@vbK *
             (age_maturity50 - ss_case0@vbt0)))

# Run DBSRA, DBSRA_40 and DBSRA4010
## DBSRA: Base Version. TAC is calculated assumed MSY harvest rate
## multiplied by the estimated current abundance (estimated B0 x Depletion)

## DBSRA_40: Same as the Base Version but assumes 40 percent current
## depletion (Bcurrent/B0 = 0.4), which is more or less the most
## optimistic state for a stock (i.e. very close to BMSY/B0 for many stocks).

## DBSRA4010: Base version paired with the 40-10 rule that linearly
## throttles back the TAC when depletion is below 0.4 down to zero at
## 10 percent of unfished biomass.

ss_case01 <- ss_case0
dbsra <- DLMtool::DBSRA(1, ss_case01, plot = FALSE)
# dbsra40 <- DLMtool::DBSRA_40(1, ss_case0, plot = TRUE)
# dbsra4010 <- DLMtool::DBSRA4010(1, ss_case0, plot = TRUE)

# Projection: case 0.1 --------------------------------------------------
projection_output1 <- list()
for (i in 1:length(projection_year)) {
  ss_case <- ss_case01
  year <- model_year[1]:(projection_year[i] - 1)
  data_id <- as.numeric(names(sa_data$fishery$obs_total_catch_biomass$fleet1)) %in% year
  ss_case@Cat <- matrix(sa_data$fishery$obs_total_catch_biomass$fleet1[data_id],
                        nrow = 1
  )
  ss_case@Year <- year
  #ss_case@Dep <- tail(ss_case@Cat[1, ], n = 1) / ss_case@Cat[1, 1]
  ss_case@Dep <- ss_case01@Dep
  projection_output1[[i]] <- DLMtool::DBSRA_(
    x = 1,
    Data = ss_case,
    depo = NULL, # Optional fixed depletion (single value)
    hcr = NULL # Optional harvest control rule for throttling catch as a function of B/B0.
  )
}

# plot figures
par(mfrow=c(1,2))
ylim <- range(projection_output1[[1]]$C_hist, unlist(sapply(projection_output1, "[", "TAC")))
plot(c(model_year, projection_year),
     c(projection_output1[[1]]$C_hist, rep(NA, length(projection_year))),
     type = "l",
     ylim = ylim,
     xlab = "Year", ylab = "Catch (mt)"
)

for (i in 1:length(projection_year)) {
  boxplot(projection_output1[[i]]$TAC,
          add = TRUE,
          at = projection_year[i],
          col = "grey",
          width = 1,
          outline = TRUE,
          axes = FALSE
  )
}

catch_year <- projection_year[1:length(projection_year) - 1]
points(catch_year, sa_data$fishery$obs_total_catch_biomass$fleet1[names(sa_data$fishery$obs_total_catch_biomass$fleet1) %in% catch_year],
       pch = 16, col = "blue"
)

legend("top",
       c("Observed Catch (model year)", "Observed Catch (projection year)", "TAC"),
       lty = c(1, NA, NA),
       pch = c(NA, 16, NA),
       col = c("black", "blue", NA),
       fill = c(NA, NA, "gray"),
       border = c(NA, NA, "black"),
       bty = "n",
       title = "Case 0.1"
)
legend("left",
       c(
         paste0("DBSRA@Dep = ", round(ss_case01@Dep, digits = 2)),
         paste0("DBSRA@BMSY_B0 = ", round(ss_case01@BMSY_B0, digits = 2)),
         paste0("DBSRA@FMSY_M = ", round(ss_case01@FMSY_M, digits = 2))
       ),
       bty="n")

# plot biomass
dbsraB_projection <- list()
for (i in 1:length(projection_year)){
  dbsraB_projection[[i]] <- apply(projection_output1[[i]]$Btrend, 2, median)
}

ylim <- range(biomass_ewe, unlist(dbsraB_projection))
plot(c(model_year, projection_year),
     biomass_ewe,
     xlab = "Year", ylab = "Biomass (mt)",
     ylim = ylim,
     pch = 16
)
for (i in 1:length(projection_year)){
  lines(model_year[1]:(projection_year[i]-1), dbsraB_projection[[i]],
        lty=i, col=i)
}
legend("bottomright",
       c("EWE", paste0("DBSRA", projection_year)),
       bty = "n",
       pch = c(16, rep(NA, length(projection_year))),
       lty = c(NA, 1:length(projection_year)),
       col = c(1, 1:length(projection_year)),
       title = "Case 0.1"
)

```

- Case 0.2

```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}

# Case 0.2 ---------------------------


msy <- c(
  4.707030582, 4.539975134, 3.3665618, 3.810355182, 2.973373656, 3.620820917, 2.923792894
)

# b0 <- 2.45240886*1000000 # final b
b0 <- 5.12023947*1000000 # max b

bmsy <- c(
  4.553527815, 4.228060737, 2.657752888, 3.039367286, 1.700737553, 2.625573544, 1.885360091
)*1000000

ss_case02 <- ss_case0
ss_case02@Dep <- biomass_ewe[2012-1985+1]/b0

# BMSY relative to unfished
# Dick and MacCall (2011): use 0.4 if target biomass is 40% of unfished biomass
ss_case02@BMSY_B0 <- mean(bmsy/b0)

dbsra <- DLMtool::DBSRA(1, ss_case02, plot = FALSE)

# Projection: case 0.2 --------------------------------------------------
projection_output2 <- list()
for (i in 1:length(projection_year)) {
  ss_case <- ss_case02
  year <- model_year[1]:(projection_year[i] - 1)
  data_id <- as.numeric(names(sa_data$fishery$obs_total_catch_biomass$fleet1)) %in% year
  ss_case@Cat <- matrix(sa_data$fishery$obs_total_catch_biomass$fleet1[data_id],
                        nrow = 1
  )
  ss_case@Year <- year
  #ss_case@Dep <- tail(ss_case@Cat[1, ], n = 1) / ss_case@Cat[1, 1]
  ss_case@Dep <- ss_case02@Dep
  projection_output2[[i]] <- DLMtool::DBSRA_(
    x = 1,
    Data = ss_case,
    depo = NULL, # Optional fixed depletion (single value)
    hcr = NULL # Optional harvest control rule for throttling catch as a function of B/B0.
  )
}

# plot figures
par(mfrow=c(1,2))
ylim <- range(projection_output2[[1]]$C_hist, unlist(sapply(projection_output2, "[", "TAC")))
plot(c(model_year, projection_year),
     c(projection_output2[[1]]$C_hist, rep(NA, length(projection_year))),
     type = "l",
     ylim = ylim,
     xlab = "Year", ylab = "Catch (mt)"
)

for (i in 1:length(projection_year)) {
  boxplot(projection_output2[[i]]$TAC,
          add = TRUE,
          at = projection_year[i],
          col = "grey",
          width = 1,
          outline = TRUE,
          axes = FALSE
  )
}

catch_year <- projection_year[1:length(projection_year) - 1]
points(catch_year, sa_data$fishery$obs_total_catch_biomass$fleet1[names(sa_data$fishery$obs_total_catch_biomass$fleet1) %in% catch_year],
       pch = 16, col = "blue"
)

legend("top",
       c("Observed Catch (model year)", "Observed Catch (projection year)", "TAC"),
       lty = c(1, NA, NA),
       pch = c(NA, 16, NA),
       col = c("black", "blue", NA),
       fill = c(NA, NA, "gray"),
       border = c(NA, NA, "black"),
       bty = "n",
       title = "Case 0.2"
)

legend("left",
       c(
         paste0("DBSRA@Dep = ", round(ss_case02@Dep, digits = 2)),
         paste0("DBSRA@BMSY_B0 = ", round(ss_case02@BMSY_B0, digits = 2)),
         paste0("DBSRA@FMSY_M = ", round(ss_case02@FMSY_M, digits = 2))
       ),
       bty="n")

# plot biomass
dbsraB_projection <- list()
for (i in 1:length(projection_year)){
  dbsraB_projection[[i]] <- apply(projection_output2[[i]]$Btrend, 2, median)
}

ylim <- range(biomass_ewe, unlist(dbsraB_projection))
plot(c(model_year, projection_year),
     biomass_ewe,
     xlab = "Year", ylab = "Biomass (mt)",
     ylim = ylim,
     pch = 16
)
for (i in 1:length(projection_year)){
  lines(model_year[1]:(projection_year[i]-1), dbsraB_projection[[i]],
        lty=i, col=i)
}
legend("bottomright",
       c("EWE", paste0("DBSRA", projection_year)),
       bty = "n",
       pch = c(16, rep(NA, length(projection_year))),
       lty = c(NA, 1:length(projection_year)),
       col = c(1, 1:length(projection_year)),
       title = "Case 0.2"
)

```

- Case 0.3
- Add a long sequence of equilibrium catches (8 years of max catch) to the start of the catch

```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}

time_id_model_year <- seq(1, nrow(biomass[[1]]), by = 12)[1:length(model_year)]
biomass_ewe_model_year <- apply(biomass[[1]][, age_name], 1, sum)[time_id_model_year] * 1000000

ss_case03 <- ss_case0
# equi_year <- 2000:2012
# equi_id <- as.numeric(names(sa_data$fishery$obs_total_catch_biomass$fleet1)) %in% equi_year
# equi_catch <- sa_data$fishery$obs_total_catch_biomass$fleet1[equi_id]

equi_year <- 2005:2012
catch_multiplier <- 1
# equi_catch <- rep(sa_data$fishery$obs_total_catch_biomass$fleet1[1], length = length(equi_year)) * catch_multiplier
equi_catch <- rep(max(sa_data$fishery$obs_total_catch_biomass$fleet), length = length(equi_year)) * catch_multiplier

# equi_year <- 1985:1993
# equi_id <- as.numeric(names(sa_data$fishery$obs_total_catch_biomass$fleet1)) %in% equi_year
# equi_catch <- sa_data$fishery$obs_total_catch_biomass$fleet1[equi_id]

data_id <- as.numeric(names(sa_data$fishery$obs_total_catch_biomass$fleet1)) %in% model_year
ss_case03@Cat <- matrix(c(equi_catch, sa_data$fishery$obs_total_catch_biomass$fleet1[data_id]),
                        nrow = 1
)

ss_case03@Year <- (model_year[1] - length(equi_year)):tail(model_year, n=1)

dep = seq(0.1, 0.9, by = 0.05)
# sum of squared differences
ssd_dep <- data.frame(
  dep = dep,
  ssd = NA
)
for (i in 1:length(dep)){
  ss_case <- ss_case03
  ss_case@Dep <- dep[i]
  dbsra <- DLMtool::DBSRA_(
    x = 1,
    Data = ss_case,
    depo = NULL,
    hcr = NULL
  )
  dbsraB <- apply(dbsra$Btrend, 2, median)
  ssd_dep$ssd[i] <- sum((dbsraB[(length(equi_year)+1):length(dbsraB)] - biomass_ewe_model_year)^2)
}

ss_case <- ss_case03
ss_case@Dep <- ssd_dep$dep[which.min(ssd_dep$ssd)] # dep = 0.8 has the smallest sum of squared differences
dbsra <- DLMtool::DBSRA_(
  x = 1,
  Data = ss_case,
  depo = NULL,
  hcr = NULL
)
dbsra_dep <- apply(dbsra$Btrend, 2, median)

bmsy_b0 <- seq(0.1, 0.9, by = 0.05)
# sum of squared differences
ssd_bmsy_b0 <- data.frame(
  bmsy_b0 = bmsy_b0,
  ssd = NA
)
for (i in 1:length(bmsy_b0)){
  ss_case <- ss_case03
  ss_case@Dep <- ssd_dep$dep[which.min(ssd_dep$ssd)]
  ss_case@BMSY_B0 <- bmsy_b0[i]
  dbsra <- DLMtool::DBSRA_(
    x = 1,
    Data = ss_case,
    depo = NULL,
    hcr = NULL
  )
  dbsraB <- apply(dbsra$Btrend, 2, median)
  ssd_bmsy_b0$ssd[i] <- sum((dbsraB[(length(equi_year)+1):length(dbsraB)] - biomass_ewe_model_year)^2)
}


ss_case <- ss_case03
ss_case@Dep <- ssd_dep$dep[which.min(ssd_dep$ssd)]
ss_case@BMSY_B0 <- ssd_bmsy_b0$bmsy_b0[which.min(ssd_bmsy_b0$ssd)] # bmsy_b0 = 0.55 has the smallest sum of squared differences: 6.6e+12
dbsra <- DLMtool::DBSRA_(
  x = 1,
  Data = ss_case,
  depo = NULL,
  hcr = NULL
)
dbsra_bmsyb0 <- apply(dbsra$Btrend, 2, median)

fmsy_m <- seq(0.1, 2, by = 0.05)
# sum of squared differences
ssd_fmsy_m <- data.frame(
  fmsy_m = fmsy_m,
  ssd = NA
)
for (i in 1:length(fmsy_m)){
  ss_case <- ss_case03
  ss_case@Dep <- ssd_dep$dep[which.min(ssd_dep$ssd)]
  ss_case@BMSY_B0 <- ssd_bmsy_b0$bmsy_b0[which.min(ssd_bmsy_b0$ssd)]
  ss_case@FMSY_M <- fmsy_m[i]
  dbsra <- DLMtool::DBSRA_(
    x = 1,
    Data = ss_case,
    depo = NULL,
    hcr = NULL
  )
  dbsraB <- apply(dbsra$Btrend, 2, median)
  ssd_fmsy_m$ssd[i] <- sum((dbsraB[(length(equi_year)+1):length(dbsraB)] - biomass_ewe_model_year)^2)
}


ss_case <- ss_case03
ss_case@Dep <- ssd_dep$dep[which.min(ssd_dep$ssd)]
ss_case@BMSY_B0 <- ssd_bmsy_b0$bmsy_b0[which.min(ssd_bmsy_b0$ssd)]
ss_case@FMSY_M <- ssd_fmsy_m$fmsy_m[which.min(ssd_fmsy_m$ssd)] # fmsy_m = 1.2 has the smallest sum of squared differences
dbsra <- DLMtool::DBSRA_(
  x = 1,
  Data = ss_case,
  depo = NULL,
  hcr = NULL
)
dbsra_fmsym <- apply(dbsra$Btrend, 2, median)

ss_case_final <- ss_case
dbsra <- DLMtool::DBSRA(1, ss_case_final, plot = FALSE)

# Projection: case 0.3 --------------------------------------------------
projection_output3 <- list()
equi_year_temp <- list()
for (i in 1:length(projection_year)) {
  ss_case_temp <- ss_case_final
  
  equi_year_temp[[i]] <- equi_year
  # equi_year_temp[[i]] <- 2000:(2012+i-1)
  # equi_catch_temp <- rep(sa_data$fishery$obs_total_catch_biomass$fleet1[1], length = length(equi_year_temp[[i]])) * catch_multiplier
  equi_catch_temp <- rep(max(sa_data$fishery$obs_total_catch_biomass$fleet1), length = length(equi_year_temp[[i]])) * catch_multiplier
  # equi_id_temp <- as.numeric(names(sa_data$fishery$obs_total_catch_biomass$fleet1)) %in% equi_year_temp[[i]]
  # equi_catch_temp <- sa_data$fishery$obs_total_catch_biomass$fleet1[equi_id_temp]
  
  data_id <- as.numeric(names(sa_data$fishery$obs_total_catch_biomass$fleet1)) %in% c(model_year[1]:(projection_year[i] - 1))
  
  ss_case_temp@Cat <- matrix(c(equi_catch_temp, sa_data$fishery$obs_total_catch_biomass$fleet1[data_id]),
                             nrow = 1
  )
  ss_case_temp@Year <- ss_case_temp@Year[1]:(projection_year[i]-1)
  
  
  projection_output3[[i]] <- DLMtool::DBSRA_(
    x = 1,
    Data = ss_case_temp,
    depo = NULL, # Optional fixed depletion (single value)
    hcr = NULL # Optional harvest control rule for throttling catch as a function of B/B0.
  )
}

# plot figures
par(mfrow=c(1,2))
c_hist <- projection_output3[[1]]$C_hist
ylim <- range(c_hist[(length(equi_year_temp[[1]])+1):length(c_hist)], unlist(sapply(projection_output3, "[", "TAC")))
plot(c(ss_case_temp@Year[(length(equi_year_temp[[1]])+1):length(c_hist)], projection_year),
     c(c_hist[(length(equi_year_temp[[1]])+1):length(c_hist)], rep(NA, length(projection_year))),
     type = "l",
     ylim = ylim,
     xlab = "Year", ylab = "Catch (mt)"
)

for (i in 1:length(projection_year)) {
  boxplot(projection_output3[[i]]$TAC,
          add = TRUE,
          at = projection_year[i],
          col = "grey",
          width = 1,
          outline = TRUE,
          axes = FALSE
  )
}

catch_year <- projection_year[1:length(projection_year) - 1]
points(catch_year, sa_data$fishery$obs_total_catch_biomass$fleet1[names(sa_data$fishery$obs_total_catch_biomass$fleet1) %in% catch_year],
       pch = 16, col = "blue"
)

legend("top",
       c("Observed Catch", "Observed Catch for TAC estimates", "TAC"),
       lty = c(1, NA, NA),
       pch = c(NA, 16, NA),
       col = c("black", "blue", NA),
       fill = c(NA, NA, "gray"),
       border = c(NA, NA, "black"),
       bty = "n",
       title = "Case 0.3"
)

legend("left",
       c(
         paste0("DBSRA@Dep = ", round(ssd_dep$dep[which.min(ssd_dep$ssd)], digits = 2)),
         paste0("DBSRA@BMSY_B0 = ", round(ssd_bmsy_b0$bmsy_b0[which.min(ssd_bmsy_b0$ssd)], digits = 2)),
         paste0("DBSRA@FMSY_M = ", round(ssd_fmsy_m$fmsy_m[which.min(ssd_fmsy_m$ssd)], digits = 2))),
       bty="n")

# plot biomass
dbsraB_projection <- list()
for (i in 1:length(projection_year)){
  full_dbsraB <- projection_output3[[i]]$Btrend
  year_id <- projection_output3[[i]]
  dbsraB_projection[[i]] <- apply(full_dbsraB[, (length(equi_year_temp[[i]])+1):ncol(full_dbsraB)], 2, median)
}

ylim = range(biomass_ewe, unlist(dbsraB_projection))
plot(c(model_year, projection_year),
     biomass_ewe,
     xlab = "Year", ylab = "Biomass (mt)",
     ylim = ylim,
     pch = 16
)
for (i in 1:length(projection_year)){
  lines(model_year[1]:(projection_year[i]-1), dbsraB_projection[[i]],
        lty=i, col=i)
}
legend("bottomright",
       c("EWE", paste0("DBSRA", projection_year)),
       bty = "n",
       pch = c(16, rep(NA, length(projection_year))),
       lty = c(NA, 1:length(projection_year)),
       col = c(1, 1:length(projection_year)),
       title = "Case 0.3"
)



```

```{r}
print(cor(biomass_ewe[1:length(model_year)], dbsraB_projection[[1]]))
```
## Linear regression models from cases 1 - 4 using "true" values from EwE
- Case 1: Link Atlantic Multidecadal Oscillation Index with menhaden biomass estimates and adjust projections: AMO is an indicator of climate conditions and would affect recruitment variability of menhaden-like species
- Case 2: Link Palmer drought severity index with menhaden biomass estimates and adjust projections: PSDI is a long-term indicator of drought conditions and it reflects river discharge and precipitation
- Case 3: Link biomass of Striped bass from the EwE with menhaden biomass estimates and adjust projections because bass is a major predator
- Case 4: Link fishing effort of menhaden with menhaden biomass estimates and adjust projections 

- Linear regression models from case 1 - 4

```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
lm_slope <- data.frame(
  case = "True indices",
  amo = NA,
  pcp = NA,
  bassB = NA,
  price = NA,
  pdsi = NA,
  effort = NA
)

year_id <- seq(1, nrow(amo_unsmooth_lag1), by = 12)
index_year <- c(model_year, projection_year)
lag = 1
biomass_lag_id <- (1+lag):length(index_year)
index_lag_id <- 1:(length(index_year)-lag)

amo <- amo_unsmooth_lag1[year_id, ]
amo_lm <- lm(biomass_ewe[biomass_lag_id] ~ amo$scaled_value[index_lag_id])
amo_fit <- fitted(amo_lm)
lm_slope$amo <- paste0(
  round(summary(amo_lm)$coefficients[2, 1], digits = 2),
  if (summary(amo_lm)$coefficients[2, 4] <= 0.05) {
    "*"
  }
)

pcp <- precipitation[year_id, ]
pcp_lm <- lm(biomass_ewe[biomass_lag_id] ~ pcp$scaled_value[index_lag_id])
pcp_fit <- fitted(pcp_lm)
lm_slope$pcp <- paste0(
  round(summary(pcp_lm)$coefficients[2, 1], digits = 2),
  if(summary(pcp_lm)$coefficients[2, 4] <= 0.05) {"*"})

bassB <- bass_bio[bass_bio$Year %in% year_id, ]
bassB_lm <- lm(biomass_ewe[biomass_lag_id] ~ bassB$bass_bio[index_lag_id])
bassB_fit <- fitted(bassB_lm)
lm_slope$bassB <- paste0(
  round(summary(bassB_lm)$coefficients[2, 1], digits = 2),
  if(summary(bassB_lm)$coefficients[2, 4] <= 0.05) {"*"})

sub_menhadenP <- menhaden_price$Inflation.Adjust.Price.Per.MT[menhaden_price$Year %in% index_year]
price_lm <- lm(biomass_ewe[biomass_lag_id] ~ sub_menhadenP[index_lag_id])
price_fit <- fitted(price_lm)
lm_slope$price <- paste0(
  round(summary(price_lm)$coefficients[2, 1], digits = 2),
  if(summary(price_lm)$coefficients[2, 4] <= 0.05) {"*"})

pdsi <- palmer_drought_severity_index[year_id, ]
pdsi_lm <- lm(biomass_ewe[biomass_lag_id] ~ pdsi$scaled_value[index_lag_id])
pdsi_fit <- fitted(pdsi_lm)
lm_slope$pdsi <- paste0(
  round(summary(pdsi_lm)$coefficients[2, 1], digits = 2),
  if(summary(pdsi_lm)$coefficients[2, 4] <= 0.05) {"*"})

effort <- apply(ewe_faa[, grep("menhaden", colnames(ewe_faa))] / ewe_catchability[year_id, grep("menhaden", colnames(ewe_catchability))], 1, sum)
effort_lm <- lm(biomass_ewe[biomass_lag_id] ~ effort[index_lag_id])
effort_fit <- fitted(effort_lm)
lm_slope$effort <- paste0(
  round(summary(effort_lm)$coefficients[2, 1], digits = 2),
  if(summary(effort_lm)$coefficients[2, 4] <= 0.05) {"*"})

par(mfrow = c(3, 2))

plot(amo$scaled_value[index_lag_id], biomass_ewe[biomass_lag_id],
     xlab = "AMO values",
     ylab = "Biomass of menhaden-like species from OM"
)
abline(amo_lm)

plot(pcp$scaled_value[index_lag_id], biomass_ewe[biomass_lag_id],
     xlab = "Precipitation values",
     ylab = "Biomass of menhaden-like species from OM"
)
abline(pcp_lm)

plot(pdsi$scaled_value[index_lag_id], biomass_ewe[biomass_lag_id],
     xlab = "PDSI values",
     ylab = "Biomass of menhaden-like species from OM"
)
abline(pdsi_lm)

plot(bassB$bass_bio[index_lag_id], biomass_ewe[biomass_lag_id],
     xlab = "Biomass of Striped bass",
     ylab = "Biomass of menhaden-like species from OM"
)
abline(bassB_lm)

plot(sub_menhadenP[index_lag_id], biomass_ewe[biomass_lag_id],
     xlab = "Menhaden price",
     ylab = "Biomass of menhaden-like species from OM"
)
abline(price_lm)

plot(effort[index_lag_id], biomass_ewe[biomass_lag_id],
     xlab = "Fishing effort of menhaden-like species from OM",
     ylab = "Biomass of menhaden-like species from OM"
)
abline(effort_lm)

```

- Slope values from linear regression models

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
knitr::kable(lm_slope)
```

## Cases 1-4 are based on the settings from case 0.1
```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
# Projection based on case 0.1 ------------------------------------

output <- compare_projections_dbsra(
  case_name = 0.1,
  projection_output_data = projection_output1,
  projection_year = projection_year,
  model_year = model_year,
  lag = 1,
  amo = amo_unsmooth_lag1,
  pcp = precipitation,
  pdsi = palmer_drought_severity_index,
  bassB = bass_bio,
  price = menhaden_price,
  effort = apply(ewe_faa[ewe_faa$X %in% ewe_faa$X[1:length(year_id)] , grep("menhaden", colnames(ewe_faa))] / ewe_catchability[year_id, grep("menhaden", colnames(ewe_catchability))], 1, sum)
)

soi_data_melt <- output$soi_data_melt
ggplot(soi_data_melt[soi_data_melt$projection_year_id==tail(projection_year, n=1), ], aes(x = year, y = value)) +
  geom_line() +
  facet_wrap(~variable, scales = "free_y") +
  labs(
    title = "Case 0.1: Status of Indicators",
    x = "Year",
    y = "Status of Indicators"
  ) +
  theme_bw()

tac_data_melt <- output$tac_data_melt
# ggplot(tac_data_melt, aes(x=variable, y = value, color = projection_year_id)) +
#   geom_boxplot()+
#   labs(
#     title = "Case 0.1: TAC",
#     x = "",
#     y = "TAC"
#   ) +
#   theme_bw()

tac_data_melt_median <- output$tac_data_melt_median
ggplot(tac_data_melt_median, aes(x = projection_year_id, y = value, color = variable)) +
  geom_line() +
  labs(
    title = "Case 0.1: Median TAC from DBSRA and adjusted TAC",
    x = "",
    y = "TAC"
  ) +
  theme_bw()

```

- Slope values from linear regression models

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
knitr::kable(output$lm_slope)
```

## Cases 1-4 are based on the settings from case 0.2
```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
# Projection based on case 0.2 ------------------------------------

output <- compare_projections_dbsra(
  case_name = 0.2,
  projection_output_data = projection_output2,
  projection_year = projection_year,
  model_year = model_year,
  lag = 1,
  amo = amo_unsmooth_lag1,
  pcp = precipitation,
  pdsi = palmer_drought_severity_index,
  bassB = bass_bio,
  price = menhaden_price,
  effort = apply(ewe_faa[ewe_faa$X %in% ewe_faa$X[1:length(year_id)] , grep("menhaden", colnames(ewe_faa))] / ewe_catchability[year_id, grep("menhaden", colnames(ewe_catchability))], 1, sum)
)

soi_data_melt <- output$soi_data_melt
ggplot(soi_data_melt[soi_data_melt$projection_year_id==tail(projection_year, n=1), ], aes(x = year, y = value)) +
  geom_line() +
  facet_wrap(~variable, scales = "free_y") +
  labs(
    title = "Case 0.2: Status of Indicators",
    x = "Year",
    y = "Status of Indicators"
  ) +
  theme_bw()

tac_data_melt <- output$tac_data_melt
# ggplot(tac_data_melt, aes(x=variable, y = value, color = projection_year_id)) +
#   geom_boxplot()+
#   labs(
#     title = "Case 0.2: TAC",
#     x = "",
#     y = "TAC"
#   ) +
#   theme_bw()

tac_data_melt_median <- output$tac_data_melt_median
ggplot(tac_data_melt_median, aes(x = projection_year_id, y = value, color = variable)) +
  geom_line() +
  labs(
    title = "Case 0.2: Median TAC from DBSRA and adjusted TAC",
    x = "",
    y = "TAC"
  ) +
  theme_bw()
```

- Slope values from linear regression models

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
knitr::kable(output$lm_slope)
```

## Cases 1-4 are based on the settings from case 0.3
```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
# Projection based on case 0.3 ------------------------------------
projection_output3_clean <- list()

for (i in 1:length(projection_year)){
  temp <- projection_output3[[i]]
  temp$Btrend <- temp$Btrend[, (length(equi_year_temp[[i]])+1): ncol(temp$Btrend)]
  projection_output3_clean[[i]] <- temp
}
output <- compare_projections_dbsra(
  case_name = 0.3,
  projection_output_data = projection_output3_clean,
  projection_year = projection_year,
  model_year = model_year,
  lag = 1,
  amo = amo_unsmooth_lag1,
  pcp = precipitation,
  pdsi = palmer_drought_severity_index,
  bassB = bass_bio,
  price = menhaden_price,
  effort = apply(ewe_faa[ewe_faa$X %in% ewe_faa$X[1:length(year_id)] , grep("menhaden", colnames(ewe_faa))] / ewe_catchability[year_id, grep("menhaden", colnames(ewe_catchability))], 1, sum)
)

soi_data_melt <- output$soi_data_melt
ggplot(soi_data_melt[soi_data_melt$projection_year_id==tail(projection_year, n=1), ], aes(x = year, y = value)) +
  geom_line() +
  facet_wrap(~variable, scales = "free_y") +
  labs(
    title = "Case 0.3: Status of Indicators",
    x = "Year",
    y = "Status of Indicators"
  ) +
  theme_bw()

tac_data_melt <- output$tac_data_melt
# ggplot(tac_data_melt, aes(x=variable, y = value, color = projection_year_id)) +
#   geom_boxplot()+
#   labs(
#     title = "Case 0.3: TAC",
#     x = "",
#     y = "TAC"
#   ) +
#   theme_bw()

tac_data_melt_median <- output$tac_data_melt_median
ggplot(tac_data_melt_median, aes(x = projection_year_id, y = value, color = variable)) +
  geom_line() +
  labs(
    title = "Case 0.3: Median TAC from DBSRA and adjusted TAC",
    x = "",
    y = "TAC"
  ) +
  theme_bw()
```

- Slope values from linear regression models

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
knitr::kable(output$lm_slope)
```
