---
title: 'Ecological and single-species reference points'
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: TRUE
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.width = 12,
  fig.height = 10,
  results = "asis"
)
options(scipen = 1, digits = 4)
```

```{r utils, include=FALSE}
devtools::load_all()
library(tidyr)
read_fmsy_table <- function(file_names,
                            skip_nrows = 12,
                            colnames = c(
                              "Group", "TL", "Fbase", "Cbase",
                              "Vbase", "FmsyFound", "Fmsy", "Cmsy", "Vmsy", "CmsyAll", "VmsyAll"
                            ),
                            functional_groups) {
  data <- vector(mode = "list", length = length(file_names))

  for (file_id in 1:length(file_names)) {
    temp <- scan(file.path(file_names[file_id]), what = "", sep = "\n")
    data[[file_id]] <- temp[-c(1:skip_nrows)]
    data[[file_id]] <- read.table(
      text = as.character(data[[file_id]]),
      sep = ",",
      col.names = c(
        "Group", "TL", "Fbase", "Cbase",
        "Vbase", "FmsyFound", "Fmsy", "Cmsy", "Vmsy", "CmsyAll", "VmsyAll"
      )
    )
    data[[file_id]]$Group[grep("menhaden", data[[file_id]]$Group)] <- paste("Case stock", c(0:5, "6+"))
    data[[file_id]] <- data[[file_id]][grep("Case stock", data[[file_id]]$Group), colnames]
  }
  return(data)
}
```

# Evaluation of equilibrium MSY reference points from EwE user manual
- Single-species FMSY (stationary FMSY)
  - Run the Ecosim model to equilibrium for a range of F values while holding biomasses of all other groups constant (except other life history stanzas for the same species in split and multi-stanza cases) 
  - Examine predicted compensatory responses by the group caused by the foraging arena functional response and related foraging time adjustment parameters
- Ecological FMSY (compensatory FMSY)
  - Allows all groups' biomass to change in response to the biomass changes of the focal FMSY groups
  - The assessment usually produces a more optimistic estimate of MSY for each group
  - Increases in food species abundances and decreases in predator abundances when any one group is harvested harder


# Output comparison
## Run model to get compensation FMSY vs stationary FMSY
```{r compensation-vs-stationary-fmsy, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
functional_groups <- c(
  "StripedBass0",
  "StripedBass2_5",
  "StripedBass6",
  "AtlanticMenhaden0",
  "AtlanticMenhaden1",
  "AtlanticMenhaden2",
  "AtlanticMenhaden3",
  "AtlanticMenhaden4",
  "AtlanticMenhaden5",
  "AtlanticMenhaden6",
  "SpinyDogfish",
  "BluefishJuvenile",
  "BluefishAdult",
  "WeakfishJuvenile",
  "WeakfishAdult",
  "AtlanticHerring0_1",
  "AtlanticHerring2",
  "Anchovies",
  "Benthos",
  "Zooplankton",
  "Phytoplankton",
  "Detritus"
)
ages <- 0:6
age_name <- paste0("AtlanticMenhaden", ages)

# base scenario
compensation_fmsy_s1 <- read_fmsy_table(
  file_names = here::here(
    "data", "ewe", "7ages_ecosim_om_msy",
    paste0("msy_base_run_age", ages), "FMSY_fullCompensation.csv"
  ),
  colnames = "Fmsy",
  functional_groups = functional_groups
)
compensation_fmsy_s1 <- c(
  compensation_fmsy_s1,
  read_fmsy_table(
    file_names = here::here(
      "data", "ewe", "7ages_ecosim_om_msy",
      "msy_base_run_fleet", "FMSY_fullCompensation.csv"
    ),
    colnames = "Fmsy",
    functional_groups = functional_groups
  )
)

stationary_fmsy_s1 <- read_fmsy_table(
  file_names = here::here(
    "data", "ewe", "7ages_ecosim_om_msy",
    paste0("msy_base_run_age", ages), "FMSY_StationarySystem.csv"
  ),
  colnames = "Fmsy",
  functional_groups = functional_groups
)
stationary_fmsy_s1 <- c(
  stationary_fmsy_s1,
  read_fmsy_table(
    file_names = here::here(
      "data", "ewe", "7ages_ecosim_om_msy",
      "msy_base_run_fleet", "FMSY_StationarySystem.csv"
    ),
    colnames = "Fmsy",
    functional_groups = functional_groups
  )
)


mean_difference <- all.equal(current = stationary_fmsy_s1, target = compensation_fmsy_s1)
mean_difference_value <- as.numeric(sapply(strsplit(mean_difference, " "), "[[", 6))
var_s1 <- var(mean_difference_value)

# Environmental forcing scenario
compensation_fmsy_s2 <- read_fmsy_table(
  file_names = here::here(
    "data", "ewe", "7ages_ecosim_om_msy",
    paste0("msy_forcing_pdsi_egg_amo1_age", ages), "FMSY_fullCompensation.csv"
  ),
  colnames = "Fmsy",
  functional_groups = functional_groups
)
compensation_fmsy_s2 <- c(
  compensation_fmsy_s2,
  read_fmsy_table(
    file_names = here::here(
      "data", "ewe", "7ages_ecosim_om_msy",
      "msy_forcing_pdsi_egg_amo1_fleet", "FMSY_fullCompensation.csv"
    ),
    colnames = "Fmsy",
    functional_groups = functional_groups
  )
)

stationary_fmsy_s2 <- read_fmsy_table(
  file_names = here::here(
    "data", "ewe", "7ages_ecosim_om_msy",
    paste0("msy_forcing_pdsi_egg_amo1_age", ages), "FMSY_StationarySystem.csv"
  ),
  colnames = "Fmsy",
  functional_groups = functional_groups
)
stationary_fmsy_s2 <- c(
  stationary_fmsy_s2,
  read_fmsy_table(
    file_names = here::here(
      "data", "ewe", "7ages_ecosim_om_msy",
      "msy_forcing_pdsi_egg_amo1_fleet", "FMSY_StationarySystem.csv"
    ),
    colnames = "Fmsy",
    functional_groups = functional_groups
  )
)
mean_difference <- all.equal(current = stationary_fmsy_s2, target = compensation_fmsy_s2)
mean_difference_value <- as.numeric(sapply(strsplit(mean_difference, " "), "[[", 6))
var_s2 <- var(mean_difference_value)
if (var_s1 == 0 & var_s2 == 0) {
  cat("- Mean relative differences between compensation and stationary FMSYs across 7 age classes from scenarios S1 and S2 = ", unique(mean_difference_value), "\n")
} else {
  cat("- Mean relative differences between compensation and stationary FMSYs vary by age groups\n")
}
```

## Run model by functional group vs by fleet 
```{r group-vs-fleet-fmsy, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
mean_difference <- c()
list_length <- length(compensation_fmsy_s1)

# base scenario
for (i in seq_along(compensation_fmsy_s1)) {
  mean_difference[i] <- all.equal(current = compensation_fmsy_s1[[list_length]], target = compensation_fmsy_s1[[i]])
}

compensation_mean_difference_s1 <- all(mean_difference)

for (i in seq_along(stationary_fmsy_s1)) {
  mean_difference[i] <- all.equal(current = stationary_fmsy_s1[[list_length]], target = stationary_fmsy_s1[[i]])
}

stationary_mean_difference_s1 <- all(mean_difference)

# environmental forcing scenario
for (i in seq_along(compensation_fmsy_s2)) {
  mean_difference[i] <- all.equal(current = compensation_fmsy_s2[[list_length]], target = compensation_fmsy_s2[[i]])
}

compensation_mean_difference_s2 <- all(mean_difference)

for (i in seq_along(stationary_fmsy_s2)) {
  mean_difference[i] <- all.equal(current = stationary_fmsy_s2[[list_length]], target = stationary_fmsy_s2[[i]])
}

stationary_mean_difference_s2 <- all(mean_difference)

if (all(c(compensation_mean_difference_s1, stationary_mean_difference_s1, compensation_mean_difference_s2, stationary_mean_difference_s2))) {
  cat("- FMSYs by functional group are identical to FMSYs by fleet\n")
} else {
  cat("- FMSYs by functional group are different to FMSYs by fleet\n")
}
```

## Run model to equilibrium for a range of F values vs run to depletion
```{r maxF-vs-depletion, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
msy_ages_label <- c(0:5, "6+")
maxF_file_path <- here::here(
  "data", "ewe", "7ages_ecosim_om_msy",
  paste0("msy_forcing_pdsi_egg_amo1_age", ages, "_details")
)
maxF_file_path <- c(
  maxF_file_path,
  here::here("data", "ewe", "7ages_ecosim_om_msy", "msy_forcing_pdsi_egg_amo1_fleet_details")
)

catch_file_names <- c(paste0("menhaden ", msy_ages_label, "_Catch_FullCompensation.csv"), "F.menhaden_Catch_FullCompensation.csv")
biomass_file_names <- c(paste0("menhaden ", msy_ages_label, "_B_FullCompensation.csv"), "F.menhaden_B_FullCompensation.csv")
compensation_msy_maxF <- list()

for (i in seq_along(maxF_file_path)) {
  compensation_msy_maxF[[i]] <- read_ewe_reference_points(
    file_path = maxF_file_path[i],
    file_names = c(
      catch_file_names[i],
      biomass_file_names[i]
    ),
    reference_points_scenario = "compensation",
    functional_groups = functional_groups,
    key_functional_group = "AtlanticMenhaden",
    ages = ages,
    plot = FALSE
  )
}

depletion_file_path <- here::here(
  "data", "ewe", "7ages_ecosim_om_msy",
  paste0("msy_forcing_pdsi_egg_amo1_age", ages, "_details_depletion")
)
depletion_file_path <- c(
  depletion_file_path,
  here::here("data", "ewe", "7ages_ecosim_om_msy", "msy_forcing_pdsi_egg_amo1_fleet_details_depletion")
)

compensation_msy_depletion <- list()

for (i in seq_along(maxF_file_path)) {
  compensation_msy_depletion[[i]] <- read_ewe_reference_points(
    file_path = depletion_file_path[i],
    file_names = c(
      catch_file_names[i],
      biomass_file_names[i]
    ),
    reference_points_scenario = "compensation",
    functional_groups = functional_groups,
    key_functional_group = "AtlanticMenhaden",
    ages = ages,
    plot = FALSE
  )
}

result_compensation <- all.equal(current = compensation_msy_maxF, target = compensation_msy_depletion)

catch_file_names <- c(paste0("menhaden ", msy_ages_label, "_Catch_StationarySystem.csv"), "F.menhaden_Catch_StationarySystem.csv")
biomass_file_names <- c(paste0("menhaden ", msy_ages_label, "_B_StationarySystem.csv"), "F.menhaden_B_StationarySystem.csv")
stationary_msy_maxF <- list()

for (i in seq_along(maxF_file_path)) {
  stationary_msy_maxF[[i]] <- read_ewe_reference_points(
    file_path = maxF_file_path[i],
    file_names = c(
      catch_file_names[i],
      biomass_file_names[i]
    ),
    reference_points_scenario = "stationary",
    functional_groups = functional_groups,
    key_functional_group = "AtlanticMenhaden",
    ages = ages,
    plot = FALSE
  )
}

stationary_msy_depletion <- list()
for (i in seq_along(maxF_file_path)) {
  stationary_msy_depletion[[i]] <- read_ewe_reference_points(
    file_path = depletion_file_path[i],
    file_names = c(
      catch_file_names[i],
      biomass_file_names[i]
    ),
    reference_points_scenario = "stationary",
    functional_groups = functional_groups,
    key_functional_group = "AtlanticMenhaden",
    ages = ages,
    plot = FALSE
  )
}


result_stationary <- all.equal(current = stationary_msy_maxF, target = stationary_msy_depletion)
if (all(c(result_compensation, result_stationary))) {
  cat("- FMSYs from the two searching methods are identical\n")
} else {
  cat("- FMSYs from the two searching methods are different\n")
}
```

## Single FMSY vs multiple FMSYs

- EwE default summary output files (e.g., FMSY_FullCompensation.csv or FMSY_StationarySystem.csv) show the estimate of FMSY for each functional group (Table 1-4).
- EwE also produces the catch of each functional group over a range of F values in F.menhaden_Catch_FullCompensation.csv or F.menhaden_Catch_StationarySystem.csv.
- How EwE summarizes FMSY-at-age is unclear. I could not reproduce the summarized FMSY-at-age from the catch over F table.
- How to extract a FMSY value from EwE output to compare it with a single-species FMSY?

```{r singleFMSY-vs-multipleFMSY, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
compensation_fmsy_s1 <- read_fmsy_table(
  file_names = here::here(
    "data", "ewe", "7ages_ecosim_om_msy",
    "msy_base_run_fleet", "FMSY_fullCompensation.csv"
  ),
  colnames = c(
    "Group", "TL", "Fbase", "Cbase",
    "Vbase", "FmsyFound", "Fmsy", "Cmsy", "Vmsy"
  ),
  functional_groups = functional_groups
)

stationary_fmsy_s1 <- read_fmsy_table(
  file_names = here::here(
    "data", "ewe", "7ages_ecosim_om_msy",
    "msy_base_run_fleet", "FMSY_StationarySystem.csv"
  ),
  colnames = c(
    "Group", "TL", "Fbase", "Cbase",
    "Vbase", "FmsyFound", "Fmsy", "Cmsy", "Vmsy"
  ),
  functional_groups = functional_groups
)

knitr::kable(compensation_fmsy_s1,
  caption = "Table 1. Base scenario S1 compensation FMSY output from EwE"
)
knitr::kable(stationary_fmsy_s1,
  caption = "Table 2. Base scenario S1 stationary FMSY output from EwE"
)

compensation_fmsy_s2 <- read_fmsy_table(
  file_names = here::here(
    "data", "ewe", "7ages_ecosim_om_msy",
    "msy_forcing_pdsi_egg_amo1_fleet", "FMSY_fullCompensation.csv"
  ),
  colnames = c(
    "Group", "TL", "Fbase", "Cbase",
    "Vbase", "FmsyFound", "Fmsy", "Cmsy", "Vmsy"
  ),
  functional_groups = functional_groups
)
stationary_fmsy_s2 <- read_fmsy_table(
  file_names = here::here(
    "data", "ewe", "7ages_ecosim_om_msy",
    "msy_forcing_pdsi_egg_amo1_fleet", "FMSY_StationarySystem.csv"
  ),
  colnames = c(
    "Group", "TL", "Fbase", "Cbase",
    "Vbase", "FmsyFound", "Fmsy", "Cmsy", "Vmsy"
  ),
  functional_groups = functional_groups
)

knitr::kable(compensation_fmsy_s2,
  caption = "Table 3. Environmental forcing scenario S2 compensation FMSY output from EwE"
)
knitr::kable(stationary_fmsy_s2,
  caption = "Table 4. Environmental forcing scenario S2 stationary FMSY output from EwE"
)

multiple_reference_points <- function(file_path,
                                      file_names,
                                      functional_groups,
                                      key_functional_group,
                                      ages,
                                      reference_points_scenario,
                                      plot) {
  msy_fleet <- read_ewe_output(
    file_path = file_path,
    file_names = file_names,
    skip_nrows = 12,
    colname_1 = "FM",
    plot = FALSE,
    figure_titles = NULL,
    functional_groups = functional_groups,
    figure_colors = NULL
  )

  catch_max_id <- MSY <- FMSY <- BMSY <- c()
  catch_max <- apply(msy_fleet[[1]][, paste0(key_functional_group, ages)], 2, max)
  for (i in seq_along(catch_max)) {
    catch_max_id[i] <- which(msy_fleet[[1]][, age_name[i]] == catch_max[i])
    MSY[i] <- msy_fleet[[1]][catch_max_id[i], age_name[i]]
    FMSY[i] <- msy_fleet[[1]]$FM[catch_max_id[i]]
    BMSY[i] <- msy_fleet[[2]][catch_max_id[i], age_name[i]]
  }
  MSY_data <- list(MSY = MSY, FMSY = FMSY, BMSY = BMSY)

  if (plot == TRUE) {
    pdf(file = file.path(file_path, paste0(reference_points_scenario, "_yield_over_F.pdf")), onefile = T)
    plot(msy_fleet[[1]]$FM, catch_sum,
      xlab = "F", ylab = "Yield",
      pch = 16, type = "o"
    )
    abline(h = MSY, lty = 2)
    abline(v = FMSY, lty = 3)
    dev.off()
  }

  return(MSY_data)
}
```
