---
title: 'Data-rich stock assessment with new EwE OM'
date: 'Updated on July 28, 2022'
output:
  html_document: 
    code_folding: hide
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Stock Synthesis 3 (SS3)

- Using Stock Synthesis 3 v3.30.19.01
- Website: https://github.com/nmfs-stock-synthesis/stock-synthesis

```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
devtools::load_all()

required_pkg <- c(
  "devtools", "here", "reshape",
  "ggplot2", "reshape2",
  "RColorBrewer", "scales", "fmsb", 
  "PBSadmb"
)

pkg_to_install <- required_pkg[!(required_pkg %in%
  installed.packages()[, "Package"])]
if (length(pkg_to_install)) install.packages(pkg_to_install)

lapply(required_pkg, library, character.only = TRUE)

devtools::install_github("r4ss/r4ss",
  ref = "c53f82fcfb3f54296d79ba3a4163990150981285"
)
library(r4ss)
```

## Case 0: stock assessment base run

```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
# Load simulated input data
source(here::here("Rscript", "simulation_newEcosim.R"))
file_path <- here::here("data", "ewe", "7ages_newsim_final", "ewe7ages_ecosim_final", "ecosim_forcing_pdsi_egg_amo1")
source(here::here("Rscript", "load_indices.R"))
file_path <- here::here("data", "data_rich", "OM2")
originalwd <- getwd()

depletion <- FALSE
depletion_ratio <- 0.8 # tried values between 0.3 - 0.8

model_year <- 1985:2012
projection_year <- 2013:2017

generate_ss3(
  file_path = file_path,
  r0 = 12, steepness = 0.55, sigmar = 0.5,
  projection_f = 0.75, projection_catch = NULL,
  sa_data = sa_data, model_year = model_year,
  projection_year = projection_year,
  use_depletion = FALSE, depletion_ratio = NULL,
  initial_equilibrium_catch = TRUE
)

# Run SS3 ----------------------------------------------------------

setwd(file_path)
system(paste(file.path(file_path, "ss_win.exe"), file.path(file_path, "data.ss"), sep = " "), show.output.on.console = TRUE)

# get FMSY
ss3list <- SS_output(
  dir = file_path,
  verbose = TRUE,
  printstats = TRUE
)

fmsy <- ss3list$derived_quants$Value[ss3list$derived_quants$Label == "annF_MSY"]

# Re-run SS3 with projection_f = fmsy
generate_ss3(
  file_path = file_path,
  r0 = 12, steepness = 0.55, sigmar = 0.5,
  projection_f = fmsy, projection_catch = NULL,
  sa_data = sa_data, model_year = model_year,
  projection_year = projection_year,
  use_depletion = FALSE, depletion_ratio = NULL,
  initial_equilibrium_catch = TRUE
)

system(paste(file.path(file_path, "ss_win.exe"), file.path(file_path, "data.ss"), sep = " "), show.output.on.console = TRUE)
on.exit(setwd(originalwd), add = TRUE)

# plot r4ss -------------------------------------------------------

# read the model output and print diagnostic messages
ss3list <- SS_output(
  dir = file_path,
  verbose = TRUE,
  printstats = TRUE
)

# plots the results
# SS_plots(ss3list)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}

# Compare SS3 estimate with EwE "true" values ---------------------
# Comparisons
project_path <- here::here()
ewe_output_path <- file.path(project_path, "data", "ewe", "7ages_newsim_final", "ewe7ages_ecosim_final", "ecosim_forcing_pdsi_egg_amo1")
# Comparisons
functional_groups <- c(
  "StripedBass0",
  "StripedBass2_5",
  "StripedBass6",
  "AtlanticMenhaden0",
  "AtlanticMenhaden1",
  "AtlanticMenhaden2",
  "AtlanticMenhaden3",
  "AtlanticMenhaden4",
  "AtlanticMenhaden5",
  "AtlanticMenhaden6",
  "SpinyDogfish",
  "BluefishJuvenile",
  "BluefishAdult",
  "WeakfishJuvenile",
  "WeakfishAdult",
  "AtlanticHerring0_1",
  "AtlanticHerring2",
  "Anchovies",
  "Benthos",
  "Zooplankton",
  "Phytoplankton",
  "Detritus"
)

age_name <- paste0("AtlanticMenhaden", 0:6)

# Biomass
biomass <- read_ewe_output(
  file_path = ewe_output_path,
  file_names = "biomass_monthly.csv",
  skip_nrows = 8,
  plot = FALSE,
  figure_titles = NULL,
  functional_groups = functional_groups,
  figure_colors = NULL
)

time_id <- seq(1, nrow(biomass[[1]]), by = 12)
biomass_ewe <- apply(biomass[[1]][, age_name], 1, sum) * 1000000

par(mfrow = c(2, 2))
model_year_id <- which(ss3list$timeseries$Yr %in% model_year)
projection_year_id <- which(ss3list$timeseries$Yr %in% projection_year)
ylim <- range(biomass_ewe[time_id], ss3list$timeseries$Bio_all)
plot(c(model_year, projection_year),
  biomass_ewe[time_id],
  xlab = "Year", ylab = "Biomass (mt)",
  ylim = ylim,
  pch = 16
)
lines(model_year, ss3list$timeseries$Bio_all[model_year_id], lty = 1)
# par(new = TRUE)
# plot(model_year, ss3list$timeseries$Bio_all[model_year_id], lty = 1, type = "l", axes = FALSE, xlab = "", ylab = "")
lines(projection_year,
  ss3list$timeseries$Bio_all[projection_year_id],
  lty = 2
)
# axis(side = 4, at = pretty(range(ss3list$timeseries$Bio_all[model_year_id])))
legend("topleft",
  c("EWE", "SS3 Estimation", "SS3 projection"),
  bty = "n",
  pch = c(16, NA, NA),
  lty = c(NA, 1, 2)
)
# cor(biomass_ewe[time_id], c(ss3list$timeseries$Bio_all[model_year_id], ss3list$timeseries$Bio_all[projection_year_id]))

# Abundance
waa <- read_ewe_output(
  file_path = ewe_output_path,
  file_names = "weight_monthly.csv",
  skip_nrows = 8,
  plot = FALSE,
  figure_titles = NULL,
  functional_groups = functional_groups,
  figure_colors = NULL
)

abundance_ewe <- apply(biomass[[1]][, age_name] * 1000000 / waa[[1]][, age_name], 1, sum)[time_id]

ylim <- range(abundance_ewe, ss3list$timeseries$`SmryNum_SX:1_GP:1` * 1000)
plot(c(model_year, projection_year),
  abundance_ewe,
  xlab = "Year", ylab = "Abundance (x1000 fish)",
  ylim = ylim,
  pch = 16
)
lines(model_year, ss3list$timeseries$`SmryNum_SX:1_GP:1`[model_year_id] * 1000, lty = 1)
# par(new = TRUE)
# plot(model_year, ss3list$timeseries$`SmryNum_SX:1_GP:1`[model_year_id] * 1000, lty = 1, type = "l", axes = FALSE, xlab = "", ylab = "")
# axis(side = 4, at = pretty(range(ss3list$timeseries$`SmryNum_SX:1_GP:1`[model_year_id] * 1000)))
lines(projection_year,
  ss3list$timeseries$`SmryNum_SX:1_GP:1`[projection_year_id] * 1000,
  lty = 2
)
legend("topright",
  c("EWE", "SS3 Estimation", "SS3 projection"),
  bty = "n",
  pch = c(16, NA, NA),
  lty = c(NA, 1, 2)
)

# cor(abundance_ewe, c(ss3list$timeseries$`SmryNum_SX:1_GP:1`[model_year_id] * 1000, ss3list$timeseries$`SmryNum_SX:1_GP:1`[projection_year_id] * 1000))
# Recruitment
waa <- read_ewe_output(
  file_path = ewe_output_path,
  file_names = "weight_monthly.csv",
  skip_nrows = 8,
  plot = FALSE,
  figure_titles = NULL,
  functional_groups = functional_groups,
  figure_colors = NULL
)

recruit_ewe <- biomass[[1]][, "AtlanticMenhaden0"][time_id] * 1000000 / waa[[1]][, "AtlanticMenhaden0"][time_id]

recruit_ss3 <- data.frame(
  year = c(model_year, projection_year),
  recruit = ss3list$natage$`1`[which(ss3list$natage$`Beg/Mid` == "B" & ss3list$natage$Yr %in% c(model_year, projection_year))] * 1000
)


ylim <- range(recruit_ewe, recruit_ss3$recruit)
plot(c(model_year, projection_year),
  recruit_ewe,
  xlab = "Year", ylab = "Abundance of age-0 fish (x1000 fish)",
  ylim = ylim,
  pch = 16
)
lines(model_year, recruit_ss3$recruit[recruit_ss3$year %in% model_year],
  lty = 1
)
# par(new = TRUE)
# plot(model_year, recruit_ss3$recruit[recruit_ss3$year %in% model_year],
#   lty = 1, type = "l", axes = FALSE, xlab = "", ylab = ""
# )
# axis(side = 4, at = pretty(range(recruit_ss3$recruit[recruit_ss3$year %in% model_year])))
lines(projection_year,
  recruit_ss3$recruit[recruit_ss3$year %in% projection_year],
  lty = 2
)
legend("topright",
  c("EWE", "SS3 Estimation", "SS3 projection"),
  bty = "n",
  pch = c(16, NA, NA),
  lty = c(NA, 1, 2)
)

# Mortality
# mortality <- read.csv(file = here::here("data", "ewe", "7ages", "updated_f.csv"))
# mortality_ewe <- apply(mortality[seq(1, nrow(mortality), by=12), grep("AtlanticMenhaden", colnames(mortality))], 1, max)

mortality <- read.csv(file = here::here("data", "ewe", "7ages_newsim_final", "fatage.csv"))
mortality_ewe <- apply(mortality[, 2:ncol(mortality)], 1, max)
# mortality_ewe <- apply(mortality[, 2:ncol(mortality)], 1, mean)

ylim <- range(mortality_ewe, ss3list$timeseries$`F:_1`)
plot(c(model_year, projection_year),
  mortality_ewe,
  xlab = "Year", ylab = "Mortality",
  ylim = ylim,
  pch = 16
)
lines(model_year, ss3list$timeseries$`F:_1`[model_year_id],
  lty = 1
)
# par(new = TRUE)
# plot(model_year, ss3list$timeseries$`F:_1`[model_year_id],
#   lty = 1, type = "l", , axes = FALSE, xlab = "", ylab = ""
# )
# axis(side = 4, at = pretty(range(ss3list$timeseries$`F:_1`[model_year_id])))
lines(projection_year,
  ss3list$timeseries$`F:_1`[projection_year_id],
  lty = 2
)
legend("topright",
  c("EWE F", "SS3 F", "SS3 FMSY"),
  bty = "n",
  pch = c(16, NA, NA),
  lty = c(NA, 1, 2)
)
```

## Cases 1-4 are based on the settings from case 0
- Case 1: Link Atlantic Multidecadal Oscillation Index with menhaden biomass estimates and adjust projections: AMO is an indicator of climate conditions and would affect recruitment variability of menhaden-like species
- Case 2: Link Palmer drought severity index with menhaden biomass estimates and adjust projections: PSDI is a long-term indicator of drought conditions and it reflects river discharge and precipitation
- Case 3: Link biomass of Striped bass from the EwE with menhaden biomass estimates and adjust projections because bass is a major predator
- Case 4: Link fishing effort of menhaden with menhaden biomass estimates and adjust projections 
- Linear regression models from case 1 - 4
  - True biomass of menhaden-like species as functions of AMO, PDSI, biomass of striped bass, and fishing effort of menhaden
  
### Status of indicators (SOI)

- If stock-indicator relationship is positive, $SOI_{y} = \frac{I_{y}-I_{y}^{min}}{I_{y}^{max}-I_{y}^{min}}$

- If stock-indicator relationship is negative, $SOI_{y} = 1-\frac{I_{y}-I_{y}^{min}}{I_{y}^{max}-I_{y}^{min}}$

where $I_{y}$ represents indicator value in year y. $I_{y}^{min}$ and $I_{y}^{max}$ represent the minimum and maximum values of $I$ from the time series.

```{r,  echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}

lm_slope <- data.frame(
  case = "True indices",
  amo = NA,
  # pcp = NA,
  bassB = NA,
  # price = NA,
  pdsi = NA,
  effort = NA
)

year_id <- seq(1, nrow(amo_unsmooth_lag1), by = 12)
index_year <- c(model_year, projection_year)
lag <- 1
biomass_lag_id <- (1 + lag):length(index_year)
index_lag_id <- 1:(length(index_year) - lag)

amo <- amo_unsmooth_lag1[year_id, ]
amo_lm <- lm(biomass_ewe[time_id][biomass_lag_id] ~ amo$scaled_value[index_lag_id])
amo_fit <- fitted(amo_lm)
lm_slope$amo <- paste0(
  round(summary(amo_lm)$coefficients[2, 1], digits = 2),
  if (summary(amo_lm)$coefficients[2, 4] <= 0.05) {
    "*"
  }
)

# pcp <- precipitation[year_id, ]
# pcp_lm <- lm(biomass_ewe[time_id][biomass_lag_id] ~ pcp$scaled_value[index_lag_id])
# pcp_fit <- fitted(pcp_lm)
# lm_slope$pcp <- paste0(
#   round(summary(pcp_lm)$coefficients[2, 1], digits = 2),
#   if(summary(pcp_lm)$coefficients[2, 4] <= 0.05) {"*"})

pdsi <- palmer_drought_severity_index[year_id, ]
pdsi_lm <- lm(biomass_ewe[time_id][biomass_lag_id] ~ pdsi$scaled_value[index_lag_id])
pdsi_fit <- fitted(pdsi_lm)
lm_slope$pdsi <- paste0(
  round(summary(pdsi_lm)$coefficients[2, 1], digits = 2),
  if (summary(pdsi_lm)$coefficients[2, 4] <= 0.05) {
    "*"
  }
)

bassB <- bass_bio[bass_bio$Year %in% year_id, ]
bassB_lm <- lm(biomass_ewe[time_id][biomass_lag_id] ~ bassB$bass_bio[index_lag_id])
bassB_fit <- fitted(bassB_lm)
lm_slope$bassB <- paste0(
  round(summary(bassB_lm)$coefficients[2, 1], digits = 2),
  if (summary(bassB_lm)$coefficients[2, 4] <= 0.05) {
    "*"
  }
)

# sub_menhadenP <- menhaden_price$Inflation.Adjust.Price.Per.MT[menhaden_price$Year %in% index_year]
# price_lm <- lm(biomass_ewe[time_id][biomass_lag_id] ~ sub_menhadenP[index_lag_id])
# price_fit <- fitted(price_lm)
# lm_slope$price <- paste0(
#   round(summary(price_lm)$coefficients[2, 1], digits = 2),
#   if(summary(price_lm)$coefficients[2, 4] <= 0.05) {"*"})

effort <- apply(ewe_faa[, grep("menhaden", colnames(ewe_faa))] / ewe_catchability[year_id, grep("menhaden", colnames(ewe_catchability))], 1, sum)
effort_lm <- lm(biomass_ewe[time_id][biomass_lag_id] ~ effort[index_lag_id])
effort_fit <- fitted(effort_lm)
lm_slope$effort <- paste0(
  round(summary(effort_lm)$coefficients[2, 1], digits = 2),
  if (summary(effort_lm)$coefficients[2, 4] <= 0.05) {
    "*"
  }
)

par(mfrow = c(2, 2))

plot(amo$scaled_value[index_lag_id], biomass_ewe[time_id][biomass_lag_id],
  xlab = "AMO values",
  ylab = "Biomass of menhaden-like species from OM"
)
abline(amo_lm)

# plot(pcp$scaled_value[index_lag_id], biomass_ewe[time_id][biomass_lag_id],
#      xlab = "Precipitation values",
#      ylab = "Biomass of menhaden-like species from OM"
# )
# abline(pcp_lm)

plot(pdsi$scaled_value[index_lag_id], biomass_ewe[time_id][biomass_lag_id],
  xlab = "PDSI values",
  ylab = "Biomass of menhaden-like species from OM"
)
abline(pdsi_lm)

plot(bassB$bass_bio[index_lag_id], biomass_ewe[time_id][biomass_lag_id],
  xlab = "Biomass of Striped bass",
  ylab = "Biomass of menhaden-like species from OM"
)
abline(bassB_lm)

# plot(sub_menhadenP[index_lag_id], biomass_ewe[time_id][biomass_lag_id],
#      xlab = "Menhaden price",
#      ylab = "Biomass of menhaden-like species from OM"
# )
# abline(price_lm)

plot(effort[index_lag_id], biomass_ewe[time_id][biomass_lag_id],
  xlab = "Fishing effort of menhaden-like species from OM",
  ylab = "Biomass of menhaden-like species from OM"
)
abline(effort_lm)
```
  
### Adjust projection

- If $\frac{B2012_{i}}{BMSY} > 1$, $F^{'}_{i} = FMSY^{min} + SOI2012 \times (FMSY^{max}-FMSY^{min})$

- If $\frac{B2012_{i}}{BMSY} \le 1$ and $\frac{B2012_{i}}{BMSY} > 0.5$, $F^{'}_{i} = SOI2012 \times \frac{B2012_{i}}{BMSY} \times FMSY_{i}$

- If $\frac{B2012_{i}}{BMSY} \le 0.5$, $F^{'}_{i} = 0$

where $i$ represents individual iterations
  
```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}

# Projection: cases 1 - 4 ---------------------------

lm_slope <- data.frame(
  case = "PDSI+AMO1 Case",
  projection_year = 1:length(projection_year),
  amo = NA,
  pdsi = NA,
  bassB = NA,
  effort = NA
)

for (projection_year_id in 1:length(projection_year)) {

  # if (projection_year_id ==1) {
  #   menhaden_b <- ss3list$timeseries$Bio_all[model_year_id]
  # } else {
  #   menhaden_b <- c(ss3list$timeseries$Bio_all[model_year_id], ss3list$timeseries$Bio_all[1:(projection_year_id-1)])
  # }
  #
  #
  # year_id <- seq(1, nrow(amo_unsmooth_lag1), by = 12)[1:(length(model_year)+projection_year_id-1)]
  #
  # if (projection_year_id == 1) {
  #   index_year = model_year
  # } else {
  #   index_year <- c(model_year, projection_year[1:(projection_year_id-1)])
  # }

  menhaden_b <- ss3list$timeseries$Bio_all[model_year_id]

  year_id <- seq(1, nrow(amo_unsmooth_lag1), by = 12)[1:length(model_year)]

  index_year <- model_year

  # Linear regression model -----------------------------------------

  lag <- 1
  biomass_lag_id <- (1 + lag):length(index_year)
  index_lag_id <- 1:(length(index_year) - lag)

  amo <- amo_unsmooth_lag1[year_id, ]
  amo_lm <- lm(menhaden_b[biomass_lag_id] ~ amo$scaled_value[index_lag_id])
  amo_fit <- fitted(amo_lm)
  lm_slope$amo <- paste0(
    round(summary(amo_lm)$coefficients[2, 1], digits = 2),
    if (summary(amo_lm)$coefficients[2, 4] <= 0.05) {
      "*"
    }
  )

  pdsi <- palmer_drought_severity_index[year_id, ]
  pdsi_lm <- lm(menhaden_b[biomass_lag_id] ~ pdsi$scaled_value[index_lag_id])
  pdsi_fit <- fitted(pdsi_lm)
  lm_slope$pdsi <- paste0(
    round(summary(pdsi_lm)$coefficients[2, 1], digits = 2),
    if (summary(pdsi_lm)$coefficients[2, 4] <= 0.05) {
      "*"
    }
  )

  bassB <- bass_bio[bass_bio$Year %in% year_id, ]
  bassB_lm <- lm(menhaden_b[biomass_lag_id] ~ bassB$bass_bio[index_lag_id])
  bassB_fit <- fitted(bassB_lm)
  lm_slope$bassB <- paste0(
    round(summary(bassB_lm)$coefficients[2, 1], digits = 2),
    if (summary(bassB_lm)$coefficients[2, 4] <= 0.05) {
      "*"
    }
  )

  effort <- apply(ewe_faa[ewe_faa$X %in% ewe_faa$X[1:length(year_id)], grep("menhaden", colnames(ewe_faa))] / ewe_catchability[year_id, grep("menhaden", colnames(ewe_catchability))], 1, sum)
  effort_lm <- lm(menhaden_b[biomass_lag_id] ~ effort[index_lag_id])
  effort_fit <- fitted(effort_lm)
  lm_slope$effort <- paste0(
    round(summary(effort_lm)$coefficients[2, 1], digits = 2),
    if (summary(effort_lm)$coefficients[2, 4] <= 0.05) {
      "*"
    }
  )

  if (projection_year_id == length(projection_year)) {
    par(mfrow = c(2, 2))

    plot(amo$scaled_value[index_lag_id], menhaden_b[biomass_lag_id],
      xlab = "AMO values",
      ylab = "Biomass of menhaden-like species"
    )
    abline(amo_lm)

    plot(pdsi$scaled_value[index_lag_id], menhaden_b[biomass_lag_id],
      xlab = "PDSI values",
      ylab = "Biomass of menhaden-like species"
    )
    abline(pdsi_lm)

    plot(bassB$bass_bio[index_lag_id], menhaden_b[biomass_lag_id],
      xlab = "Biomass of Striped bass",
      ylab = "Biomass of menhaden-like species"
    )
    abline(bassB_lm)

    plot(effort[index_lag_id], menhaden_b[biomass_lag_id],
      xlab = "Menhaden fishing effort",
      ylab = "Biomass of menhaden-like species"
    )
    abline(effort_lm)
  }


  # status of indicators --------------------------------------------

  amo_soi <- calc_soi(
    indicator_data = amo$scaled_value,
    slope = coef(amo_lm)[2]
  )

  pdsi_soi <- calc_soi(
    indicator_data = pdsi$scaled_value,
    slope = coef(pdsi_lm)[2]
  )

  bassB_soi <- calc_soi(
    indicator_data = bassB$bass_bio,
    slope = coef(bassB_lm)[2]
  )

  effort_soi <- calc_soi(
    indicator_data = effort,
    slope = coef(effort_lm)[2]
  )

  if (projection_year_id == 1) {
    scaled_data <- data.frame(
      year = model_year,
      projection_year_id = projection_year_id,
      amo = scale(amo$scaled_value)[, 1],
      pdsi = scale(pdsi$scaled_value)[, 1],
      bassB = scale(bassB$bass_bio)[, 1],
      effort = scale(effort)[, 1],
      menhadenB = scale(menhaden_b)[, 1]
    )

    soi_data <- data.frame(
      year = model_year,
      projection_year_id = projection_year_id,
      amo = amo_soi,
      pdsi = pdsi_soi,
      bass_b = bassB_soi,
      effort = effort_soi
    )
  } else {
    scaled_data <- rbind(
      scaled_data,
      data.frame(
        year = index_year,
        projection_year_id = projection_year_id,
        amo = scale(amo$scaled_value)[, 1],
        pdsi = scale(pdsi$scaled_value)[, 1],
        bassB = scale(bassB$bass_bio)[, 1],
        effort = scale(effort)[, 1],
        menhadenB = scale(menhaden_b)[, 1]
      )
    )

    soi_data <- rbind(
      soi_data,
      data.frame(
        year = index_year,
        projection_year_id = projection_year_id,
        amo = amo_soi,
        pdsi = pdsi_soi,
        bass_b = bassB_soi,
        effort = effort_soi
      )
    )
  }


  # Adjusted FMSY ----------------------------------------------------
  # if (projection_year_id == 1) {
  #   Bt_BMSY <- ss3list$Kobe$B.Bmsy[length(model_year)]
  #   Bt_BMSY_sd <- ss3list$derived_quants$StdDev[ss3list$derived_quants$Label == paste0("Bratio_", tail(model_year, n = 1))]
  # } else {
  #   Bt_BMSY <- ss3list$Kobe$B.Bmsy[length(model_year) + projection_year_id - 1]
  #   Bt_BMSY_sd <- ss3list$derived_quants$StdDev[ss3list$derived_quants$Label == paste0("Bratio_", projection_year[projection_year_id] - 1)]
  # }
  
  if (projection_year_id == 1) {
    Bt_BMSY <- ss3list$Kobe$B.Bmsy[length(model_year)]

  } else {
    Bt_BMSY <- ss3list$Kobe$B.Bmsy[length(model_year)+projection_year_id-1]
  }

  # randomly draw 1000 values
  # ss3_fmsy <- rnorm(1000, ss3list$derived_quants$Value[ss3list$derived_quants$Label == "annF_MSY"], 0.5)
  # ss3_Bt_BMSY <- rep(Bt_BMSY, 1000)

  ss3_fmsy_mean <- ss3list$derived_quants$Value[ss3list$derived_quants$Label == "annF_MSY"]
  ss3_fmsy_sd <- ss3list$derived_quants$StdDev[ss3list$derived_quants$Label == "annF_MSY"]
  
  ss3_fmsy <- c(ss3_fmsy_mean - 1.96 * ss3_fmsy_sd, ss3_fmsy_mean, ss3_fmsy_mean + 1.96 * ss3_fmsy_sd)
  ss3_Bt_BMSY <- rep(Bt_BMSY, length(ss3_fmsy))



  ss3_fmsy[ss3_fmsy < 0] <- 0.1

  amo_fmsy <- adjust_projection_jabba(
    FMSY = ss3_fmsy,
    soi = tail(amo_soi, n = 1),
    Bt_BMSY = ss3_Bt_BMSY
  )
  pdsi_fmsy <- adjust_projection_jabba(
    FMSY = ss3_fmsy,
    soi = tail(pdsi_soi, n = 1),
    Bt_BMSY = ss3_Bt_BMSY
  )
  bassB_fmsy <- adjust_projection_jabba(
    FMSY = ss3_fmsy,
    soi = tail(bassB_soi, n = 1),
    Bt_BMSY = ss3_Bt_BMSY
  )
  effort_fmsy <- adjust_projection_jabba(
    FMSY = ss3_fmsy,
    soi = tail(effort_soi, n = 1),
    Bt_BMSY = ss3_Bt_BMSY
  )

  if (projection_year_id == 1) {
    fmsy_data <- data.frame(
      iter = 1:length(amo_fmsy),
      projection_year_id = projection_year[projection_year_id],
      SS3 = ss3_fmsy,
      amo = amo_fmsy,
      pdsi = pdsi_fmsy,
      bassB = bassB_fmsy,
      effort = effort_fmsy
    )
  } else {
    fmsy_data <- rbind(
      fmsy_data,
      data.frame(
        iter = 1:length(amo_fmsy),
        projection_year_id = projection_year[projection_year_id],
        SS3 = ss3_fmsy,
        amo = amo_fmsy,
        pdsi = pdsi_fmsy,
        bassB = bassB_fmsy,
        effort = effort_fmsy
      )
    )
  }
}

soi_data_melt <- reshape2::melt(
  soi_data,
  id = c("year", "projection_year_id")
)
soi_data_melt$projection_year_id <- as.factor(projection_year)

ggplot(soi_data_melt[soi_data_melt$projection_year_id == projection_year[1], ], aes(x = year, y = value)) +
  geom_line() +
  facet_wrap(~variable, scales = "free_y") +
  labs(
    title = "Status of Indicators",
    x = "Year",
    y = "Status of Indicators"
  ) +
  theme_bw()

fmsy_data_melt <- reshape2::melt(
  fmsy_data,
  id = c("iter", "projection_year_id")
)
fmsy_data_melt$projection_year_id <- as.factor(fmsy_data_melt$projection_year_id)

# ggplot(fmsy_data_melt, aes(x = iter, y = value, color = projection_year_id)) +
#   geom_line() +
#   facet_wrap(~variable) +
#   labs(
#     title = "FMSY",
#     x = "Iteration",
#     y = "FMSY"
#   ) +
#   theme_bw()

ggplot(fmsy_data_melt, aes(x = variable, y = value, color = projection_year_id)) +
  geom_boxplot() +
  labs(
    title = "FMSY",
    x = "",
    y = "FMSY"
  ) +
  theme_bw()

fmsy_data_melt_median <- aggregate(value ~ projection_year_id + variable, data = fmsy_data_melt, median)
fmsy_data_melt_median$projection_year_id <- as.numeric(as.character(fmsy_data_melt_median$projection_year_id))
ggplot(fmsy_data_melt_median, aes(x = projection_year_id, y = value, color = variable)) +
  geom_line() +
  labs(
    title = "Median FMSY from SS3 and adjusted FMSY",
    x = "",
    y = "FMSY"
  ) +
  theme_bw()
```

- Slope values from linear regression models

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
knitr::kable(lm_slope)
```

- Project biomass based on adjusted $FMSY$
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
# Re-run SS3 with adjusted FMSY

projection_file_path <- here::here("data", "data_rich", "OM2_projections")
originalwd <- getwd()
setwd(projection_file_path)
ss3_projection <- list()
fmsy_vec <- aggregate(value ~ variable, fmsy_data_melt_median, median)
for (i in 1:nrow(fmsy_vec)) {
  generate_ss3(
    file_path = projection_file_path,
    r0 = 12, steepness = 0.55, sigmar = 0.5,
    projection_f = fmsy_vec$value[i], projection_catch = NULL,
    sa_data = sa_data, model_year = model_year,
    projection_year = projection_year,
    use_depletion = FALSE, depletion_ratio = NULL,
    initial_equilibrium_catch = TRUE
  )
  system(paste(file.path(projection_file_path, "ss_win.exe"), file.path(projection_file_path, "data.ss"), sep = " "), show.output.on.console = TRUE)

  ss3_output <- SS_output(
    dir = projection_file_path,
    verbose = TRUE,
    printstats = TRUE
  )
  
  ss_std <- PBSadmb::readRep("ss", suffix = ".std")
  msy_std <- ss_std[ss_std$name=="Mgmt_quant",]
  
  ss3_output$msy <- msy_std
  
  ss3_projection[[i]] <- ss3_output
}

on.exit(setwd(originalwd), add = TRUE)
save(ss3_projection, file = file.path(projection_file_path, "ss3_projections.RData"))



ssb_label <- paste0("SSB_", projection_year)
recruit_label <- paste0("Recr_", projection_year)
catch_label <- paste0("ForeCatch_", projection_year)


for (i in 1:nrow(fmsy_vec)){
  fmsy_data_melt_median$ssb[fmsy_data_melt_median$variable==fmsy_vec$variable[i]] <- ss3_projection[[i]]$derived_quants$Value[ss3_projection[[i]]$derived_quants$Label %in% ssb_label]
  
  fmsy_data_melt_median$recruit[fmsy_data_melt_median$variable==fmsy_vec$variable[i]] <- ss3_projection[[i]]$derived_quants$Value[ss3_projection[[i]]$derived_quants$Label %in% recruit_label]
  
  fmsy_data_melt_median$catch[fmsy_data_melt_median$variable==fmsy_vec$variable[i]] <- ss3_projection[[i]]$derived_quants$Value[ss3_projection[[i]]$derived_quants$Label %in% catch_label]
  
  fmsy_data_melt_median$F2017_FMSY[fmsy_data_melt_median$variable==fmsy_vec$variable[i]] <- tail(ss3_projection[[i]]$Kobe$F.Fmsy, n=1)/fmsy_data_melt_median$value[fmsy_data_melt_median$variable==fmsy_vec$variable[i]]
  fmsy_data_melt_median$B2017_K[fmsy_data_melt_median$variable==fmsy_vec$variable[i]] <- tail(ss3_projection[[i]]$timeseries$Bio_all, n=1)/ss3_projection[[i]]$timeseries$Bio_all[1]
  fmsy_data_melt_median$B2017_BMSY[fmsy_data_melt_median$variable==fmsy_vec$variable[i]] <- tail(ss3_projection[[i]]$Kobe$B.Bmsy, n=1)
  fmsy_data_melt_median$Average_Biomass[fmsy_data_melt_median$variable==fmsy_vec$variable[i]] <- mean(ss3_projection[[i]]$timeseries$Bio_all[ss3_projection[[i]]$timeseries$Era == "FORE"])
  fmsy_data_melt_median$Bonanza_Period[fmsy_data_melt_median$variable==fmsy_vec$variable[i]] <- sum((ss3_projection[[i]]$timeseries$Bio_all[ss3_projection[[i]]$timeseries$Era == "FORE"]/ss3_projection[[i]]$timeseries$Bio_all[1])>0.8)
  fmsy_data_melt_median$Collapse_Period[fmsy_data_melt_median$variable==fmsy_vec$variable[i]] <- sum((ss3_projection[[i]]$timeseries$Bio_all[ss3_projection[[i]]$timeseries$Era == "FORE"]/ss3_projection[[i]]$timeseries$Bio_all[1])<0.2)
  
}

ggplot(fmsy_data_melt_median, aes(x = projection_year_id, y = ssb, color = variable))+
  geom_line() +
  geom_point()+
  #facet_wrap(~variable) +
  labs(
    title = "",
    x = "",
    y = "SSB"
  ) +
  theme_bw()

ggplot(fmsy_data_melt_median, aes(x = projection_year_id, y = recruit, color = variable))+
  geom_line() +
  geom_point()+
  #facet_wrap(~variable) +
  labs(
    title = "",
    x = "",
    y = "Recruit"
  ) +
  theme_bw()

```
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}

om_K <- 5.12023947*1000000 # max b
om_bmsy <- c(
  4.553527815, 4.228060737, 2.657752888, 3.039367286, 1.700737553, 2.625573544, 1.885360091
)*1000000
om_fmsy <- c(
  0.092402786, 0.344614655, 1.101458788, 0.722086847,
  1.569404483, 0.988227546, 0.72328496
)

evaluation_table <- data.frame(
  Average_Catch = mean(sa_data$fishery$obs_total_catch_biomass$fleet1[as.numeric(names(sa_data$fishery$obs_total_catch_biomass$fleet1)) %in% projection_year]),
  F2017_FMSY = mean(tail(mortality_ewe, n=1)/om_fmsy),
  B2017_K = tail(biomass_ewe[time_id], n=1)/om_K, 
  B2017_BMSY = mean(tail(biomass_ewe[time_id], n=1)/om_bmsy),
  Average_Biomass = mean(tail(biomass_ewe[time_id], n=length(projection_year))),
  Bonanza_Period = sum((tail(biomass_ewe[time_id], n=length(projection_year))/om_K)>0.8),
  Collapse_Period = sum((tail(biomass_ewe[time_id], n=length(projection_year))/om_K)<0.2)
)

case_names = unique(fmsy_data_melt_median$variable)
for (i in 1:length(case_names)) {
  # projected_biomass <- aggregate(biomass ~ year + tac, data = biomass_projection, median)
  # bk <- aggregate(bk ~ year + tac + variable, data = biomass_projection, median)
  
  evaluation_table <- rbind(
    evaluation_table,
    c(
      mean(fmsy_data_melt_median$catch[fmsy_data_melt_median$variable == case_names[i]]),
      tail(fmsy_data_melt_median$F2017_FMSY[fmsy_data_melt_median$variable == case_names[i]], n=1),
      tail(fmsy_data_melt_median$B2017_K[fmsy_data_melt_median$variable == case_names[i]], n=1),
      tail(fmsy_data_melt_median$B2017_BMSY[fmsy_data_melt_median$variable == case_names[i]], n=1),
      mean(fmsy_data_melt_median$Average_Biomass[fmsy_data_melt_median$variable == case_names[i]]),
      tail(fmsy_data_melt_median$Bonanza_Period, n=1), 
      tail(fmsy_data_melt_median$Collapse_Period, n=1)
    )
  )
}

evaluation_table <- rbind(
  apply(evaluation_table, 2, max),
  rep(0, ncol(evaluation_table)),
  evaluation_table
)

row.names(evaluation_table) <- c("Max", "Min",
                                 "OM", "SS3 Default",
                                 "SS3+AMO",
                                 "SS3+PDSI",
                                 "SS3+Bass Biomass",
                                 "SS3+Effort")

evaluation_table["Max", c("Bonanza_Period", "Collapse_Period", "F2017_FMSY")] <- c(length(projection_year), length(projection_year), max(c(evaluation_table$F2017_FMSY, 4)))
evaluation_table[c("Max", "Min"), c("F2017_FMSY", "Collapse_Period")] <- apply(evaluation_table[c("Max", "Min"), c("F2017_FMSY", "Collapse_Period")], 2, rev)

colors_border <- RColorBrewer::brewer.pal(nrow(evaluation_table)-2, "Dark2")
colors_in <- alpha(colors_border,0.3)

radarchart(evaluation_table,
           pcol=colors_border, pfcol=colors_in, plwd=4 , plty=1,
           axistype = 5, axislabcol="blue", 
           paxislabels = round(evaluation_table["Max",],2), palcex = 2)
legend(x=0.9, y=0.7, legend = rownames(evaluation_table[-c(1,2),]), bty = "n", pch=20 , col=colors_border, text.col = "black", cex=1.2, pt.cex=3)

```

