---
title: 'OM3 data-poor stock assessment'
date: "`r Sys.Date()`"
output:
  html_document: 
    code_folding: hide
  word_document: default
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Depletion-Based Stock Reduction Analysis(DB-SRA) from DLMtool

- Website: [https://github.com/Blue-Matter/DLMtool](https://github.com/Blue-Matter/DLMtool)

```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
devtools::load_all()

required_pkg <- c("DLMtool", "here", "ggplot2", "reshape2",
                  "RColorBrewer", "scales", "fmsb") ## DLMtool: version 6.0.3

pkg_to_install <- required_pkg[!(required_pkg %in%
                                   installed.packages()[, "Package"])]
if (length(pkg_to_install)) install.packages(pkg_to_install)

lapply(required_pkg, library, character.only = TRUE)
```

## Case 0: stock assessment base run (terminal year = 2009)
- B0
```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
# Load simulated input data
source(here::here("Rscript", "simulationOM3.R"))# OM reference points

# Reference points scenarios
# Maximum relative F = 7
# No. of steps = 700
# No. of trial years = 100
# Option 1: Search by fleets or groups
# Option 2: Full compensation or stationary system

functional_groups <- c(
  "StripedBass0",
  "StripedBass2_5",
  "StripedBass6",
  "AtlanticMenhaden0",
  "AtlanticMenhaden1",
  "AtlanticMenhaden2",
  "AtlanticMenhaden3",
  "AtlanticMenhaden4",
  "AtlanticMenhaden5",
  "AtlanticMenhaden6",
  "SpinyDogfish",
  "BluefishJuvenile",
  "BluefishAdult",
  "WeakfishJuvenile",
  "WeakfishAdult",
  "AtlanticHerring0_1",
  "AtlanticHerring2",
  "Anchovies",
  "Benthos",
  "Zooplankton",
  "Phytoplankton",
  "Detritus"
)
ages <- 0:6
start_year <- 1985
terminal_year <- 2009
projection_nyear <- 5
model_year <- start_year:terminal_year
projection_year <- (terminal_year+1):(terminal_year+projection_nyear)

file_path <- here::here("data", "ewe", "7ages_newsim_om3", "ewe7ages_ecosim_om3", "msy_forcing_pdsi_egg_amo1", "fleet")

compensation_msy <- read_ewe_reference_points(
  file_path = file_path,
  file_names = c(
    "F.menhaden_Catch_FullCompensation.csv",
    "F.menhaden_B_FullCompensation.csv"
  ),
  reference_points_scenario = "compensation",
  functional_groups = functional_groups,
  key_functional_group = "AtlanticMenhaden",
  ages = ages,
  plot = TRUE
) # MSY, FMSY, BMSY: 0.5913518, 2.939998, 1.619142

stationary_msy <- read_ewe_reference_points(
  file_path = file_path,
  file_names = c(
    "F.menhaden_Catch_StationarySystem.csv",
    "F.menhaden_B_StationarySystem.csv"
  ),
  reference_points_scenario = "stationary",
  functional_groups = functional_groups,
  key_functional_group = "AtlanticMenhaden",
  ages = ages,
  plot = TRUE
) # MSY, FMSY, BMSY: 0.5784879, 2.899998, 1.604036

msy_mean <- sapply(1:length(compensation_msy), function(x) {mean(c(compensation_msy[[x]], stationary_msy[[x]]))})
names(msy_mean) <- names(compensation_msy)

temp <- scan(file.path(file_path, "FMSY_FullCompensation.csv"), what = "", sep = "\n")
fmsy_data <- temp[-c(1:9)]
fmsy_data <- read.table(
    text = as.character(fmsy_data),
    sep = ",", 
    col.names = c(
      "Group", "TL", "Fbase", "Cbase", "Vbase", 
      "FmsyFound", "Fmsy", "Cmsy", "Vmsy", "CmsyAll", "VmsyAll"
    )
  )
row_names <- paste("menhaden", ages)
row_names[length(row_names)] <- "menhaden 6+"
om_fmsy_group <- fmsy_data$Fmsy[fmsy_data$Group %in% row_names]

# OM unfished biomass --------------------------------------------
age_name <- paste0("AtlanticMenhaden", ages)

# Only menhaden F = 0, other functional groups: F = stock assessment F from 1987 - 2017, then F = 0 for the rest of the years
biomass <- read_ewe_output(
  file_path = here::here("data", "ewe", "7ages_newsim_om3", "ewe7ages_ecosim_om3_F0_menhaden", "ecosim_forcing_pdsi_egg_amo1"),
  file_names = "biomass_monthly.csv",
  skip_nrows = 8,
  plot = FALSE,
  figure_titles = NULL,
  functional_groups = functional_groups,
  figure_colors = NULL
)
time_id <- seq(1, nrow(biomass[[1]]), by = 12)
biomass_f0_menhaden <- apply(biomass[[1]][, age_name], 1, sum)[time_id] * 1000000

# All functional groups F = 0
biomass <- read_ewe_output(
  file_path = here::here("data", "ewe", "7ages_newsim_om3", "ewe7ages_ecosim_om3_F0_all_functional_groups", "ecosim_forcing_pdsi_egg_amo1"),
  file_names = "biomass_monthly.csv",
  skip_nrows = 8,
  plot = FALSE,
  figure_titles = NULL,
  functional_groups = functional_groups,
  figure_colors = NULL
)
time_id <- seq(1, nrow(biomass[[1]]), by = 12)
biomass_f0_all <- apply(biomass[[1]][, age_name], 1, sum)[time_id] * 1000000

x <- start_year:(start_year + length(time_id) - 1)
yrange <- range(biomass_f0_menhaden, biomass_f0_all)
plot(x, biomass_f0_menhaden,
     xlab = "Year", ylab = "Biomass",
     lty = 1, type = "l"
)
lines(x, biomass_f0_all,
      pch = 1, lty = 2
)
legend("topright",
       c("Menhaden F = 0", "All functional groups F = 0"),
       lty = c(1, 2),
       bty = "n"
)

B0_F0_menhaden <- mean(tail(biomass_f0_menhaden, n = length(ages) * 2))
B0_F0_all <- mean(tail(biomass_f0_all, n = length(ages) * 2))
B0_F0_mean <- mean(c(B0_F0_menhaden, B0_F0_all))

file_path <- here::here("data", "ewe", "7ages_newsim_om3", "ewe7ages_ecosim_om3", "ecosim_forcing_pdsi_egg_amo1")
source(here::here("Rscript", "load_indices.R"))

set.seed(999)
# Load EwE biomass data

age_name <- paste0("AtlanticMenhaden", ages)

biomass <- read_ewe_output(
  file_path = file_path,
  file_names = "biomass_monthly.csv",
  skip_nrows = 8,
  plot = FALSE,
  figure_titles = NULL,
  functional_groups = functional_groups,
  figure_colors = NULL
)

time_id <- seq(1, nrow(biomass[[1]]), by = 12)[1:(length(model_year)+length(projection_year))]
biomass_ewe <- apply(biomass[[1]][, age_name], 1, sum) * 1000000
# Set up JABBA base case assessment

output_dir <- here::here("data", "data_poor", "om3")
if (!dir.exists(output_dir)) dir.create(output_dir)
```

- Case 0: scenario A
```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
# Scenario A: default stock assessment run ----------------------------
## DB-SRA is a method designed for determining a catch limit
## and management reference points for data-limited fisheries
## where catches are known from the beginning of exploitation.
## However, the catch data from the menhaden-like species case is not
## from the beginning of the exploitation.

# Populate the input data object

# Create a blank DLM object
ss_case0 <- new("Data")
# Change default area from 2 to 1
ss_case0@nareas <- 1
# Name of the case
ss_case0@Name <- "case0"
# Catch data
data_id <- as.numeric(names(sa_data$fishery$obs_total_catch_biomass$fleet1)) %in% model_year
ss_case0@Cat <- matrix(sa_data$fishery$obs_total_catch_biomass$fleet1[data_id],
                       nrow = 1
)
# State units of catch
ss_case0@Units <- sa_data$fishery$units_info$units_biomass
# Years
ss_case0@Year <- model_year
# Depletion relative to unfished
ss_case0@Dep <-  tail(ss_case0@Cat[1, ], n = 1) / max(ss_case0@Cat[1, ])

# VB maximum growth rate
ss_case0@vbK <- sa_data$biodata$k
# VB theoretical age at zero length
# default from EwE: -0.1
# https://www.researchgate.net/publication/267193103_Ecopath_with_Ecosim_A_User's_Guide#pf66
ss_case0@vbt0 <- sa_data$biodata$t0
# VB maximum length
# ss_case0@vbLinf <- (sa_data$biodata$winf * 1000 / sa_data$biodata$lw_a)^(1 / sa_data$biodata$lw_b)
ss_case0@vbLinf <- 500 # mm from FishBase
# Ratio of FMSY/M
# Q: Is it possible to find the ratio of FMSY to M
# for pelagic species in the Northwestern Atlantic Ocean?
# EwE FMSY values
### fmsy <- c(
###  0.092402786, 0.344614655, 1.101458788, 0.722086847,
###  1.569404483, 0.988227546, 0.72328496
###)

# Use compensation Fmsy (one value)
#fmsy_m <- mean(compensation_msy$FMSY / sa_data$biodata$natural_mortality_matrix[1, ])

# Use Fmsy at age
fmsy_m <- mean(om_fmsy_group / sa_data$biodata$natural_mortality_matrix[1, ])

ss_case0@FMSY_M <- fmsy_m

#ss_case0@Mort <- 0.67 #sa_data$biodata$natural_mortality_matrix[1, ]/(1-exp(-ss_case0@vbK*(1:7-ss_case0@vbt0)))^(-3*0.305)

# BMSY relative to unfished
# Dick and MacCall (2011): use 0.4 if target biomass is 40% of unfished biomass
### ss_case0@BMSY_B0 <- 0.3 # BAM FEC30% target

ss_case0@BMSY_B0 <- compensation_msy$BMSY / B0_F0_menhaden
# Length at 50% maturity
age_maturity50 <- 2
ss_case0@L50 <- ss_case0@vbLinf *
  (1 - exp(-ss_case0@vbK *
             (age_maturity50 - ss_case0@vbt0)))

# Run DBSRA, DBSRA_40 and DBSRA4010
## DBSRA: Base Version. TAC is calculated assumed MSY harvest rate
## multiplied by the estimated current abundance (estimated B0 x Depletion)

## DBSRA_40: Same as the Base Version but assumes 40 percent current
## depletion (Bcurrent/B0 = 0.4), which is more or less the most
## optimistic state for a stock (i.e. very close to BMSY/B0 for many stocks).

## DBSRA4010: Base version paired with the 40-10 rule that linearly
## throttles back the TAC when depletion is below 0.4 down to zero at
## 10 percent of unfished biomass.

ss_case01 <- ss_case0
dbsra <- DLMtool::DBSRA(1, ss_case01, plot = FALSE)
# dbsra40 <- DLMtool::DBSRA_40(1, ss_case0, plot = TRUE)
# dbsra4010 <- DLMtool::DBSRA4010(1, ss_case0, plot = TRUE)

# Projection: Scenario A --------------------------------------------------
projection_output1 <- list()
for (i in 1:length(projection_year)) {
  ss_case <- ss_case01
  year <- model_year[1]:(projection_year[i] - 1)
  data_id <- as.numeric(names(sa_data$fishery$obs_total_catch_biomass$fleet1)) %in% year
  ss_case@Cat <- matrix(sa_data$fishery$obs_total_catch_biomass$fleet1[data_id],
                        nrow = 1
  )
  ss_case@Year <- year
  #ss_case@Dep <- tail(ss_case@Cat[1, ], n = 1) / ss_case@Cat[1, 1]
  ss_case@Dep <- ss_case01@Dep
  projection_output1[[i]] <- DLMtool::DBSRA_(
    x = 1,
    Data = ss_case,
    depo = NULL, # Optional fixed depletion (single value)
    hcr = NULL # Optional harvest control rule for throttling catch as a function of B/B0.
  )
}

# plot figures
par(mfrow=c(1,2))
ylim <- range(projection_output1[[1]]$C_hist, unlist(sapply(projection_output1, "[", "TAC")))
plot(c(model_year, projection_year),
     c(projection_output1[[1]]$C_hist, rep(NA, length(projection_year))),
     type = "l",
     ylim = ylim,
     xlab = "Year", ylab = "Catch (mt)"
)

for (i in 1:length(projection_year)) {
  boxplot(projection_output1[[i]]$TAC,
          add = TRUE,
          at = projection_year[i],
          col = "grey",
          width = 1,
          outline = TRUE,
          axes = FALSE
  )
}

catch_year <- projection_year[1:length(projection_year) - 1]
points(catch_year, sa_data$fishery$obs_total_catch_biomass$fleet1[names(sa_data$fishery$obs_total_catch_biomass$fleet1) %in% catch_year],
       pch = 16, col = "blue"
)

legend("top",
       c("Observed Catch (model year)", "Observed Catch (projection year)", "TAC"),
       lty = c(1, NA, NA),
       pch = c(NA, 16, NA),
       col = c("black", "blue", NA),
       fill = c(NA, NA, "gray"),
       border = c(NA, NA, "black"),
       bty = "n",
       title = "Case 0: Scenario A"
)
legend("left",
       c(
         paste0("DBSRA@Dep = ", round(ss_case01@Dep, digits = 2)),
         paste0("DBSRA@BMSY_B0 = ", round(ss_case01@BMSY_B0, digits = 2)),
         paste0("DBSRA@FMSY_M = ", round(ss_case01@FMSY_M, digits = 2))
       ),
       bty="n")

# plot biomass
dbsraB_projection <- list()
for (i in 1:length(projection_year)){
  dbsraB_projection[[i]] <- apply(projection_output1[[i]]$Btrend, 2, median)
}

# ylim <- range(biomass_ewe[time_id], unlist(dbsraB_projection))
# for (i in 1:length(projection_year)){
#   lines(model_year[1]:(projection_year[i]-1), dbsraB_projection[[i]],
#         lty=i, col=i)
# }
# legend("bottomright",
#        c("EWE", paste0("DBSRA", projection_year)),
#        pch = c(16, rep(NA, length(projection_year))),
#        lty = c(NA, 1:length(projection_year)),
#        col = c(1, 1:length(projection_year)),
#        title = "Case 0: Scenario A", 
#        bty = "n"
# )
ylim <- range(biomass_ewe[time_id], unlist(dbsraB_projection[[1]]))
plot(c(model_year),
     biomass_ewe[time_id][1:length(model_year)],
     xlab = "Year", ylab = "Biomass (mt)",
     ylim = ylim,
     pch = 16
)
lines(model_year[1]:(projection_year[1]-1), dbsraB_projection[[1]],
        lty=1, col=1)
legend("bottomright",
       c("EWE", "DBSRA"),
       pch = c(16, NA),
       lty = c(NA, 1),
       col = c(1, 1),
       title = "Case 0: Scenario A", 
       bty = "n"
)
```

- Case 0: scenario B

```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}

# Scenario B ---------------------------
ss_case02 <- ss_case0
ss_case02@Dep <- biomass_ewe[time_id][terminal_year-start_year+1]/B0_F0_menhaden

dbsra <- DLMtool::DBSRA(1, ss_case02, plot = FALSE)

# Projection: Scenario B --------------------------------------------------
projection_output2 <- list()
for (i in 1:length(projection_year)) {
  ss_case <- ss_case02
  year <- model_year[1]:(projection_year[i] - 1)
  data_id <- as.numeric(names(sa_data$fishery$obs_total_catch_biomass$fleet1)) %in% year
  ss_case@Cat <- matrix(sa_data$fishery$obs_total_catch_biomass$fleet1[data_id],
                        nrow = 1
  )
  ss_case@Year <- year
  #ss_case@Dep <- tail(ss_case@Cat[1, ], n = 1) / ss_case@Cat[1, 1]
  ss_case@Dep <- ss_case02@Dep
  projection_output2[[i]] <- DLMtool::DBSRA_(
    x = 1,
    Data = ss_case,
    depo = NULL, # Optional fixed depletion (single value)
    hcr = NULL # Optional harvest control rule for throttling catch as a function of B/B0.
  )
}


# plot figures
par(mfrow=c(1,2))
ylim <- range(projection_output2[[1]]$C_hist, unlist(sapply(projection_output2, "[", "TAC")))
plot(c(model_year, projection_year),
     c(projection_output2[[1]]$C_hist, rep(NA, length(projection_year))),
     type = "l",
     ylim = ylim,
     xlab = "Year", ylab = "Catch (mt)"
)

for (i in 1:length(projection_year)) {
  boxplot(projection_output2[[i]]$TAC,
          add = TRUE,
          at = projection_year[i],
          col = "grey",
          width = 1,
          outline = TRUE,
          axes = FALSE
  )
}

catch_year <- projection_year[1:length(projection_year) - 1]
points(catch_year, sa_data$fishery$obs_total_catch_biomass$fleet1[names(sa_data$fishery$obs_total_catch_biomass$fleet1) %in% catch_year],
       pch = 16, col = "blue"
)

legend("top",
       c("Observed Catch (model year)", "Observed Catch (projection year)", "TAC"),
       lty = c(1, NA, NA),
       pch = c(NA, 16, NA),
       col = c("black", "blue", NA),
       fill = c(NA, NA, "gray"),
       border = c(NA, NA, "black"),
       bty = "n",
       title = "Case 0: Scenario B"
)

legend("left",
       c(
         paste0("DBSRA@Dep = ", round(ss_case02@Dep, digits = 2)),
         paste0("DBSRA@BMSY_B0 = ", round(ss_case02@BMSY_B0, digits = 2)),
         paste0("DBSRA@FMSY_M = ", round(ss_case02@FMSY_M, digits = 2))
       ),
       bty="n")

# plot biomass
dbsraB_projection <- list()
for (i in 1:length(projection_year)){
  dbsraB_projection[[i]] <- apply(projection_output2[[i]]$Btrend, 2, median)
}

# ylim <- range(biomass_ewe[time_id], unlist(dbsraB_projection))
# plot(c(model_year, projection_year),
#      biomass_ewe[time_id],
#      xlab = "Year", ylab = "Biomass (mt)",
#      ylim = ylim,
#      pch = 16
# )
# for (i in 1:length(projection_year)){
#   lines(model_year[1]:(projection_year[i]-1), dbsraB_projection[[i]],
#         lty=i, col=i)
# }
# legend("bottomright",
#        c("EWE", paste0("DBSRA", projection_year)),
#        bty = "n",
#        pch = c(16, rep(NA, length(projection_year))),
#        lty = c(NA, 1:length(projection_year)),
#        col = c(1, 1:length(projection_year)),
#        title = "Case 0: Scenario B"
# )
ylim <- range(biomass_ewe[time_id], unlist(dbsraB_projection[[1]]))
plot(c(model_year),
     biomass_ewe[time_id][1:length(model_year)],
     xlab = "Year", ylab = "Biomass (mt)",
     ylim = ylim,
     pch = 16
)
lines(model_year[1]:(projection_year[1]-1), dbsraB_projection[[1]],
      lty=1, col=1)
legend("bottomright",
       c("EWE", "DBSRA"),
       pch = c(16, NA),
       lty = c(NA, 1),
       col = c(1, 1),
       title = "Case 0: Scenario B", 
       bty = "n"
)

```

- Case 0: scenario C
  - Add 11 years of equilibrium catches (max catch) to the start of the catch
  - Try a sequence of Dep (0.1 - 0.9 with interval of 0.05), BMSY_B0 (0.1 - 0.9 with interval of 0.05), and FMSY_M (0.1 - 2.0 with an interval of 0.05) and find the scenario that has the lowest sum of squared differences

```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
# time_id_model_year <- seq(1, nrow(biomass[[1]]), by = 12)[1:length(model_year)]
# biomass_ewe_model_year <- apply(biomass[[1]][, age_name], 1, sum)[time_id_model_year] * 1000000
# 
# ss_case03 <- ss_case0
# 
# equi_year <- start_year:(start_year+10)
# catch_multiplier <- 1
# equi_catch <- rep(sa_data$fishery$obs_total_catch_biomass$fleet1[1], length = length(equi_year)) * catch_multiplier
# # equi_catch <- rep(max(sa_data$fishery$obs_total_catch_biomass$fleet), length = length(equi_year)) * catch_multiplier
# 
# data_id <- as.numeric(names(sa_data$fishery$obs_total_catch_biomass$fleet1)) %in% model_year
# ss_case03@Cat <- matrix(c(equi_catch, sa_data$fishery$obs_total_catch_biomass$fleet1[data_id]),
#                         nrow = 1
# )
# 
# ss_case03@Year <- (model_year[1] - length(equi_year)):tail(model_year, n=1)
# 
# dep = seq(0.1, 0.9, by = 0.05)
# # sum of squared differences
# ssd_dep <- data.frame(
#   dep = dep,
#   ssd = NA
# )
# for (i in 1:length(dep)){
#   ss_case <- ss_case03
#   ss_case@Dep <- dep[i]
#   dbsra <- DLMtool::DBSRA_(
#     x = 1,
#     Data = ss_case,
#     depo = NULL,
#     hcr = NULL
#   )
#   dbsraB <- apply(dbsra$Btrend, 2, median)
#   ssd_dep$ssd[i] <- sum((dbsraB[(length(equi_year)+1):length(dbsraB)] - biomass_ewe_model_year)^2)
# }
# 
# ss_case <- ss_case03
# ss_case@Dep <- ssd_dep$dep[which.min(ssd_dep$ssd)] # dep = 0.5 has the smallest sum of squared differences
# dbsra <- DLMtool::DBSRA_(
#   x = 1,
#   Data = ss_case,
#   depo = NULL,
#   hcr = NULL
# )
# dbsra_dep <- apply(dbsra$Btrend, 2, median)
# 
# bmsy_b0 <- seq(0.1, 0.9, by = 0.05)
# # sum of squared differences
# ssd_bmsy_b0 <- data.frame(
#   bmsy_b0 = bmsy_b0,
#   ssd = NA
# )
# for (i in 1:length(bmsy_b0)){
#   ss_case <- ss_case03
#   ss_case@Dep <- ssd_dep$dep[which.min(ssd_dep$ssd)]
#   ss_case@BMSY_B0 <- bmsy_b0[i]
#   dbsra <- DLMtool::DBSRA_(
#     x = 1,
#     Data = ss_case,
#     depo = NULL,
#     hcr = NULL
#   )
#   dbsraB <- apply(dbsra$Btrend, 2, median)
#   ssd_bmsy_b0$ssd[i] <- sum((dbsraB[(length(equi_year)+1):length(dbsraB)] - biomass_ewe_model_year)^2)
# }
# 
# 
# ss_case <- ss_case03
# ss_case@Dep <- ssd_dep$dep[which.min(ssd_dep$ssd)]
# ss_case@BMSY_B0 <- ssd_bmsy_b0$bmsy_b0[which.min(ssd_bmsy_b0$ssd)] # bmsy_b0 = 0.55 has the smallest sum of squared differences: 6.6e+12
# dbsra <- DLMtool::DBSRA_(
#   x = 1,
#   Data = ss_case,
#   depo = NULL,
#   hcr = NULL
# )
# dbsra_bmsyb0 <- apply(dbsra$Btrend, 2, median)
# 
# fmsy_m <- seq(0.1, 2, by = 0.05)
# # sum of squared differences
# ssd_fmsy_m <- data.frame(
#   fmsy_m = fmsy_m,
#   ssd = NA
# )
# for (i in 1:length(fmsy_m)){
#   ss_case <- ss_case03
#   ss_case@Dep <- ssd_dep$dep[which.min(ssd_dep$ssd)]
#   ss_case@BMSY_B0 <- ssd_bmsy_b0$bmsy_b0[which.min(ssd_bmsy_b0$ssd)]
#   ss_case@FMSY_M <- fmsy_m[i]
#   dbsra <- DLMtool::DBSRA_(
#     x = 1,
#     Data = ss_case,
#     depo = NULL,
#     hcr = NULL
#   )
#   dbsraB <- apply(dbsra$Btrend, 2, median)
#   ssd_fmsy_m$ssd[i] <- sum((dbsraB[(length(equi_year)+1):length(dbsraB)] - biomass_ewe_model_year)^2)
# }
# 
# 
# ss_case <- ss_case03
# ss_case@Dep <- ssd_dep$dep[which.min(ssd_dep$ssd)]
# ss_case@BMSY_B0 <- ssd_bmsy_b0$bmsy_b0[which.min(ssd_bmsy_b0$ssd)]
# ss_case@FMSY_M <- ssd_fmsy_m$fmsy_m[which.min(ssd_fmsy_m$ssd)] # fmsy_m = 1.2 has the smallest sum of squared differences
# dbsra <- DLMtool::DBSRA_(
#   x = 1,
#   Data = ss_case,
#   depo = NULL,
#   hcr = NULL
# )
# dbsra_fmsym <- apply(dbsra$Btrend, 2, median)
# 
# ss_case_final <- ss_case
# dbsra <- DLMtool::DBSRA(1, ss_case_final, plot = FALSE)
# 
# # Projection: scenario C --------------------------------------------------
# projection_output3 <- list()
# equi_year_temp <- list()
# for (i in 1:length(projection_year)) {
#   ss_case_temp <- ss_case_final
#   
#   equi_year_temp[[i]] <- equi_year
#   # equi_year_temp[[i]] <- 2000:(2012+i-1)
#   equi_catch_temp <- rep(sa_data$fishery$obs_total_catch_biomass$fleet1[1], length = length(equi_year_temp[[i]])) * catch_multiplier
#   # equi_catch_temp <- rep(max(sa_data$fishery$obs_total_catch_biomass$fleet1), length = length(equi_year_temp[[i]])) * catch_multiplier
#   
#   # equi_id_temp <- as.numeric(names(sa_data$fishery$obs_total_catch_biomass$fleet1)) %in% equi_year_temp[[i]]
#   # equi_catch_temp <- sa_data$fishery$obs_total_catch_biomass$fleet1[equi_id_temp]
#   
#   data_id <- as.numeric(names(sa_data$fishery$obs_total_catch_biomass$fleet1)) %in% c(model_year[1]:(projection_year[i] - 1))
#   
#   ss_case_temp@Cat <- matrix(c(equi_catch_temp, sa_data$fishery$obs_total_catch_biomass$fleet1[data_id]),
#                              nrow = 1
#   )
#   ss_case_temp@Year <- ss_case_temp@Year[1]:(projection_year[i]-1)
#   
#   
#   projection_output3[[i]] <- DLMtool::DBSRA_(
#     x = 1,
#     Data = ss_case_temp,
#     depo = NULL, # Optional fixed depletion (single value)
#     hcr = NULL # Optional harvest control rule for throttling catch as a function of B/B0.
#   )
# }
# 
# # plot figures
# par(mfrow=c(1,2))
# c_hist <- projection_output3[[1]]$C_hist
# ylim <- range(c_hist[(length(equi_year_temp[[1]])+1):length(c_hist)], unlist(sapply(projection_output3, "[", "TAC")))
# plot(c(ss_case_temp@Year[(length(equi_year_temp[[1]])+1):length(c_hist)], projection_year),
#      c(c_hist[(length(equi_year_temp[[1]])+1):length(c_hist)], rep(NA, length(projection_year))),
#      type = "l",
#      ylim = ylim,
#      xlab = "Year", ylab = "Catch (mt)"
# )
# 
# for (i in 1:length(projection_year)) {
#   boxplot(projection_output3[[i]]$TAC,
#           add = TRUE,
#           at = projection_year[i],
#           col = "grey",
#           width = 1,
#           outline = TRUE,
#           axes = FALSE
#   )
# }
# 
# catch_year <- projection_year[1:length(projection_year) - 1]
# points(catch_year, sa_data$fishery$obs_total_catch_biomass$fleet1[names(sa_data$fishery$obs_total_catch_biomass$fleet1) %in% catch_year],
#        pch = 16, col = "blue"
# )
# 
# legend("top",
#        c("Observed Catch", "Observed Catch for TAC estimates", "TAC"),
#        lty = c(1, NA, NA),
#        pch = c(NA, 16, NA),
#        col = c("black", "blue", NA),
#        fill = c(NA, NA, "gray"),
#        border = c(NA, NA, "black"),
#        bty = "n",
#        title = "Case 0: scenario C"
# )
# 
# legend("left",
#        c(
#          paste0("DBSRA@Dep = ", round(ssd_dep$dep[which.min(ssd_dep$ssd)], digits = 2)),
#          paste0("DBSRA@BMSY_B0 = ", round(ssd_bmsy_b0$bmsy_b0[which.min(ssd_bmsy_b0$ssd)], digits = 2)),
#          paste0("DBSRA@FMSY_M = ", round(ssd_fmsy_m$fmsy_m[which.min(ssd_fmsy_m$ssd)], digits = 2))),
#        bty="n")
# 
# # plot biomass
# dbsraB_projection <- list()
# for (i in 1:length(projection_year)){
#   full_dbsraB <- projection_output3[[i]]$Btrend
#   year_id <- projection_output3[[i]]
#   dbsraB_projection[[i]] <- apply(full_dbsraB[, (length(equi_year_temp[[i]])+1):ncol(full_dbsraB)], 2, median)
# }
# 
# ylim = range(biomass_ewe[time_id], unlist(dbsraB_projection))
# plot(c(model_year, projection_year),
#      biomass_ewe[time_id],
#      xlab = "Year", ylab = "Biomass (mt)",
#      ylim = ylim,
#      pch = 16
# )
# for (i in 1:length(projection_year)){
#   lines(model_year[1]:(projection_year[i]-1), dbsraB_projection[[i]],
#         lty=i, col=i)
# }
# legend("bottomright",
#        c("EWE", paste0("DBSRA", projection_year)),
#        bty = "n",
#        pch = c(16, rep(NA, length(projection_year))),
#        lty = c(NA, 1:length(projection_year)),
#        col = c(1, 1:length(projection_year)),
#        title = "Case 0: scenario C"
# )


```
```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
time_id_model_year <- seq(1, nrow(biomass[[1]]), by = 12)[1:length(model_year)]
biomass_ewe_model_year <- apply(biomass[[1]][, age_name], 1, sum)[time_id_model_year] * 1000000

ss_case03 <- ss_case0

equi_year <- start_year:(start_year+10)
catch_multiplier <- 1
equi_catch <- rep(sa_data$fishery$obs_total_catch_biomass$fleet1[1], length = length(equi_year)) * catch_multiplier
# equi_catch <- rep(max(sa_data$fishery$obs_total_catch_biomass$fleet), length = length(equi_year)) * catch_multiplier

data_id <- as.numeric(names(sa_data$fishery$obs_total_catch_biomass$fleet1)) %in% model_year
ss_case03@Cat <- matrix(c(equi_catch, sa_data$fishery$obs_total_catch_biomass$fleet1[data_id]),
                        nrow = 1
)

ss_case03@Year <- (model_year[1] - length(equi_year)):tail(model_year, n=1)

dep = seq(0.1, 0.9, by = 0.05)
bmsy_b0 <- seq(0.1, 0.9, by = 0.05)
fmsy_m <- seq(0.1, 2, by = 0.05)

param_matrix <- expand.grid(dep, bmsy_b0, fmsy_m)
colnames(param_matrix) <- c("dep", "bmsy_b0", "fmsy_m")
param_matrix$ssd <- NA

find_min_ssd = FALSE
if (find_min_ssd == TRUE){
  for (i in 1:nrow(param_matrix)){
  ss_case <- ss_case03
  ss_case@Dep <- param_matrix$dep[i]
  ss_case@BMSY_B0 <- param_matrix$bmsy_b0[i]
  ss_case@FMSY_M <- param_matrix$fmsy_m[i]
  dbsra <- DLMtool::DBSRA_(
    x = 1,
    Data = ss_case,
    depo = NULL,
    hcr = NULL
  )
  dbsraB <- apply(dbsra$Btrend, 2, median)
  param_matrix$ssd[i] <- sum((dbsraB[(length(equi_year)+1):length(dbsraB)] - biomass_ewe_model_year)^2)
}

write.csv(param_matrix, here::here("data", "data_poor", paste0("dbsra_ssd", terminal_year, ".csv")))
}


param_matrix <- read.csv(here::here("data", "data_poor", paste0("dbsra_ssd", terminal_year, ".csv")))

ss_case <- ss_case03
ss_case@Dep <- param_matrix$dep[which.min(param_matrix$ssd)]
ss_case@BMSY_B0 <- param_matrix$bmsy_b0[which.min(param_matrix$ssd)]
ss_case@FMSY_M <- param_matrix$fmsy_m[which.min(param_matrix$ssd)] 

dbsra <- DLMtool::DBSRA_(
  x = 1,
  Data = ss_case,
  depo = NULL,
  hcr = NULL
)
dbsra_fmsym <- apply(dbsra$Btrend, 2, median)

ss_case_final <- ss_case
dbsra <- DLMtool::DBSRA(1, ss_case_final, plot = FALSE)

# Projection: scenario C --------------------------------------------------
projection_output3 <- list()
equi_year_temp <- list()
for (i in 1:length(projection_year)) {
  ss_case_temp <- ss_case_final
  
  equi_year_temp[[i]] <- equi_year
  # equi_year_temp[[i]] <- 2000:(2012+i-1)
  equi_catch_temp <- rep(sa_data$fishery$obs_total_catch_biomass$fleet1[1], length = length(equi_year_temp[[i]])) * catch_multiplier
  # equi_catch_temp <- rep(max(sa_data$fishery$obs_total_catch_biomass$fleet1), length = length(equi_year_temp[[i]])) * catch_multiplier
  
  # equi_id_temp <- as.numeric(names(sa_data$fishery$obs_total_catch_biomass$fleet1)) %in% equi_year_temp[[i]]
  # equi_catch_temp <- sa_data$fishery$obs_total_catch_biomass$fleet1[equi_id_temp]
  
  data_id <- as.numeric(names(sa_data$fishery$obs_total_catch_biomass$fleet1)) %in% c(model_year[1]:(projection_year[i] - 1))
  
  ss_case_temp@Cat <- matrix(c(equi_catch_temp, sa_data$fishery$obs_total_catch_biomass$fleet1[data_id]),
                             nrow = 1
  )
  ss_case_temp@Year <- ss_case_temp@Year[1]:(projection_year[i]-1)
  
  
  projection_output3[[i]] <- DLMtool::DBSRA_(
    x = 1,
    Data = ss_case_temp,
    depo = NULL, # Optional fixed depletion (single value)
    hcr = NULL # Optional harvest control rule for throttling catch as a function of B/B0.
  )
}

# plot figures
par(mfrow=c(1,2))
c_hist <- projection_output3[[1]]$C_hist
ylim <- range(c_hist[(length(equi_year_temp[[1]])+1):length(c_hist)], unlist(sapply(projection_output3, "[", "TAC")))
plot(c(ss_case_temp@Year[(length(equi_year_temp[[1]])+1):length(c_hist)], projection_year),
     c(c_hist[(length(equi_year_temp[[1]])+1):length(c_hist)], rep(NA, length(projection_year))),
     type = "l",
     ylim = ylim,
     xlab = "Year", ylab = "Catch (mt)"
)

for (i in 1:length(projection_year)) {
  boxplot(projection_output3[[i]]$TAC,
          add = TRUE,
          at = projection_year[i],
          col = "grey",
          width = 1,
          outline = TRUE,
          axes = FALSE
  )
}

catch_year <- projection_year[1:length(projection_year) - 1]
points(catch_year, sa_data$fishery$obs_total_catch_biomass$fleet1[names(sa_data$fishery$obs_total_catch_biomass$fleet1) %in% catch_year],
       pch = 16, col = "blue"
)

legend("top",
       c("Observed Catch", "Observed Catch for TAC estimates", "TAC"),
       lty = c(1, NA, NA),
       pch = c(NA, 16, NA),
       col = c("black", "blue", NA),
       fill = c(NA, NA, "gray"),
       border = c(NA, NA, "black"),
       bty = "n",
       title = "Case 0: scenario C"
)

legend("left",
       c(
         paste0("DBSRA@Dep = ", round(param_matrix$dep[which.min(param_matrix$ssd)], digits = 2)),
         paste0("DBSRA@BMSY_B0 = ", round(param_matrix$bmsy_b0[which.min(param_matrix$ssd)], digits = 2)),
         paste0("DBSRA@FMSY_M = ", round(param_matrix$fmsy_m[which.min(param_matrix$ssd)], digits = 2))),
       bty="n")

# plot biomass
dbsraB_projection <- list()
for (i in 1:length(projection_year)){
  full_dbsraB <- projection_output3[[i]]$Btrend
  year_id <- projection_output3[[i]]
  dbsraB_projection[[i]] <- apply(full_dbsraB[, (length(equi_year_temp[[i]])+1):ncol(full_dbsraB)], 2, median)
}

# ylim = range(biomass_ewe[time_id], unlist(dbsraB_projection))
# plot(c(model_year, projection_year),
#      biomass_ewe[time_id],
#      xlab = "Year", ylab = "Biomass (mt)",
#      ylim = ylim,
#      pch = 16
# )
# for (i in 1:length(projection_year)){
#   lines(model_year[1]:(projection_year[i]-1), dbsraB_projection[[i]],
#         lty=i, col=i)
# }
# legend("bottomright",
#        c("EWE", paste0("DBSRA", projection_year)),
#        bty = "n",
#        pch = c(16, rep(NA, length(projection_year))),
#        lty = c(NA, 1:length(projection_year)),
#        col = c(1, 1:length(projection_year)),
#        title = "Case 0: scenario C"
# )
ylim <- range(biomass_ewe[time_id], unlist(dbsraB_projection[[1]]))
plot(c(model_year),
     biomass_ewe[time_id][1:length(model_year)],
     xlab = "Year", ylab = "Biomass (mt)",
     ylim = ylim,
     pch = 16
)
lines(model_year[1]:(projection_year[1]-1), dbsraB_projection[[1]],
      lty=1, col=1)
legend("bottomright",
       c("EWE", "DBSRA"),
       bty = "n",
       pch = c(16, NA),
       lty = c(NA, 1),
       col = c(1, 1),
       title = "Case 0: scenario C"
)

```

## Linear regression models from cases 1 - 5 using "true" values from EwE
- Case 1: Link Atlantic Multidecadal Oscillation Index with menhaden biomass estimates and adjust projections: AMO is an indicator of climate conditions and would affect recruitment variability of menhaden-like species
- Case 2: Link Palmer drought severity index with menhaden biomass estimates and adjust projections: PSDI is a long-term indicator of drought conditions and it reflects river discharge and precipitation
- Case 3: Link biomass of Striped bass from the EwE with menhaden biomass estimates and adjust projections because bass is a major predator
- Case 4: Link fishing effort of menhaden with menhaden biomass estimates and adjust projections 
- Case 5: Link catch per unit effort of menhaden with menhaden biomass estimates and adjust projections

- Linear regression models from case 1 - 5 (Lag = 1)
  - True biomass of menhaden-like species as functions of AMO, PDSI, biomass of striped bass, fishing effort of menhaden, and menhaden CPUE

### Status of indicators (SOI)

- If stock-indicator relationship is positive, $SOI_{y} = \frac{I_{y}-I_{y}^{min}}{I_{y}^{max}-I_{y}^{min}}$
  
- If stock-indicator relationship is negative, $SOI_{y} = 1-\frac{I_{y}-I_{y}^{min}}{I_{y}^{max}-I_{y}^{min}}$
  
  where $I_{y}$ represents indicator value in year y. $I_{y}^{min}$ and $I_{y}^{max}$ represent the minimum and maximum values of $I$ from the time series.
  
### Adjust projections

- If $\frac{B2009_{i}}{BMSY} > 1$, $F^{'}_{i} = FMSY^{min} + SOI2009 \times (FMSY^{max}-FMSY^{min})$

- If $\frac{B2009_{i}}{BMSY} \le 1$ and $\frac{B2009_{i}}{BMSY} > 0.5$, $F^{'}_{i} = SOI2009 \times \frac{B2009_{i}}{BMSY} \times FMSY_{i}$
  
- If $\frac{B2009_{i}}{BMSY} \le 0.5$, $F^{'}_{i} = 0$

where $i$ represents individual iterations

```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
lm_slope <- data.frame(
  case = "True indices",
  amo = NA,
  #pcp = NA,
  bassB = NA,
  #price = NA,
  pdsi = NA,
  effort = NA,
  cpue = NA
)

year_id <- seq(1, nrow(amo_unsmooth_lag1), by = 12)
index_year <- c(model_year)
lag = 1
biomass_lag_id <- (1+lag):length(index_year)
index_lag_id <- 1:(length(index_year)-lag)

amo <- amo_unsmooth_lag1[year_id, ]
amo_lm <- lm(biomass_ewe[time_id][biomass_lag_id] ~ amo$scaled_value[index_lag_id])
amo_fit <- fitted(amo_lm)
lm_slope$amo <- paste0(
  round(summary(amo_lm)$coefficients[2, 1], digits = 2),
  if (summary(amo_lm)$coefficients[2, 4] <= 0.05) {
    "*"
  }
)

# pcp <- precipitation[year_id, ]
# pcp_lm <- lm(biomass_ewe[time_id][biomass_lag_id] ~ pcp$scaled_value[index_lag_id])
# pcp_fit <- fitted(pcp_lm)
# lm_slope$pcp <- paste0(
#   round(summary(pcp_lm)$coefficients[2, 1], digits = 2),
#   if(summary(pcp_lm)$coefficients[2, 4] <= 0.05) {"*"})

pdsi <- palmer_drought_severity_index[year_id, ]
pdsi_lm <- lm(biomass_ewe[time_id][biomass_lag_id] ~ pdsi$scaled_value[index_lag_id])
pdsi_fit <- fitted(pdsi_lm)
lm_slope$pdsi <- paste0(
  round(summary(pdsi_lm)$coefficients[2, 1], digits = 2),
  if(summary(pdsi_lm)$coefficients[2, 4] <= 0.05) {"*"})

bassB <- bass_bio[bass_bio$Year %in% year_id, ]
bassB_lm <- lm(biomass_ewe[time_id][biomass_lag_id] ~ bassB$bass_bio[index_lag_id])
bassB_fit <- fitted(bassB_lm)
lm_slope$bassB <- paste0(
  round(summary(bassB_lm)$coefficients[2, 1], digits = 2),
  if(summary(bassB_lm)$coefficients[2, 4] <= 0.05) {"*"})

# sub_menhadenP <- menhaden_price$Inflation.Adjust.Price.Per.MT[menhaden_price$Year %in% index_year]
# price_lm <- lm(biomass_ewe[time_id][biomass_lag_id] ~ sub_menhadenP[index_lag_id])
# price_fit <- fitted(price_lm)
# lm_slope$price <- paste0(
#   round(summary(price_lm)$coefficients[2, 1], digits = 2),
#   if(summary(price_lm)$coefficients[2, 4] <= 0.05) {"*"})

effort <- apply(ewe_faa[, grep("menhaden", colnames(ewe_faa))] / ewe_catchability[year_id, grep("menhaden", colnames(ewe_catchability))], 1, sum)
effort_lm <- lm(biomass_ewe[time_id][biomass_lag_id] ~ effort[index_lag_id])
effort_fit <- fitted(effort_lm)
lm_slope$effort <- paste0(
  round(summary(effort_lm)$coefficients[2, 1], digits = 2),
  if(summary(effort_lm)$coefficients[2, 4] <= 0.05) {"*"})

cpue <- sa_data$fishery$obs_total_catch_biomass$fleet1/effort
cpue_lm <- lm(biomass_ewe[time_id][biomass_lag_id] ~ cpue[index_lag_id])
cpue_fit <- fitted(cpue_lm)
lm_slope$cpue <- paste0(
  round(summary(cpue_lm)$coefficients[2, 1], digits = 2),
  if(summary(cpue_lm)$coefficients[2, 4] <= 0.05) {"*"})

# linear regression analysis summary table
lm_data_om <- rbind(
  data.frame(
    Menhaden_Biomass = biomass_ewe[time_id][biomass_lag_id],
    Variable = "AMO",
    Index_Value = amo$scaled_value[index_lag_id]
  ),
  data.frame(
    Menhaden_Biomass = biomass_ewe[time_id][biomass_lag_id],
    Variable = "PDSI",
    Index_Value = pdsi$scaled_value[index_lag_id]
  ),
  data.frame(
    Menhaden_Biomass = biomass_ewe[time_id][biomass_lag_id],
    Variable = "Biomass of Striped bass",
    Index_Value = bassB$bass_bio[index_lag_id]
  ),
  data.frame(
    Menhaden_Biomass = biomass_ewe[time_id][biomass_lag_id],
    Variable = "Menhaden fishing effort",
    Index_Value = effort[index_lag_id]
  ),
  data.frame(
    Menhaden_Biomass = biomass_ewe[time_id][biomass_lag_id],
    Variable = "Menhaden CPUE",
    Index_Value = cpue[index_lag_id]
  )
)

lm_data_om$model <- "OM"

# jpeg(filename = file.path(figure_path, paste0("lm_slope_om_", terminal_year, ".jpeg")), width = 200, height = 100, units = "mm", res = 1800)
p <- gridExtra::tableGrob(lm_slope)
gridExtra::grid.arrange(p)
# dev.off()
```

## Cases 1-5 are based on the settings from Scenario A
```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
# Projection based on Scenario A ------------------------------------

output <- compare_projections_dbsra(
  case_name = "scenario A",
  projection_output_data = projection_output1,
  projection_year = projection_year,
  model_year = model_year,
  lag = 1,
  amo = amo_unsmooth_lag1,
  pcp = precipitation,
  pdsi = palmer_drought_severity_index,
  bassB = bass_bio,
  price = menhaden_price,
  effort = apply(ewe_faa[, grep("menhaden", colnames(ewe_faa))] / ewe_catchability[year_id, grep("menhaden", colnames(ewe_catchability))], 1, sum),
  cpue = sa_data$fishery$obs_total_catch_biomass$fleet1 / (apply(ewe_faa[, grep("menhaden", colnames(ewe_faa))] / ewe_catchability[year_id, grep("menhaden", colnames(ewe_catchability))], 1, sum)),
  indices = c("amo", "pdsi", "bassB", "effort", "cpue")
)

# Linear regression figure
lm_data <- rbind(lm_data_om, output$lm_data_em)
# jpeg(filename = file.path(figure_path, paste0("linear_regression", terminal_year, ".jpeg")), width = 200, height = 100, units = "mm", res = 1800)
ggplot(lm_data, aes(x = Index_Value, y = Menhaden_Biomass, color = model)) +
  geom_point() +
  geom_smooth(method = lm) +
  facet_wrap(~Variable, scales = "free_x") +
  labs(
    title = "Linear regression analysis",
    x = "Indicator Value",
    y = "Menhaden spawning biomass (mt)"
  ) +
  theme_bw()
# dev.off()

soi_data_melt <- output$soi_data_melt
ggplot(soi_data_melt[soi_data_melt$projection_year_id==projection_year[1], ], aes(x = year, y = value)) +
  geom_line() +
  facet_wrap(~variable, scales = "free_y") +
  labs(
    title = "Scenario A: Status of Indicators",
    x = "Year",
    y = "Status of Indicators"
  ) +
  theme_bw()

tac_data_melt <- output$tac_data_melt
ggplot(tac_data_melt, aes(x=variable, y = value, color = projection_year_id)) +
  geom_boxplot() +
  labs(
    title = "Scenario A: TAC",
    x = "",
    y = "TAC"
  ) +
  theme_bw()
# ggplot(tac_data_melt, aes(x=variable, y = value, color = projection_year_id)) +
#   geom_violin()+
#   geom_boxplot(width=0.1) +
#   # facet_wrap(~variable)+
#   labs(
#     title = "Scenario A: TAC",
#     x = "",
#     y = "TAC"
#   ) +
#   theme_bw()
# 
# tac_data_melt_median <- output$tac_data_melt_median
# ggplot(tac_data_melt_median, aes(x = projection_year_id, y = value, color = variable)) +
#   geom_line() +
#   labs(
#     title = "Scenario A: Median TAC from DBSRA and adjusted TAC",
#     x = "",
#     y = "TAC"
#   ) +
#   theme_bw()

```

- Slope values from linear regression models

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
knitr::kable(output$lm_slope)
```

## Cases 1-5 are based on the settings from Scenario B
```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
# Projection based on Scenario B ------------------------------------

output <- compare_projections_dbsra(
  case_name = "scenario B",
  projection_output_data = projection_output2,
  projection_year = projection_year,
  model_year = model_year,
  lag = 1,
  amo = amo_unsmooth_lag1,
  pcp = precipitation,
  pdsi = palmer_drought_severity_index,
  bassB = bass_bio,
  price = menhaden_price,
  effort = apply(ewe_faa[, grep("menhaden", colnames(ewe_faa))] / ewe_catchability[year_id, grep("menhaden", colnames(ewe_catchability))], 1, sum),
  cpue = sa_data$fishery$obs_total_catch_biomass$fleet1 / (apply(ewe_faa[, grep("menhaden", colnames(ewe_faa))] / ewe_catchability[year_id, grep("menhaden", colnames(ewe_catchability))], 1, sum)),
  indices = c("amo", "pdsi", "bassB", "effort", "cpue")
)

# Linear regression figure
lm_data <- rbind(lm_data_om, output$lm_data_em)
# jpeg(filename = file.path(figure_path, paste0("linear_regression", terminal_year, ".jpeg")), width = 200, height = 100, units = "mm", res = 1800)
ggplot(lm_data, aes(x = Index_Value, y = Menhaden_Biomass, color = model)) +
  geom_point() +
  geom_smooth(method = lm) +
  facet_wrap(~Variable, scales = "free_x") +
  labs(
    title = "Linear regression analysis",
    x = "Indicator Value",
    y = "Menhaden spawning biomass (mt)"
  ) +
  theme_bw()
# dev.off()

soi_data_melt <- output$soi_data_melt
ggplot(soi_data_melt[soi_data_melt$projection_year_id==projection_year[1], ], aes(x = year, y = value)) +
  geom_line() +
  facet_wrap(~variable, scales = "free_y") +
  labs(
    title = "Scenario B: Status of Indicators",
    x = "Year",
    y = "Status of Indicators"
  ) +
  theme_bw()

tac_data_melt <- output$tac_data_melt
ggplot(tac_data_melt, aes(x=variable, y = value, color = projection_year_id)) +
  geom_boxplot() +
  labs(
    title = "Scenario B: TAC",
    x = "",
    y = "TAC"
  ) +
  theme_bw()
# ggplot(tac_data_melt, aes(x=variable, y = value, color = projection_year_id)) +
#   geom_violin()+
#   geom_boxplot(width=0.1) +
#   # facet_wrap(~variable)+
#   labs(
#     title = "Scenario B: TAC",
#     x = "",
#     y = "TAC"
#   ) +
#   theme_bw()
# 
# tac_data_melt_median <- output$tac_data_melt_median
# ggplot(tac_data_melt_median, aes(x = projection_year_id, y = value, color = variable)) +
#   geom_line() +
#   labs(
#     title = "Scenario B: Median TAC from DBSRA and adjusted TAC",
#     x = "",
#     y = "TAC"
#   ) +
#   theme_bw()
```

- Slope values from linear regression models

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
knitr::kable(output$lm_slope)
```

## Cases 1-5 are based on the settings from Scenario C
```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
# Projection based on Scenario C ------------------------------------
projection_output3_clean <- list()

for (i in 1:length(projection_year)){
  temp <- projection_output3[[i]]
  temp$Btrend <- temp$Btrend[, (length(equi_year_temp[[i]])+1): ncol(temp$Btrend)]
  projection_output3_clean[[i]] <- temp
}
output <- compare_projections_dbsra(
  case_name = "Scenario C",
  projection_output_data = projection_output3_clean,
  projection_year = projection_year,
  model_year = model_year,
  lag = 1,
  amo = amo_unsmooth_lag1,
  pcp = precipitation,
  pdsi = palmer_drought_severity_index,
  bassB = bass_bio,
  price = menhaden_price,
  effort = apply(ewe_faa[, grep("menhaden", colnames(ewe_faa))] / ewe_catchability[year_id, grep("menhaden", colnames(ewe_catchability))], 1, sum),
  cpue = sa_data$fishery$obs_total_catch_biomass$fleet1 / (apply(ewe_faa[, grep("menhaden", colnames(ewe_faa))] / ewe_catchability[year_id, grep("menhaden", colnames(ewe_catchability))], 1, sum)),
  indices = c("amo", "pdsi", "bassB", "effort", "cpue")
)

# Linear regression figure
lm_data <- rbind(lm_data_om, output$lm_data_em)
# jpeg(filename = file.path(figure_path, paste0("linear_regression", terminal_year, ".jpeg")), width = 200, height = 100, units = "mm", res = 1800)
ggplot(lm_data, aes(x = Index_Value, y = Menhaden_Biomass, color = model)) +
  geom_point() +
  geom_smooth(method = lm) +
  facet_wrap(~Variable, scales = "free_x") +
  labs(
    title = "Linear regression analysis",
    x = "Indicator Value",
    y = "Menhaden spawning biomass (mt)"
  ) +
  theme_bw()
# dev.off()

soi_data_melt <- output$soi_data_melt
ggplot(soi_data_melt[soi_data_melt$projection_year_id==projection_year[1], ], aes(x = year, y = value)) +
  geom_line() +
  facet_wrap(~variable, scales = "free_y") +
  labs(
    title = "Scenario C: Status of Indicators",
    x = "Year",
    y = "Status of Indicators"
  ) +
  theme_bw()

tac_data_melt <- output$tac_data_melt
ggplot(tac_data_melt, aes(x=variable, y = value, color = projection_year_id)) +
  geom_boxplot() +
  labs(
    title = "Scenario C: TAC",
    x = "",
    y = "TAC"
  ) +
  theme_bw()
# ggplot(tac_data_melt, aes(x=variable, y = value, color = projection_year_id)) +
#   geom_violin()+
#   geom_boxplot(width=0.1) +
#   # facet_wrap(~variable)+
#   labs(
#     title = "Scenario C: TAC",
#     x = "",
#     y = "TAC"
#   ) +
#   theme_bw()
# 
# tac_data_melt_median <- output$tac_data_melt_median
# ggplot(tac_data_melt_median, aes(x = projection_year_id, y = value, color = variable)) +
#   geom_line() +
#   labs(
#     title = "Scenario C: Median TAC from DBSRA and adjusted TAC",
#     x = "",
#     y = "TAC"
#   ) +
#   theme_bw()


for (i in 1:nrow(tac_data_melt)){
  temp <- projection_output3[[which(projection_year == tac_data_melt$projection_year_id[i])]]
  temp_B <- (temp$Btrend[, 1] * temp$Bt_Kstore)[tac_data_melt$iter[i]]
  tac_data_melt$fmort[i] <- tac_data_melt$value[i]/temp_B
}

fmort_data_melt_median <- aggregate(fmort ~ projection_year_id+variable, data = tac_data_melt, median)
projection_f <- fmort_data_melt_median
fishery_sel <- IFA4EBFM::logistic(
    pattern = "double_logistic",
    x = sa_data$biodata$ages,
    slope_asc = 3.1,
    location_asc = 1.8,
    slope_desc = 0.88,
    location_desc = 0.01
) 

for (i in 1:nrow(projection_f)) {
    projection_f[i, paste0("fmsy_", sa_data$biodata$ages)] <- projection_f$fmort[i] * fishery_sel
}

write.csv(projection_f, here::here("data", "data_poor", paste0("fmsy_median_data", terminal_year, ".csv")))

Bt_BMSY_data <- matrix(NA, ncol=length(projection_year), nrow=length(projection_output3_clean[[1]]$Bt_Kstore))
for (projection_year_id in 1:length(projection_year)){
    projection_output <- projection_output3_clean
    Bt_BMSY_data[, projection_year_id] <- projection_output[[projection_year_id]]$Bt_Kstore / projection_output[[projection_year_id]]$BMSY_K_Mstore
}

write.csv(Bt_BMSY_data, here::here("data", "data_poor", paste0("Bt_BMSY_data", terminal_year, ".csv")))

```

- Slope values from linear regression models

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
knitr::kable(output$lm_slope)
```

- Projections
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
# tac_data_melt$biomass <- tac_data_melt$catch <- tac_data_melt$B2017_K <-
  # tac_data_melt$B2017_BMSY <- tac_data_melt$Bonanza_percentage <- tac_data_melt$Collapse_percentage <- NA

cases <- unique(tac_data_melt$variable)
iters <- unique(tac_data_melt$iter)

for (case_id in 1:length(cases)){
  temp <- tac_data_melt[tac_data_melt$variable==cases[case_id], ]
  
  for (iter in 1:length(iters)){
    tac_temp <- temp[temp$iter==iters[iter], ]
    
    ss_temp <- ss_case_final
    ss_temp@Cat <- matrix(c(ss_case_final@Cat, tac_temp$value), nrow = 1)
    ss_temp@Year <- c(ss_case_final@Year, as.numeric(as.character(tac_temp$projection_year_id)))
    model <- DLMtool::DBSRA_(
      x = 1,
      Data = ss_temp,
      depo = NULL, # Optional fixed depletion (single value)
      hcr = NULL # Optional harvest control rule for throttling catch as a function of B/B0.
    )
    
    tac_data_melt$biomass[(tac_data_melt$variable==cases[case_id]) & (tac_data_melt$iter == iters[iter])] <- 
      apply(model$Btrend[, ss_temp@Year %in% as.numeric(as.character(tac_temp$projection_year_id))], 2, median)
    
    tac_data_melt$catch[(tac_data_melt$variable==cases[case_id]) & (tac_data_melt$iter == iters[iter])] <- 
      tac_temp$value
    
    tac_data_melt$B2017_K[(tac_data_melt$variable==cases[case_id]) & (tac_data_melt$iter == iters[iter])] <- 
      median(model$Bt_Kstore)
    
    tac_data_melt$B2017_BMSY[(tac_data_melt$variable==cases[case_id]) & (tac_data_melt$iter == iters[iter])] <-
      median(model$Bt_Kstore/model$BMSY_K_Mstore)
    
    tac_data_melt$K[(tac_data_melt$variable==cases[case_id]) & (tac_data_melt$iter == iters[iter])] <- 
      median(model$Btrend[, ncol(model$Btrend)] / model$Bt_Kstore)
    
    tac_data_melt$Bt_K[(tac_data_melt$variable==cases[case_id]) & (tac_data_melt$iter == iters[iter])] <- 
      tac_data_melt$biomass[(tac_data_melt$variable==cases[case_id]) & (tac_data_melt$iter == iters[iter])] / 
      tac_data_melt$K[(tac_data_melt$variable==cases[case_id]) & (tac_data_melt$iter == iters[iter])]
    
    
    # tac_data_melt$Bonanza_Percentage[(tac_data_melt$variable==cases[case_id]) & (tac_data_melt$iter == iters[iter])] <-
    #   length(model$Bt_Kstore[model$Bt_Kstore>0.8])/length(model$Bt_Kstore)*100
    # 
    # tac_data_melt$Collapse_Percentage[(tac_data_melt$variable==cases[case_id]) & (tac_data_melt$iter == iters[iter])] <-
    #   length(model$Bt_Kstore[model$Bt_Kstore<0.2])/length(model$Bt_Kstore)*100
    
  
  }
  
  
  
}

ggplot(tac_data_melt, aes(x=projection_year_id, y = biomass, color = projection_year_id)) +
  geom_violin()+
  geom_boxplot(width=0.1) +
  facet_wrap(~variable)+
  labs(
    title = " Estimated biomass based on TAC",
    x = "",
    y = "Biomass"
  ) +
  theme_bw()

ggplot(tac_data_melt, aes(x=projection_year_id, y = biomass, color = projection_year_id)) +
  geom_violin()+
  geom_boxplot(width=0.1) +
  facet_wrap(~variable, scales="free_y")+
  labs(
    title = " Estimated biomass based on TAC",
    x = "",
    y = "Biomass"
  ) +
  theme_bw()

```

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
om_K <- B0_F0_menhaden
om_bmsy <- compensation_msy$BMSY
om_fmsy <- compensation_msy$FMSY

cases <- c(
  "ecosim_data_moderate_om_mediumF",
  "ecosim_data_poor_dbsra_mediumF",
  "ecosim_data_poor_amo_mediumF",
  "ecosim_data_poor_pdsi_mediumF",
  "ecosim_data_poor_bassB_mediumF",
  "ecosim_data_poor_effort_mediumF",
  "ecosim_data_poor_cpue_mediumF"
)

evaluation_table <- data.frame(
  Average_Catch = NA,
  B_K = NA,
  B_BMSY = NA,
  Average_Biomass = NA,
  Bonanza_Period = NA,
  Collapse_Period = NA
)

for (i in seq_along(cases)) {
  file_path <- here::here("data", "ewe", "7ages_newsim_om3", paste0("ewe7ages_ecosim_om3_projection_", terminal_year), cases[i])
  # Load EwE biomass data
  functional_groups <- c(
    "StripedBass0",
    "StripedBass2_5",
    "StripedBass6",
    "AtlanticMenhaden0",
    "AtlanticMenhaden1",
    "AtlanticMenhaden2",
    "AtlanticMenhaden3",
    "AtlanticMenhaden4",
    "AtlanticMenhaden5",
    "AtlanticMenhaden6",
    "SpinyDogfish",
    "BluefishJuvenile",
    "BluefishAdult",
    "WeakfishJuvenile",
    "WeakfishAdult",
    "AtlanticHerring0_1",
    "AtlanticHerring2",
    "Anchovies",
    "Benthos",
    "Zooplankton",
    "Phytoplankton",
    "Detritus"
  )

  age_name <- paste0("AtlanticMenhaden", 0:6)

  biomass <- read_ewe_output(
    file_path = file_path,
    file_names = "biomass_monthly.csv",
    skip_nrows = 8,
    plot = FALSE,
    figure_titles = NULL,
    functional_groups = functional_groups,
    figure_colors = NULL
  )

  time_id <- seq(1, nrow(biomass[[1]]), by = 12)[1:(length(model_year) + projection_nyear)]
  biomass_ewe <- apply(biomass[[1]][, age_name], 1, sum) * 1000000

  catch <- read_ewe_output(
    file_path = file_path,
    file_names = "catch_monthly.csv",
    skip_nrows = 8,
    plot = FALSE,
    figure_titles = NULL,
    functional_groups = functional_groups,
    figure_colors = NULL
  )
  catch_ewe <- apply(catch[[1]][, age_name], 1, sum) * 1000000

  evaluation_table[i, ] <- c(
    # mean catch
    mean(tail(catch_ewe[time_id], n = length(projection_year))),
    # Bend/K
    tail(biomass_ewe[time_id], n = 1) / om_K,
    # Bend/BMSY
    tail(biomass_ewe[time_id], n = 1) / om_bmsy,
    # mean biomass
    mean(tail(biomass_ewe[time_id], n = length(projection_year))),
    # Bonanza length
    sum((tail(biomass_ewe[time_id], n = length(projection_year)) / om_K) > 0.8),
    # Minmize collapse length
    sum((tail(biomass_ewe[time_id], n = length(projection_year)) / om_K) < 0.2)
  )
}

case_names <- levels(tac_data_melt$variable)
for (i in 1:length(case_names)) {
  temp <- tac_data_melt[tac_data_melt$variable == case_names[i], ]

  evaluation_table <- rbind(
    evaluation_table,
    c(
      mean(aggregate(catch ~ projection_year_id, data = temp, median)$catch),
      aggregate(B2017_K ~ projection_year_id, data = temp[temp$projection_year_id == tail(projection_year, n = 1), ], median)$B2017_K,
      aggregate(B2017_BMSY ~ projection_year_id, data = temp[temp$projection_year_id == tail(projection_year, n = 1), ], median)$B2017_BMSY,
      mean(aggregate(biomass ~ projection_year_id, data = temp, median)$biomass),
      sum(aggregate(Bt_K ~ projection_year_id, data = temp, median)$Bt_K > 0.8),
      sum(aggregate(Bt_K ~ projection_year_id, data = temp, median)$Bt_K < 0.2)
    )
  )
}

evaluation_table <- rbind(
  apply(evaluation_table, 2, max),
  rep(0, ncol(evaluation_table)),
  evaluation_table
)

row.names(evaluation_table) <- c(
  "Max", "Min",
  "OM+OM FMSY",
  "OM+DBSRA FMSY",
  "OM+AMO Fadj",
  "OM+PDSI Fadj",
  "OM+Bass Biomass Fadj",
  "OM+Effot Fadj",
  "OM+CPUE Fadj",
  "DBSRA EM+DBSRA FMSY",
  "DBSRA EM+AMO Fadj",
  "DBSRA EM+PDSI Fadj",
  "DBSRA EM+Bass Biomass Fadj",
  "DBSRA EM+Effort Fadj",
  "DBSRA EM+CPUE Fadj"
)

evaluation_table["Max", c("Bonanza_Period", "Collapse_Period")] <- c(length(projection_year), length(projection_year))
evaluation_table[c("Max", "Min"), c("Collapse_Period")] <- rev(evaluation_table[c("Max", "Min"), c("Collapse_Period")])

case_num <- 5
# jpeg(filename = file.path(figure_path, paste0("radar_mediumF_", terminal_year, ".jpeg")), width = 200, height = 200, units = "mm", res = 1800)
par(mfrow = c(3, 3), mar = c(0, 0, 0, 0))
colors <- c("gray", brewer.pal(12, "Paired"))
# colors <- brewer.pal(12,"Paired")

variable_label <- c("Mean Catch", paste0("B", tail(projection_year, n = 1), "/K"), paste0("B", tail(projection_year, n = 1), "/BMSY"), "Mean Biomass", "Bonanza \n Length", "Minimize \n Collapse \n Length")

for (i in 1:case_num) {
  colors_border <- colors[c(1:2, 2 + i, case_num + 3, case_num + 3 + i)]
  radarchart(evaluation_table[c(1:4, 4 + i, case_num + 5, case_num + 5 + i), ],
    seg = 5,
    pcol = colors_border, plwd = 2, plty = 1,
    axistype = 0, axislabcol = "black",
    paxislabels = round(evaluation_table["Max", ], 2), palcex = 1,
    vlabels = variable_label, vlcex = 0.8
  )
  # colors_border <- colors[c(1, 1+i, case_num+2, case_num+2+i)]
  # radarchart(evaluation_table[c(1:3, 3+i, case_num+4, case_num+4+i), ],
  #            seg=5,
  #            pcol=colors_border, plwd=2, plty=1,
  #            axistype = 0, axislabcol="black",
  #            paxislabels = round(evaluation_table["Max",],2), palcex = 1,
  #            vlabels = variable_label, vlcex = 0.8)
}
colors_border <- colors[c(1:2, (case_num + 3):length(colors))]
radarchart(evaluation_table[c(1:4, (case_num + 5):nrow(evaluation_table)), ],
  seg = 5,
  pcol = colors_border, plwd = 2, plty = 1,
  axistype = 2, axislabcol = "black",
  paxislabels = round(evaluation_table["Max", ], 2), palcex = 1,
  vlabels = variable_label, vlcex = 0.8
)
colors_border <- colors[1:length(colors)]
plot(1, type = "n", axes = FALSE, xlab = "", ylab = "")
legend("center", legend = rownames(evaluation_table[-c(1, 2), ]), bty = "n", pch = 20, col = colors_border, text.col = "black", cex = 0.9, pt.cex = 3)

format(evaluation_table, digits = 3)
```
