---
title: 'OM3 data-rich stock assessment (1995)'
date: "`r Sys.Date()`"
output:
  html_document: 
    code_folding: hide
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Stock Synthesis 3 (SS3)

- Using Stock Synthesis 3 v3.30.19.01
- Website: https://github.com/nmfs-stock-synthesis/stock-synthesis

```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
devtools::load_all()

required_pkg <- c(
  "devtools", "here", "reshape",
  "ggplot2", "reshape2",
  "RColorBrewer", "scales", "fmsb",
  "PBSadmb"
)

pkg_to_install <- required_pkg[!(required_pkg %in%
  installed.packages()[, "Package"])]
if (length(pkg_to_install)) install.packages(pkg_to_install)

invisible(lapply(required_pkg, library, character.only = TRUE))

devtools::install_github("r4ss/r4ss",
  ref = "c53f82fcfb3f54296d79ba3a4163990150981285"
)
library(r4ss)
```

## Unfished biomass of menhaden-like species and unfished age 0 menhaden-like fish from the EwE operating model
- f0_menhaden: menhaden-like species F = 0
- f0_menhaden_bass: menhaden-like species and Striped bass F = 0
- f0_all: all functional groups F = 0
- f0_all_noEnv: all functional groups F = 0 and no AMO and PDSI impacts

```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
# Load simulated input data
fishery_CV_input <- 0.05
survey_CV_input <- 0.1
source(here::here("Rscript", "simulationOM3.R")) # OM reference points

# Reference points scenarios
# Maximum relative F = 7
# No. of steps = 700
# No. of trial years = 100
# Option 1: Search by fleets or groups
# Option 2: Full compensation or stationary system

functional_groups <- c(
  "StripedBass0",
  "StripedBass2_5",
  "StripedBass6",
  "AtlanticMenhaden0",
  "AtlanticMenhaden1",
  "AtlanticMenhaden2",
  "AtlanticMenhaden3",
  "AtlanticMenhaden4",
  "AtlanticMenhaden5",
  "AtlanticMenhaden6",
  "SpinyDogfish",
  "BluefishJuvenile",
  "BluefishAdult",
  "WeakfishJuvenile",
  "WeakfishAdult",
  "AtlanticHerring0_1",
  "AtlanticHerring2",
  "Anchovies",
  "Benthos",
  "Zooplankton",
  "Phytoplankton",
  "Detritus"
)
ages <- 0:6
start_year <- 1985
terminal_year <- 1995
projection_nyear <- 5
model_year <- start_year:terminal_year
projection_year <- (terminal_year + 1):(terminal_year + projection_nyear)

file_path <- here::here("data", "ewe", "7ages_newsim_om3", "ewe7ages_ecosim_om3", "msy_forcing_pdsi_egg_amo1", "fleet")
figure_path <- here::here("figure", "data_rich")
if (!dir.exists(figure_path)) dir.create(figure_path)

compensation_msy <- read_ewe_reference_points(
  file_path = file_path,
  file_names = c(
    "F.menhaden_Catch_FullCompensation.csv",
    "F.menhaden_B_FullCompensation.csv"
  ),
  reference_points_scenario = "compensation",
  functional_groups = functional_groups,
  key_functional_group = "AtlanticMenhaden",
  ages = ages,
  plot = TRUE
) # MSY, FMSY, BMSY: 0.5913518, 2.939998, 1.619142

stationary_msy <- read_ewe_reference_points(
  file_path = file_path,
  file_names = c(
    "F.menhaden_Catch_StationarySystem.csv",
    "F.menhaden_B_StationarySystem.csv"
  ),
  reference_points_scenario = "stationary",
  functional_groups = functional_groups,
  key_functional_group = "AtlanticMenhaden",
  ages = ages,
  plot = TRUE
) # MSY, FMSY, BMSY: 0.5784879, 2.899998, 1.604036

msy_mean <- sapply(1:length(compensation_msy), function(x) {
  mean(c(compensation_msy[[x]], stationary_msy[[x]]))
})
names(msy_mean) <- names(compensation_msy)

temp <- scan(file.path(file_path, "FMSY_FullCompensation.csv"), what = "", sep = "\n")
fmsy_data <- temp[-c(1:9)]
fmsy_data <- read.table(
  text = as.character(fmsy_data),
  sep = ",",
  col.names = c(
    "Group", "TL", "Fbase", "Cbase", "Vbase",
    "FmsyFound", "Fmsy", "Cmsy", "Vmsy", "CmsyAll", "VmsyAll"
  )
)
row_names <- paste("menhaden", ages)
row_names[length(row_names)] <- "menhaden 6+"
om_fmsy_group <- fmsy_data$Fmsy[fmsy_data$Group %in% row_names]

# OM unfished biomass and R0--------------------------------------------
age_name <- paste0("AtlanticMenhaden", ages)

# Only menhaden F = 0, other functional groups: F = stock assessment F from 1987 - 2017, then F = 0 for the rest of the years
biomass <- read_ewe_output(
  file_path = here::here("data", "ewe", "7ages_newsim_om3", "ewe7ages_ecosim_om3_F0_menhaden", "ecosim_forcing_pdsi_egg_amo1"),
  file_names = "biomass_monthly.csv",
  skip_nrows = 8,
  plot = FALSE,
  figure_titles = NULL,
  functional_groups = functional_groups,
  figure_colors = NULL
)
time_id <- seq(1, nrow(biomass[[1]]), by = 12)
biomass_f0_menhaden <- apply(biomass[[1]][, age_name], 1, sum)[time_id] * 1000000

# R0
waa <- read_ewe_output(
  file_path = here::here("data", "ewe", "7ages_newsim_om3", "ewe7ages_ecosim_om3_F0_menhaden", "ecosim_forcing_pdsi_egg_amo1"),
  file_names = "weight_monthly.csv",
  skip_nrows = 8,
  plot = FALSE,
  figure_titles = NULL,
  functional_groups = functional_groups,
  figure_colors = NULL
)

abundance0_f0_menhaden <- (biomass[[1]][, age_name[1]] * 1000000 / waa[[1]][, age_name[1]])[time_id]
# menhaden and bass F = 0
biomass <- read_ewe_output(
  file_path = here::here("data", "ewe", "7ages_newsim_om3", "ewe7ages_ecosim_om3_F0_menhaden_bass", "ecosim_forcing_pdsi_egg_amo1"),
  file_names = "biomass_monthly.csv",
  skip_nrows = 8,
  plot = FALSE,
  figure_titles = NULL,
  functional_groups = functional_groups,
  figure_colors = NULL
)
time_id <- seq(1, nrow(biomass[[1]]), by = 12)
biomass_f0_menhaden_bass <- apply(biomass[[1]][, age_name], 1, sum)[time_id] * 1000000

# R0
waa <- read_ewe_output(
  file_path = here::here("data", "ewe", "7ages_newsim_om3", "ewe7ages_ecosim_om3_F0_menhaden_bass", "ecosim_forcing_pdsi_egg_amo1"),
  file_names = "weight_monthly.csv",
  skip_nrows = 8,
  plot = FALSE,
  figure_titles = NULL,
  functional_groups = functional_groups,
  figure_colors = NULL
)

abundance0_f0_menhaden_bass <- (biomass[[1]][, age_name[1]] * 1000000 / waa[[1]][, age_name[1]])[time_id]

# All functional groups F = 0
biomass <- read_ewe_output(
  file_path = here::here("data", "ewe", "7ages_newsim_om3", "ewe7ages_ecosim_om3_F0_all_functional_groups", "ecosim_forcing_pdsi_egg_amo1"),
  file_names = "biomass_monthly.csv",
  skip_nrows = 8,
  plot = FALSE,
  figure_titles = NULL,
  functional_groups = functional_groups,
  figure_colors = NULL
)
time_id <- seq(1, nrow(biomass[[1]]), by = 12)
biomass_f0_all <- apply(biomass[[1]][, age_name], 1, sum)[time_id] * 1000000

# R0
waa <- read_ewe_output(
  file_path = here::here("data", "ewe", "7ages_newsim_om3", "ewe7ages_ecosim_om3_F0_all_functional_groups", "ecosim_forcing_pdsi_egg_amo1"),
  file_names = "weight_monthly.csv",
  skip_nrows = 8,
  plot = FALSE,
  figure_titles = NULL,
  functional_groups = functional_groups,
  figure_colors = NULL
)

abundance0_f0_all <- (biomass[[1]][, age_name[1]] * 1000000 / waa[[1]][, age_name[1]])[time_id]

# All functional groups F = 0 and no environmental impacts
biomass <- read_ewe_output(
  file_path = here::here("data", "ewe", "7ages_newsim_om3", "ewe7ages_ecosim_om3_F0_all_functional_groups_noEnv", "ecosim_forcing_pdsi_egg_amo1"),
  file_names = "biomass_monthly.csv",
  skip_nrows = 8,
  plot = FALSE,
  figure_titles = NULL,
  functional_groups = functional_groups,
  figure_colors = NULL
)
time_id <- seq(1, nrow(biomass[[1]]), by = 12)
biomass_f0_all_noEnv <- apply(biomass[[1]][, age_name], 1, sum)[time_id] * 1000000

# R0
waa <- read_ewe_output(
  file_path = here::here("data", "ewe", "7ages_newsim_om3", "ewe7ages_ecosim_om3_F0_all_functional_groups_noEnv", "ecosim_forcing_pdsi_egg_amo1"),
  file_names = "weight_monthly.csv",
  skip_nrows = 8,
  plot = FALSE,
  figure_titles = NULL,
  functional_groups = functional_groups,
  figure_colors = NULL
)

abundance0_f0_all_noEnv <- (biomass[[1]][, age_name[1]] * 1000000 / waa[[1]][, age_name[1]])[time_id]

biomass_f0 <- data.frame(
  year = start_year:(start_year + length(time_id) - 1),
  data_type = "Biomass of menhaden-like species (mt)",
  f0_menhaden = biomass_f0_menhaden, 
  f0_menhaden_bass = biomass_f0_menhaden_bass, 
  f0_all = biomass_f0_all,
  f0_all_noEnv = biomass_f0_all_noEnv
)

abundance0_f0 <- data.frame(
  year = start_year:(start_year + length(time_id) - 1),
  data_type = "Abundance of age 0 menhaden-like species",
  f0_menhaden = abundance0_f0_menhaden, 
  f0_menhaden_bass = abundance0_f0_menhaden_bass, 
  f0_all = abundance0_f0_all,
  f0_all_noEnv = abundance0_f0_all_noEnv
)

biomass_f0_reshape <- reshape2::melt(biomass_f0, id=c("year", "data_type"))
abundance0_f0_reshape <- reshape2::melt(abundance0_f0, id=c("year", "data_type"))
f0_data <- rbind(biomass_f0_reshape, abundance0_f0_reshape)

colnames(f0_data) <- c("Year", "Data_Type", "Scenario", "Value")
ggplot(f0_data, aes(x = Year, y = Value, color = Scenario)) +
  geom_line(aes(linetype=Scenario)) +
  facet_wrap(~Data_Type, scales = "free_y") +
  labs(
    x = "Year",
    y = "Value"
  ) +
  theme_bw()

B0_F0_menhaden <- mean(tail(biomass_f0_menhaden, n = length(ages) * 2))
B0_F0_all <- mean(tail(biomass_f0_all, n = length(ages) * 2))
B0_F0_mean <- mean(c(B0_F0_menhaden, B0_F0_all))

R0_F0_menhaden <- mean(tail(abundance0_f0_menhaden, n = length(ages) * 2))
R0_F0_all <- mean(tail(abundance0_f0_all, n = length(ages) * 2))
R0_F0_mean <- mean(c(R0_F0_menhaden, R0_F0_all))

file_path <- here::here("data", "ewe", "7ages_newsim_om3", "ewe7ages_ecosim_om3", "ecosim_forcing_pdsi_egg_amo1")
source(here::here("Rscript", "load_indices.R"))

set.seed(999)
# Load EwE biomass data

age_name <- paste0("AtlanticMenhaden", ages)

biomass <- read_ewe_output(
  file_path = file_path,
  file_names = "biomass_monthly.csv",
  skip_nrows = 8,
  plot = FALSE,
  figure_titles = NULL,
  functional_groups = functional_groups,
  figure_colors = NULL
)

time_id <- seq(1, nrow(biomass[[1]]), by = 12)[1:(length(model_year) + length(projection_year))]
biomass_ewe <- apply(biomass[[1]][, age_name], 1, sum) * 1000000
# Set up JABBA base case assessment

output_dir <- here::here("data", "data_poor", "om3")
if (!dir.exists(output_dir)) dir.create(output_dir)
```

## Case 0: stock assessment base run (terminal year = 1995)

```{r, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
# Load simulated input data
file_path <- here::here("data", "ewe", "7ages_newsim_om3", "ewe7ages_ecosim_om3", "ecosim_forcing_pdsi_egg_amo1")
source(here::here("Rscript", "load_indices.R"))
file_path <- here::here("data", "data_rich", paste0("OM3_", terminal_year))
if (!dir.exists(file_path)) dir.create(file_path)

depletion <- FALSE
depletion_ratio <- 0.8 # tried values between 0.3 - 0.8

generate_ss3(
  file_path = file_path,
  r0 = log(R0_F0_menhaden / 1000),
  steepness = 0.99,
  sigmar = 0.99,
  projection_f = 0.75, projection_catch = NULL,
  sa_data = sa_data, model_year = model_year,
  projection_year = projection_year,
  use_depletion = FALSE, depletion_ratio = NULL,
  initial_equilibrium_catch = TRUE,
  settlement_age = 1
)

## If settlement age = 0, settlement month = 1, and spawn month = 1
## Higher estimated biomass over time

# file_path <- here::here("data", "data_rich", "OM2_SettlementAge0")
# generate_ss3(
#   file_path = file_path,
#   r0 = 12, steepness = 0.55, sigmar = 0.5,
#   projection_f = 0.75, projection_catch = NULL,
#   sa_data = sa_data, model_year = model_year,
#   projection_year = projection_year,
#   use_depletion = FALSE, depletion_ratio = NULL,
#   initial_equilibrium_catch = TRUE,
#   settlement_age = 0
# )

## Run SS3
ss3_exe_path <- file.path(file_path, "ss_win.exe")
if (!file.exists(ss3_exe_path)) file.copy(here::here("data", "data_rich", "ss_win.exe"), file_path)

shell(
  paste0(
    "cd ", file_path,
    " & ss_win "
  )
)

# get FMSY
ss3list <- r4ss::SS_output(
  dir = file_path,
  verbose = TRUE,
  printstats = TRUE
)

fmsy <- ss3list$derived_quants$Value[ss3list$derived_quants$Label == "annF_MSY"]


# Re-run SS3 with projection_f = fmsy
generate_ss3(
  file_path = file_path,
  r0 = log(R0_F0_menhaden / 1000),
  steepness = 0.99,
  # sigmar = 0.99,
  sigmar = ss3list$sigma_R_info$alternative_sigma_R[1],
  projection_f = fmsy, projection_catch = NULL,
  sa_data = sa_data, model_year = model_year,
  projection_year = projection_year,
  use_depletion = FALSE, depletion_ratio = NULL,
  initial_equilibrium_catch = TRUE,
  settlement_age = 1
)

if (!file.exists(ss3_exe_path)) file.copy(here::here("data", "data_rich", "ss_win.exe"), file_path)

shell(
  paste0(
    "cd ", file_path,
    " & ss_win "
  )
)

# plot r4ss -------------------------------------------------------

# read the model output and print diagnostic messages
ss3list <- r4ss::SS_output(
  dir = file_path,
  verbose = TRUE,
  printstats = TRUE
)

# plot the results
# r4ss::SS_plots(ss3list)
# unlink(file.path(file_path, "plots"), recursive=TRUE)

# MCMC run
run_mcmc <- FALSE
mcmc_dir <- here::here(dirname(here::here()), paste0("OM3_mcmc_", terminal_year))
if (!dir.exists(mcmc_dir)) dir.create(mcmc_dir)

if (run_mcmc & length(dir(mcmc_dir, all.files = TRUE)) > 0) {
  generate_ss3(
    file_path = mcmc_dir,
    r0 = log(R0_F0_menhaden / 1000),
    steepness = 0.99,
    # sigmar = 0.99,
    sigmar = ss3list$sigma_R_info$alternative_sigma_R[1],
    projection_f = fmsy, projection_catch = NULL,
    sa_data = sa_data, model_year = model_year,
    projection_year = projection_year,
    use_depletion = FALSE, depletion_ratio = NULL,
    initial_equilibrium_catch = TRUE,
    settlement_age = 1
  )

  ss3_exe_path <- file.path(mcmc_dir, "ss_win.exe")
  if (!file.exists(ss3_exe_path)) file.copy(here::here("data", "data_rich", "ss_win.exe"), ss3_exe_path)
  # shell(
  #   paste0(
  #     "cd ", mcmc_dir,
  #     " & ss_win ",
  #     "-mcmc 14000 -mcsave 10 -mcseed 91438",
  #     " & ss_win -mceval"
  #   )
  # )

  shell(
    paste0(
      "cd ", mcmc_dir,
      " & ss_win ",
      "-mcmc 1400000 -mcsave 1000 -mcseed 91438",
      " & ss_win -mceval"
    )
  )
}

mcmc_output <- r4ss::SSgetMCMC(mcmc_dir)
fmsy_mcmc <- mcmc_output$annF_MSY
bratio_terminal_mcmc <- mcmc_output[, paste0("Bratio_", terminal_year)]
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
ci_calculation <- function(distribution, value, std, year, data_type, ewe_data) {
  if (distribution == "lognormal") {
    std_log <- sqrt(log(1 + (std / value)^2))

    ci_lower <- qlnorm(
      p = 0.025,
      meanlog = log(value),
      sdlog = std_log
    )

    ci_upper <- qlnorm(
      p = 0.975,
      meanlog = log(value),
      sdlog = std_log
    )
  }

  if (distribution == "normal") {
    ci_upper <- value + 1.96 * std
    ci_lower <- pmax(value - 1.96 * std, 0)
  }

  return(data.frame(
    value = value,
    std = std,
    ci_upper = ci_upper,
    ci_lower = ci_lower, 
    year = year, 
    data_type = data_type,
    ewe_data = ewe_data
  ))
}
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}

# Compare SS3 estimate with EwE "true" values ---------------------
# Comparisons
project_path <- here::here()
ewe_output_path <- file_path <- here::here("data", "ewe", "7ages_newsim_om3", "ewe7ages_ecosim_om3", "ecosim_forcing_pdsi_egg_amo1")

# Biomass
biomass <- read_ewe_output(
  file_path = ewe_output_path,
  file_names = "biomass_monthly.csv",
  skip_nrows = 8,
  plot = FALSE,
  figure_titles = NULL,
  functional_groups = functional_groups,
  figure_colors = NULL
)

time_id <- seq(1, nrow(biomass[[1]]), by = 12)[1:(length(model_year))]
ssb_ewe <- apply(biomass[[1]][, age_name] * matrix(rep(t(sa_data$biodata$maturity_matrix), 12), ncol = ncol(sa_data$biodata$maturity_matrix), byrow = TRUE), 1, sum) * 1000000
# ssb <- biomass[[1]][time_id, age_name] * sa_data$biodata$maturity_matrix
# ssb_ewe <- apply(ssb, 1, sum)*1000000

biomass_ewe <- apply(biomass[[1]][, age_name], 1, sum) * 1000000

waa <- read_ewe_output(
  file_path = ewe_output_path,
  file_names = "weight_monthly.csv",
  skip_nrows = 8,
  plot = FALSE,
  figure_titles = NULL,
  functional_groups = functional_groups,
  figure_colors = NULL
)

abundance_ewe <- apply(biomass[[1]][, age_name] * 1000000 / waa[[1]][, age_name], 1, sum)

recruit_ewe <- biomass[[1]][, "AtlanticMenhaden0"] * 1000000 / waa[[1]][, "AtlanticMenhaden0"]

mortality <- read.csv(file = here::here("data", "ewe", "7ages_newsim_om3", "fatage.csv"))

mortality_ewe <- apply(mortality[, 2:ncol(mortality)], 1, max)
model_year_id <- which(ss3list$timeseries$Yr %in% model_year)
projection_year_id <- which(ss3list$timeseries$Yr %in% projection_year)

derived_quants <- ss3list[["derived_quants"]]
# SB
sb_data <- ci_calculation(
  distribution = "normal", 
  value = derived_quants[paste0("SSB_", model_year), "Value"],
  std = derived_quants[paste0("SSB_", model_year), "StdDev"], 
  year = model_year, 
  data_type = "SB (mt)", 
  ewe_data = ssb_ewe[time_id]
)

# R
r_data <- ci_calculation(
  distribution = "lognormal", 
  value = head(derived_quants[paste0("Recr_", model_year), "Value"], -1),
  std = head(derived_quants[paste0("Recr_", model_year), "StdDev"], -1), 
  year = model_year[-1], 
  data_type = "R (x1000 fish)", 
  ewe_data = recruit_ewe[time_id[-1]]/1000
)

# F
f_data <- ci_calculation(
  distribution = "normal", 
  value = derived_quants[paste0("F_", model_year), "Value"],
  std = derived_quants[paste0("F_", model_year), "StdDev"], 
  year = model_year, 
  data_type = "F", 
  ewe_data = mortality_ewe[1:length(model_year)]
)

time_series_data <- rbind(sb_data, r_data, f_data)
time_series_data_reshape <- reshape2::melt(time_series_data, id = c("year", "data_type"))
ggplot(time_series_data, aes(x = year, y = value)) + 
  facet_wrap(~data_type, scales = "free_y") +
  geom_line(col='blue') + 
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.1)+
  geom_point(aes(x = year, y = ewe_data))+
  labs(
    x = "Year",
    y = "Value"
  ) +
  theme_bw() 
```
## Cases 1-5 are based on the settings from case 0
- Case 1: Link Atlantic Multidecadal Oscillation Index with menhaden biomass estimates and adjust projections: AMO is an indicator of climate conditions and would affect recruitment variability of menhaden-like species
- Case 2: Link Palmer drought severity index with menhaden biomass estimates and adjust projections: PSDI is a long-term indicator of drought conditions and it reflects river discharge and precipitation
- Case 3: Link biomass of Striped bass from the EwE with menhaden biomass estimates and adjust projections because bass is a major predator
- Case 4: Link catch per unit effort of menhaden with menhaden biomass estimates and adjust projections 
- Case 5: Link mean age for fishing fleet with menhaden biomass estimates and adjust projections 

*Notes*: here, the biomass estimates are spawning biomass estimates.

- Linear regression models from case 1 - 5
  - True biomass of menhaden-like species as functions of AMO, PDSI, biomass of striped bass, catch per unit effort of menhaden, mean age for fishing fleet 
### Status of indicators (SOI)

- If stock-indicator relationship is positive, $SOI_{y} = \frac{I_{y}-I_{y}^{min}}{I_{y}^{max}-I_{y}^{min}}$
  
- If stock-indicator relationship is negative, $SOI_{y} = 1-\frac{I_{y}-I_{y}^{min}}{I_{y}^{max}-I_{y}^{min}}$
  
  where $I_{y}$ represents indicator value in year y. $I_{y}^{min}$ and $I_{y}^{max}$ represent the minimum and maximum values of $I$ from the time series.
  
### Adjust projections

- If $\frac{B1995_{i}}{BMSY} > 1$, $F^{'}_{i} = FMSY^{min} + SOI1995 \times (FMSY^{max}-FMSY^{min})$

- If $\frac{B1995_{i}}{BMSY} \le 1$ and $\frac{B1995_{i}}{BMSY} > 0.5$, $F^{'}_{i} = SOI1995 \times \frac{B1995_{i}}{BMSY} \times FMSY_{i}$
  
- If $\frac{B1995_{i}}{BMSY} \le 0.5$, $F^{'}_{i} = 0$

where $i$ represents individual iterations

```{r,  echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}

# Load mean age for fishery fleet
om_caa <- om_caa_temp <- sa_data$fishery$om_caa_abundance
om_caa$sum <- apply(om_caa_temp, 1, sum)
om_caa$prodsum <- apply(t(om_caa_temp) * c(1:7), 2, sum)
om_caa$meanage <- om_caa$prodsum / om_caa$sum

obs_caa <- obs_caa_temp <- sa_data$fishery$obs_caa_prop$fleet1
obs_caa$sum <- apply(obs_caa_temp, 1, sum)
obs_caa$prodsum <- apply(t(obs_caa_temp) * c(1:7), 2, sum)
obs_caa$meanage <- obs_caa$prodsum / obs_caa$sum

lm_slope <- data.frame(
  case = "True indices",
  amo = NA,
  # pcp = NA,
  bassB = NA,
  # price = NA,
  pdsi = NA,
  cpue = NA,
  meanage = NA
)

biomass_ewe <- ssb_ewe

year_id <- seq(1, nrow(amo_unsmooth_lag1), by = 12)
index_year <- c(model_year)
lag <- 1
biomass_lag_id <- (1 + lag):length(index_year)
index_lag_id <- 1:(length(index_year) - lag)

amo <- amo_unsmooth_lag1[year_id, ]
amo_lm <- lm(biomass_ewe[time_id][biomass_lag_id] ~ amo$scaled_value[index_lag_id])
amo_fit <- fitted(amo_lm)
lm_slope$amo <- paste0(
  round(summary(amo_lm)$coefficients[2, 1], digits = 2),
  if (summary(amo_lm)$coefficients[2, 4] <= 0.05) {
    "*"
  }
)

# pcp <- precipitation[year_id, ]
# pcp_lm <- lm(biomass_ewe[time_id][biomass_lag_id] ~ pcp$scaled_value[index_lag_id])
# pcp_fit <- fitted(pcp_lm)
# lm_slope$pcp <- paste0(
#   round(summary(pcp_lm)$coefficients[2, 1], digits = 2),
#   if(summary(pcp_lm)$coefficients[2, 4] <= 0.05) {"*"})

pdsi <- palmer_drought_severity_index[year_id, ]
pdsi_lm <- lm(biomass_ewe[time_id][biomass_lag_id] ~ pdsi$scaled_value[index_lag_id])
pdsi_fit <- fitted(pdsi_lm)
lm_slope$pdsi <- paste0(
  round(summary(pdsi_lm)$coefficients[2, 1], digits = 2),
  if (summary(pdsi_lm)$coefficients[2, 4] <= 0.05) {
    "*"
  }
)

bassB <- bass_bio[bass_bio$Year %in% year_id, ]
bassB_lm <- lm(biomass_ewe[time_id][biomass_lag_id] ~ bassB$bass_bio[index_lag_id])
bassB_fit <- fitted(bassB_lm)
lm_slope$bassB <- paste0(
  round(summary(bassB_lm)$coefficients[2, 1], digits = 2),
  if (summary(bassB_lm)$coefficients[2, 4] <= 0.05) {
    "*"
  }
)

# sub_menhadenP <- menhaden_price$Inflation.Adjust.Price.Per.MT[menhaden_price$Year %in% index_year]
# price_lm <- lm(biomass_ewe[time_id][biomass_lag_id] ~ sub_menhadenP[index_lag_id])
# price_fit <- fitted(price_lm)
# lm_slope$price <- paste0(
#   round(summary(price_lm)$coefficients[2, 1], digits = 2),
#   if(summary(price_lm)$coefficients[2, 4] <= 0.05) {"*"})

effort <- apply(ewe_faa[, grep("menhaden", colnames(ewe_faa))] / ewe_catchability[seq(1, nrow(amo_unsmooth_lag1), by = 12), grep("menhaden", colnames(ewe_catchability))], 1, sum)

cpue <- sa_data$fishery$obs_total_catch_biomass$fleet1 / effort
cpue_lm <- lm(biomass_ewe[time_id][biomass_lag_id] ~ cpue[index_lag_id])
cpue_fit <- fitted(cpue_lm)
lm_slope$cpue <- paste0(
  round(summary(cpue_lm)$coefficients[2, 1], digits = 2),
  if (summary(cpue_lm)$coefficients[2, 4] <= 0.05) {
    "*"
  }
)

meanage <- om_caa$meanage
meanage_lm <- lm(biomass_ewe[time_id][biomass_lag_id] ~ meanage[index_lag_id])
meanage_fit <- fitted(meanage_lm)
lm_slope$meanage <- paste0(
  round(summary(meanage_lm)$coefficients[2, 1], digits = 2),
  if (summary(meanage_lm)$coefficients[2, 4] <= 0.05) {
    "*"
  }
)

# linear regression analysis summary table
lm_data_om <- rbind(
  data.frame(
    Menhaden_Biomass = biomass_ewe[time_id][biomass_lag_id],
    Variable = "AMO",
    Index_Value = amo$scaled_value[index_lag_id]
  ),
  data.frame(
    Menhaden_Biomass = biomass_ewe[time_id][biomass_lag_id],
    Variable = "PDSI",
    Index_Value = pdsi$scaled_value[index_lag_id]
  ),
  data.frame(
    Menhaden_Biomass = biomass_ewe[time_id][biomass_lag_id],
    Variable = "Biomass of Striped bass",
    Index_Value = bassB$bass_bio[index_lag_id]
  ),
  data.frame(
    Menhaden_Biomass = biomass_ewe[time_id][biomass_lag_id],
    Variable = "Menhaden CPUE",
    Index_Value = cpue[index_lag_id]
  ),
  data.frame(
    Menhaden_Biomass = biomass_ewe[time_id][biomass_lag_id],
    Variable = "Menhaden mean age",
    Index_Value = meanage[index_lag_id]
  )
)

lm_data_om$model <- "OM"

# jpeg(filename = file.path(figure_path, paste0("lm_slope_om_", terminal_year, ".jpeg")), width = 200, height = 100, units = "mm", res = 1800)
p <- gridExtra::tableGrob(lm_slope)
gridExtra::grid.arrange(p)
# dev.off()
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}

# Projection: cases 1 - 5 ---------------------------

lm_slope <- data.frame(
  case = "PDSI+AMO1 Case",
  projection_year = 1:length(projection_year),
  amo = NA,
  pdsi = NA,
  bassB = NA,
  cpue = NA,
  meanage = NA
)

for (projection_year_id in 1:length(projection_year)) {

  # if (projection_year_id ==1) {
  #   menhaden_b <- ss3list$timeseries$Bio_all[model_year_id]
  # } else {
  #   menhaden_b <- c(ss3list$timeseries$Bio_all[model_year_id], ss3list$timeseries$Bio_all[1:(projection_year_id-1)])
  # }
  #
  #
  # year_id <- seq(1, nrow(amo_unsmooth_lag1), by = 12)[1:(length(model_year)+projection_year_id-1)]
  #
  # if (projection_year_id == 1) {
  #   index_year = model_year
  # } else {
  #   index_year <- c(model_year, projection_year[1:(projection_year_id-1)])
  # }

  # menhaden_b <- ss3list$timeseries$Bio_all[model_year_id]
  menhaden_b <- ss3list$timeseries$SpawnBio[model_year_id]

  year_id <- seq(1, nrow(amo_unsmooth_lag1), by = 12)[1:length(model_year)]

  index_year <- model_year

  # Linear regression model -----------------------------------------

  lag <- 1
  biomass_lag_id <- (1 + lag):length(index_year)
  index_lag_id <- 1:(length(index_year) - lag)

  amo <- amo_unsmooth_lag1[year_id, ]
  amo_lm <- lm(menhaden_b[biomass_lag_id] ~ amo$scaled_value[index_lag_id])
  amo_fit <- fitted(amo_lm)
  lm_slope$amo <- paste0(
    round(summary(amo_lm)$coefficients[2, 1], digits = 2),
    if (summary(amo_lm)$coefficients[2, 4] <= 0.05) {
      "*"
    }
  )

  pdsi <- palmer_drought_severity_index[year_id, ]
  pdsi_lm <- lm(menhaden_b[biomass_lag_id] ~ pdsi$scaled_value[index_lag_id])
  pdsi_fit <- fitted(pdsi_lm)
  lm_slope$pdsi <- paste0(
    round(summary(pdsi_lm)$coefficients[2, 1], digits = 2),
    if (summary(pdsi_lm)$coefficients[2, 4] <= 0.05) {
      "*"
    }
  )

  bassB <- bass_bio[bass_bio$Year %in% year_id, ]
  bassB_lm <- lm(menhaden_b[biomass_lag_id] ~ bassB$bass_bio[index_lag_id])
  bassB_fit <- fitted(bassB_lm)
  lm_slope$bassB <- paste0(
    round(summary(bassB_lm)$coefficients[2, 1], digits = 2),
    if (summary(bassB_lm)$coefficients[2, 4] <= 0.05) {
      "*"
    }
  )

  effort <- apply(ewe_faa[ewe_faa$X %in% ewe_faa$X[1:length(year_id)], grep("menhaden", colnames(ewe_faa))] / ewe_catchability[year_id, grep("menhaden", colnames(ewe_catchability))], 1, sum)
  cpue <- (sa_data$fishery$om_total_catch_biomass / effort)[1:length(year_id)]
  cpue_lm <- lm(menhaden_b[biomass_lag_id] ~ cpue[index_lag_id])
  cpue_fit <- fitted(cpue_lm)
  lm_slope$cpue <- paste0(
    round(summary(cpue_lm)$coefficients[2, 1], digits = 2),
    if (summary(cpue_lm)$coefficients[2, 4] <= 0.05) {
      "*"
    }
  )

  meanage <- obs_caa[1:length(year_id), "meanage"]
  meanage_lm <- lm(menhaden_b[biomass_lag_id] ~ meanage[index_lag_id])
  meanage_fit <- fitted(meanage_lm)
  lm_slope$meanage <- paste0(
    round(summary(meanage_lm)$coefficients[2, 1], digits = 2),
    if (summary(meanage_lm)$coefficients[2, 4] <= 0.05) {
      "*"
    }
  )

  if (projection_year_id == 1) {
    lm_data_em <- rbind(
      data.frame(
        Menhaden_Biomass = menhaden_b[biomass_lag_id],
        Variable = "AMO",
        Index_Value = amo$scaled_value[index_lag_id]
      ),
      data.frame(
        Menhaden_Biomass = menhaden_b[biomass_lag_id],
        Variable = "PDSI",
        Index_Value = pdsi$scaled_value[index_lag_id]
      ),
      data.frame(
        Menhaden_Biomass = menhaden_b[biomass_lag_id],
        Variable = "Biomass of Striped bass",
        Index_Value = bassB$bass_bio[index_lag_id]
      ),
      data.frame(
        Menhaden_Biomass = menhaden_b[biomass_lag_id],
        Variable = "Menhaden CPUE",
        Index_Value = cpue[index_lag_id]
      ),
      data.frame(
        Menhaden_Biomass = menhaden_b[biomass_lag_id],
        Variable = "Menhaden mean age",
        Index_Value = meanage[index_lag_id]
      )
    )
    lm_data_em$model <- "EM"
  }



  # status of indicators --------------------------------------------

  amo_soi <- calc_soi(
    indicator_data = amo$scaled_value,
    slope = coef(amo_lm)[2]
  )

  pdsi_soi <- calc_soi(
    indicator_data = pdsi$scaled_value,
    slope = coef(pdsi_lm)[2]
  )

  bassB_soi <- calc_soi(
    indicator_data = bassB$bass_bio,
    slope = coef(bassB_lm)[2]
  )

  cpue_soi <- calc_soi(
    indicator_data = effort,
    slope = coef(cpue_lm)[2]
  )

  meanage_soi <- calc_soi(
    indicator_data = meanage,
    slope = coef(meanage_lm)[2]
  )

  if (projection_year_id == 1) {
    scaled_data <- data.frame(
      year = model_year,
      projection_year_id = projection_year_id,
      amo = scale(amo$scaled_value)[, 1],
      pdsi = scale(pdsi$scaled_value)[, 1],
      bassB = scale(bassB$bass_bio)[, 1],
      cpue = scale(cpue)[, 1],
      meanage = scale(meanage)[, 1],
      menhadenB = scale(menhaden_b)[, 1]
    )

    soi_data <- data.frame(
      year = model_year,
      projection_year_id = projection_year_id,
      amo = amo_soi,
      pdsi = pdsi_soi,
      bass_b = bassB_soi,
      cpue = cpue_soi,
      meanage = meanage_soi
    )
  } else {
    scaled_data <- rbind(
      scaled_data,
      data.frame(
        year = index_year,
        projection_year_id = projection_year_id,
        amo = scale(amo$scaled_value)[, 1],
        pdsi = scale(pdsi$scaled_value)[, 1],
        bassB = scale(bassB$bass_bio)[, 1],
        cpue = scale(cpue)[, 1],
        meanage = scale(meanage)[, 1],
        menhadenB = scale(menhaden_b)[, 1]
      )
    )

    soi_data <- rbind(
      soi_data,
      data.frame(
        year = index_year,
        projection_year_id = projection_year_id,
        amo = amo_soi,
        pdsi = pdsi_soi,
        bass_b = bassB_soi,
        cpue = cpue_soi,
        meanage = meanage_soi
      )
    )
  }


  # Adjusted FMSY ----------------------------------------------------
  # if (projection_year_id == 1) {
  #   Bt_BMSY <- ss3list$Kobe$B.Bmsy[length(model_year)]
  #   Bt_BMSY_sd <- ss3list$derived_quants$StdDev[ss3list$derived_quants$Label == paste0("Bratio_", tail(model_year, n = 1))]
  # } else {
  #   Bt_BMSY <- ss3list$Kobe$B.Bmsy[length(model_year) + projection_year_id - 1]
  #   Bt_BMSY_sd <- ss3list$derived_quants$StdDev[ss3list$derived_quants$Label == paste0("Bratio_", projection_year[projection_year_id] - 1)]
  # }

  # if (projection_year_id == 1) {
  #   Bt_BMSY <- ss3list$Kobe$B.Bmsy[length(model_year)]
  #
  # } else {
  #   Bt_BMSY <- ss3list$Kobe$B.Bmsy[length(model_year)+projection_year_id-1]
  # }

  # randomly draw 1000 values
  # ss3_fmsy <- rnorm(1000, ss3list$derived_quants$Value[ss3list$derived_quants$Label == "annF_MSY"], 0.5)
  # ss3_Bt_BMSY <- rnorm(1000, Bt_BMSY, 1.0)
  # ss3_Bt_BMSY[ss3_Bt_BMSY<0] <- 0.0001

  # ss3_fmsy_mean <- ss3list$derived_quants$Value[ss3list$derived_quants$Label == "annF_MSY"]
  # ss3_fmsy_sd <- ss3list$derived_quants$StdDev[ss3list$derived_quants$Label == "annF_MSY"]

  # ss3_fmsy <- c(ss3_fmsy_mean - 1.96 * ss3_fmsy_sd, ss3_fmsy_mean, ss3_fmsy_mean + 1.96 * ss3_fmsy_sd)
  # ss3_Bt_BMSY <- rep(Bt_BMSY, length(ss3_fmsy))

  # ss3_fmsy[ss3_fmsy < 0] <- 0.1

  ss3_fmsy <- fmsy_mcmc
  ss3_Bt_BMSY <- bratio_terminal_mcmc

  amo_fmsy <- adjust_projection_jabba(
    FMSY = ss3_fmsy,
    soi = tail(amo_soi, n = 1),
    Bt_BMSY = as.matrix(ss3_Bt_BMSY)
  )
  pdsi_fmsy <- adjust_projection_jabba(
    FMSY = ss3_fmsy,
    soi = tail(pdsi_soi, n = 1),
    Bt_BMSY = as.matrix(ss3_Bt_BMSY)
  )
  bassB_fmsy <- adjust_projection_jabba(
    FMSY = ss3_fmsy,
    soi = tail(bassB_soi, n = 1),
    Bt_BMSY = as.matrix(ss3_Bt_BMSY)
  )
  cpue_fmsy <- adjust_projection_jabba(
    FMSY = ss3_fmsy,
    soi = tail(cpue_soi, n = 1),
    Bt_BMSY = as.matrix(ss3_Bt_BMSY)
  )
  meanage_fmsy <- adjust_projection_jabba(
    FMSY = ss3_fmsy,
    soi = tail(meanage_soi, n = 1),
    Bt_BMSY = as.matrix(ss3_Bt_BMSY)
  )

  if (projection_year_id == 1) {
    fmsy_data <- data.frame(
      iter = 1:length(amo_fmsy),
      projection_year_id = projection_year[projection_year_id],
      SS3 = ss3_fmsy,
      amo = amo_fmsy,
      pdsi = pdsi_fmsy,
      bassB = bassB_fmsy,
      cpue = cpue_fmsy,
      meanage = meanage_fmsy
    )
  } else {
    fmsy_data <- rbind(
      fmsy_data,
      data.frame(
        iter = 1:length(amo_fmsy),
        projection_year_id = projection_year[projection_year_id],
        SS3 = ss3_fmsy,
        amo = amo_fmsy,
        pdsi = pdsi_fmsy,
        bassB = bassB_fmsy,
        cpue = cpue_fmsy,
        meanage = meanage_fmsy
      )
    )
  }
}
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
# Linear regression figure
lm_data <- rbind(lm_data_om, lm_data_em)
# jpeg(filename = file.path(figure_path, paste0("linear_regression", terminal_year, ".jpeg")), width = 200, height = 100, units = "mm", res = 1800)
ggplot(lm_data, aes(x = Index_Value, y = Menhaden_Biomass, color = model)) +
  geom_point() +
  geom_smooth(method = lm) +
  facet_wrap(~Variable, scales = "free_x") +
  labs(
    title = "Linear regression analysis",
    x = "Indicator Value",
    y = "Menhaden spawning biomass (mt)"
  ) +
  theme_bw()
# dev.off()

soi_data_melt <- reshape2::melt(
  soi_data,
  id = c("year", "projection_year_id")
)
soi_data_melt$projection_year_id <- rep(rep(projection_year, each = length(model_year)), times = ncol(soi_data) - 2)

# SOI figure
# jpeg(filename = file.path(figure_path, paste0("soi", terminal_year, ".jpeg")), width = 200, height = 100, units = "mm", res = 1800)
ggplot(soi_data_melt[soi_data_melt$projection_year_id == projection_year[1], ], aes(x = year, y = value)) +
  geom_line() +
  facet_wrap(~variable, scales = "free_y") +
  labs(
    title = "Status of Indicators",
    x = "Year",
    y = "Status of Indicators"
  ) +
  theme_bw()
# dev.off()

fmsy_data_melt <- reshape2::melt(
  fmsy_data,
  id = c("iter", "projection_year_id")
)
fmsy_data_melt$projection_year_id <- as.factor(fmsy_data_melt$projection_year_id)

# ggplot(fmsy_data_melt, aes(x = iter, y = value, color = projection_year_id)) +
#   geom_line() +
#   facet_wrap(~variable) +
#   labs(
#     title = "FMSY",
#     x = "Iteration",
#     y = "FMSY"
#   ) +
#   theme_bw()

# FMSY figure
# jpeg(filename = file.path(figure_path, paste0("FMSY", terminal_year, ".jpeg")), width = 200, height = 100, units = "mm", res = 1800)
ggplot(fmsy_data_melt, aes(x = variable, y = value, color = projection_year_id)) +
  geom_boxplot() +
  labs(
    title = "FMSY",
    x = "",
    y = "FMSY"
  ) +
  theme_bw()
# dev.off()

# jpeg(filename = file.path(figure_path, paste0("violin_FMSY", terminal_year, ".jpeg")), width = 200, height = 100, units = "mm", res = 1800)
# ggplot(fmsy_data_melt, aes(x = variable, y = value, color = projection_year_id)) +
#   geom_violin()+
#   geom_boxplot(width=0.1) +
#   labs(
#     title = "FMSY",
#     x = "",
#     y = "FMSY"
#   ) +
#   theme_bw()
# dev.off()


fmsy_data_melt_median <- aggregate(value ~ projection_year_id + variable, data = fmsy_data_melt, median)
fmsy_data_melt_median$projection_year_id <- as.numeric(as.character(fmsy_data_melt_median$projection_year_id))

# jpeg(filename = file.path(figure_path, paste0("median_fmsy", terminal_year, ".jpeg")), width = 200, height = 100, units = "mm", res = 1800)
# ggplot(fmsy_data_melt_median, aes(x = projection_year_id, y = value, color = variable)) +
#   geom_line() +
#   labs(
#     title = "Median FMSY from JABBA and adjusted FMSY",
#     x = "",
#     y = "FMSY"
#   ) +
#   theme_bw()
# dev.off()
```

- Slope values from linear regression models

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
knitr::kable(lm_slope)
```

- Project biomass based on $F_{MSY}$
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
# Re-run SS3 with Fadj

projection_file_path <- here::here("data", "data_rich", paste0("OM3_projections_", terminal_year))
if (!dir.exists(projection_file_path)) dir.create(projection_file_path)

fmsy_vec <- aggregate(value ~ variable, fmsy_data_melt_median, median)
if (!file.exists(file.path(projection_file_path, "ss3_projections.RData"))) {
  ss3_projection <- list()
  for (i in 1:nrow(fmsy_vec)) {
    generate_ss3(
      file_path = projection_file_path,
      r0 = log(R0_F0_menhaden / 1000),
      steepness = 0.99,
      # sigmar = 0.99,
      sigmar = ss3list$sigma_R_info$alternative_sigma_R[1],
      projection_f = fmsy_vec$value[i], projection_catch = NULL,
      sa_data = sa_data, model_year = model_year,
      projection_year = projection_year,
      use_depletion = FALSE, depletion_ratio = NULL,
      initial_equilibrium_catch = TRUE,
      settlement_age = 1
    )

    if (!file.exists(file.path(projection_file_path, "ss_win.exe"))) file.copy(here::here("data", "data_rich", "ss_win.exe"), projection_file_path)

    shell(
      paste0(
        "cd ", projection_file_path,
        " & ss_win "
      )
    )

    ss3_output <- SS_output(
      dir = projection_file_path,
      verbose = TRUE,
      printstats = TRUE
    )

    ss3_projection[[i]] <- ss3_output
  }

  save(ss3_projection, file = file.path(projection_file_path, "ss3_projections.RData"))
} else {
  load(file.path(projection_file_path, "ss3_projections.RData"))
}


projection_f <- rbind(
  fmsy_data_melt_median,
  data.frame(
    projection_year_id = projection_year,
    variable = "om",
    value = compensation_msy$FMSY
  )
)

fishery_sel <- IFA4EBFM::logistic(
  pattern = "double_logistic",
  x = sa_data$biodata$ages,
  slope_asc = 3.1,
  location_asc = 1.8,
  slope_desc = 0.88,
  location_desc = 0.01
)

for (i in 1:nrow(projection_f)) {
  if (projection_f[i, "variable"] == "om" & !is.null(om_fmsy_group)) {
    projection_f[i, paste0("fmsy_", sa_data$biodata$ages)] <- om_fmsy_group
    projection_f[i, paste0("fmsy1.25_", sa_data$biodata$ages)] <- om_fmsy_group * 1.25
    projection_f[i, paste0("fmsy0.75_", sa_data$biodata$ages)] <- om_fmsy_group * 0.75
  } else {
    projection_f[i, paste0("fmsy_", sa_data$biodata$ages)] <- projection_f$value[i] * fishery_sel
    projection_f[i, paste0("fmsy1.25_", sa_data$biodata$ages)] <- projection_f$value[i] * fishery_sel * 1.25
    projection_f[i, paste0("fmsy0.75_", sa_data$biodata$ages)] <- projection_f$value[i] * fishery_sel * 0.75
  }
}

write.csv(fmsy_data_melt, here::here("data", "data_rich", paste0("fmsy_data", terminal_year, ".csv")))
write.csv(projection_f, here::here("data", "data_rich", paste0("fmsy_median_data", terminal_year, ".csv")))

ssb_label <- paste0("SSB_", projection_year)
recruit_label <- paste0("Recr_", projection_year)
catch_label <- paste0("ForeCatch_", projection_year)


for (i in 1:nrow(fmsy_vec)) {
  fmsy_data_melt_median$ssb[fmsy_data_melt_median$variable == fmsy_vec$variable[i]] <- ss3_projection[[i]]$derived_quants$Value[ss3_projection[[i]]$derived_quants$Label %in% ssb_label]
  fmsy_data_melt_median$ssb_std[fmsy_data_melt_median$variable == fmsy_vec$variable[i]] <- ss3_projection[[i]]$derived_quants$StdDev[ss3_projection[[i]]$derived_quants$Label %in% ssb_label]

  fmsy_data_melt_median$recruit[fmsy_data_melt_median$variable == fmsy_vec$variable[i]] <- ss3_projection[[i]]$derived_quants$Value[ss3_projection[[i]]$derived_quants$Label %in% recruit_label]
  fmsy_data_melt_median$recruit_std[fmsy_data_melt_median$variable == fmsy_vec$variable[i]] <- ss3_projection[[i]]$derived_quants$StdDev[ss3_projection[[i]]$derived_quants$Label %in% recruit_label]

  fmsy_data_melt_median$catch[fmsy_data_melt_median$variable == fmsy_vec$variable[i]] <- ss3_projection[[i]]$derived_quants$Value[ss3_projection[[i]]$derived_quants$Label %in% catch_label]
  fmsy_data_melt_median$catch_std[fmsy_data_melt_median$variable == fmsy_vec$variable[i]] <- ss3_projection[[i]]$derived_quants$StdDev[ss3_projection[[i]]$derived_quants$Label %in% catch_label]

  fmsy_data_melt_median$F_FMSY[fmsy_data_melt_median$variable == fmsy_vec$variable[i]] <- tail(ss3_projection[[i]]$Kobe$F.Fmsy, n = 1) / fmsy_data_melt_median$value[fmsy_data_melt_median$variable == fmsy_vec$variable[i]]
  fmsy_data_melt_median$B_K[fmsy_data_melt_median$variable == fmsy_vec$variable[i]] <- tail(ss3_projection[[i]]$timeseries$Bio_all, n = 1) / ss3_projection[[i]]$timeseries$Bio_all[1]
  fmsy_data_melt_median$B_BMSY[fmsy_data_melt_median$variable == fmsy_vec$variable[i]] <- tail(ss3_projection[[i]]$Kobe$B.Bmsy, n = 1)
  fmsy_data_melt_median$Average_Biomass[fmsy_data_melt_median$variable == fmsy_vec$variable[i]] <- mean(ss3_projection[[i]]$timeseries$Bio_all[ss3_projection[[i]]$timeseries$Era == "FORE"])
  fmsy_data_melt_median$Bonanza_Period[fmsy_data_melt_median$variable == fmsy_vec$variable[i]] <- sum((ss3_projection[[i]]$timeseries$Bio_all[ss3_projection[[i]]$timeseries$Era == "FORE"] / ss3_projection[[i]]$timeseries$Bio_all[1]) > 0.8)
  fmsy_data_melt_median$Collapse_Period[fmsy_data_melt_median$variable == fmsy_vec$variable[i]] <- sum((ss3_projection[[i]]$timeseries$Bio_all[ss3_projection[[i]]$timeseries$Era == "FORE"] / ss3_projection[[i]]$timeseries$Bio_all[1]) < 0.2)
}


ggplot(fmsy_data_melt_median, aes(x = projection_year_id, y = ssb, color = variable)) +
  geom_line() +
  geom_point() +
  # facet_wrap(~variable) +
  labs(
    title = "",
    x = "",
    y = "SB (mt)"
  ) +
  theme_bw()

ggplot(fmsy_data_melt_median, aes(x = projection_year_id, y = recruit, color = variable)) +
  geom_line() +
  geom_point() +
  # facet_wrap(~variable) +
  labs(
    title = "",
    x = "",
    y = "R (x1000 fish)"
  ) +
  theme_bw()

projection_time_id <- tail(seq(1, nrow(biomass[[1]]), by = 12), n=projection_nyear)
sb_data <- ci_calculation(
  distribution = "normal", 
  value = fmsy_data_melt_median$ssb,
  std = fmsy_data_melt_median$ssb_std, 
  year = projection_year, 
  data_type = "SB (mt)", 
  ewe_data = ssb_ewe[projection_time_id]
)
sb_data$model <- fmsy_data_melt_median$variable

r_data <- ci_calculation(
  distribution = "lognormal", 
  value = fmsy_data_melt_median$recruit,
  std = fmsy_data_melt_median$recruit_std, 
  year = projection_year, 
  data_type = "R (x1000 fish)", 
  ewe_data = recruit_ewe[projection_time_id]/1000
)
r_data$model <- fmsy_data_melt_median$variable

time_series_data <- rbind(sb_data, r_data)
# ggplot(time_series_data, aes(x = year, y = value, color = model)) + 
#   facet_wrap(~data_type, scales = "free_y") +
#   geom_line(position=position_dodge(1)) + 
#   geom_pointrange(aes(ymin=ci_lower, ymax=ci_upper), 
#                 position=position_dodge(1)) +
#   labs(
#     x = "Year",
#     y = "Value"
#   ) +
#   theme_bw()
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
cases <- c(
  "ecosim_data_om_mediumF",
  "ecosim_data_rich_ss3_mediumF",
  "ecosim_data_rich_amo_mediumF",
  "ecosim_data_rich_pdsi_mediumF",
  "ecosim_data_rich_bassb_mediumF",
  "ecosim_data_rich_cpue_mediumF",
  "ecosim_data_rich_meanage_mediumF"
)
variables <- c("om", "SS3", "amo", "pdsi", "bassB", "cpue", "meanage")

om_projection <- list()

for (i in 1:length(cases)){
  file_path <- here::here("data", "ewe", "7ages_newsim_om3", paste0("ewe7ages_ecosim_om3_projection_", terminal_year), cases[i])
  # Load EwE biomass data
  
  biomass <- IFA4EBFM::read_ewe_output(
    file_path = file_path,
    file_names = "biomass_monthly.csv",
    skip_nrows = 8,
    plot = FALSE,
    figure_titles = NULL,
    functional_groups = functional_groups,
    figure_colors = NULL
  )
  
  waa <- IFA4EBFM::read_ewe_output(
    file_path = file_path,
    file_names = "weight_monthly.csv",
    skip_nrows = 8,
    plot = FALSE,
    figure_titles = NULL,
    functional_groups = functional_groups,
    figure_colors = NULL
  )
  
  catch <- IFA4EBFM::read_ewe_output(
    file_path = file_path,
    file_names = "catch_monthly.csv",
    skip_nrows = 8,
    plot = FALSE,
    figure_titles = NULL,
    functional_groups = functional_groups,
    figure_colors = NULL
  )
  
  time_id <- tail(seq(1, nrow(biomass[[1]]), by = 12), n = projection_nyear)
  
  abundance_ewe <- apply(biomass[[1]][, age_name] * 1000000 / waa[[1]][, age_name], 1, sum)
  
  om_dataframe <- data.frame(
    recruit = (biomass[[1]][, "AtlanticMenhaden0"] * 1000000 / waa[[1]][, "AtlanticMenhaden0"])[time_id],
    ssb = apply(biomass[[1]][, age_name] * matrix(rep(t(sa_data$biodata$maturity_matrix), 12), ncol = ncol(sa_data$biodata$maturity_matrix), byrow = TRUE), 1, sum)[time_id] * 1000000,
    catch = apply(catch[[1]][, age_name], 1, sum)[time_id] * 1000000,
    projection_year_id = projection_year,
    variable = variables[i]
  )
   
  
  om_projection[[i]] <- om_dataframe 
}

om_projection <- do.call(rbind.data.frame, om_projection)
names(om_projection) <- c("recruit", "ssb", "catch", "projection_year_id", "variable")

ggplot(om_projection, aes(x = projection_year_id, y = ssb, color = variable)) +
  geom_line() +
  geom_point() +
  labs(
    title = "",
    x = "",
    y = "SB (mt)"
  ) +
  theme_bw()

ggplot(om_projection, aes(x = projection_year_id, y = recruit, color = variable)) +
  geom_line() +
  geom_point() +
  labs(
    title = "",
    x = "",
    y = "R (x1000 fish)"
  ) +
  theme_bw()

ggplot(om_projection, aes(x = projection_year_id, y = catch, color = variable)) +
  geom_line() +
  geom_point() +
  labs(
    title = "",
    x = "",
    y = "Catch (mt)"
  ) +
  theme_bw()
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}

om_K <- B0_F0_menhaden
om_bmsy <- compensation_msy$BMSY
om_fmsy <- compensation_msy$FMSY

cases <- c(
  "ecosim_data_om_mediumF",
  "ecosim_data_rich_ss3_mediumF",
  "ecosim_data_rich_amo_mediumF",
  "ecosim_data_rich_pdsi_mediumF",
  "ecosim_data_rich_bassb_mediumF",
  "ecosim_data_rich_cpue_mediumF",
  "ecosim_data_rich_meanage_mediumF"
)

evaluation_table <- data.frame(
  Average_Catch = NA,
  B_K = NA,
  B_BMSY = NA,
  Average_Biomass = NA,
  Bonanza_Period = NA,
  Collapse_Period = NA
)

for (i in seq_along(cases)) {
  file_path <- here::here("data", "ewe", "7ages_newsim_om3", paste0("ewe7ages_ecosim_om3_projection_", terminal_year), cases[i])
  # Load EwE biomass data
  
  biomass <- read_ewe_output(
    file_path = file_path,
    file_names = "biomass_monthly.csv",
    skip_nrows = 8,
    plot = FALSE,
    figure_titles = NULL,
    functional_groups = functional_groups,
    figure_colors = NULL
  )

  time_id <-  seq(1, nrow(biomass[[1]]), by = 12)[1:(length(model_year)+projection_nyear)]
  biomass_ewe <- apply(biomass[[1]][, age_name], 1, sum) * 1000000

  catch <- read_ewe_output(
    file_path = file_path,
    file_names = "catch_monthly.csv",
    skip_nrows = 8,
    plot = FALSE,
    figure_titles = NULL,
    functional_groups = functional_groups,
    figure_colors = NULL
  )
  catch_ewe <- apply(catch[[1]][, age_name], 1, sum) * 1000000

  evaluation_table[i, ] <- c(
    # mean catch
    mean(tail(catch_ewe[time_id], n=length(projection_year))), 
    # Bend/K
    tail(biomass_ewe[time_id], n=1)/om_K,
    # Bend/BMSY
    tail(biomass_ewe[time_id], n=1)/om_bmsy,
    # mean biomass
    mean(tail(biomass_ewe[time_id], n=length(projection_year))),
    # Bonanza length
    sum((tail(biomass_ewe[time_id], n=length(projection_year))/om_K)>0.8),
    # Minmize collapse length
    sum((tail(biomass_ewe[time_id], n=length(projection_year))/om_K)<0.2)
  )
}

case_names <- unique(fmsy_data_melt_median$variable)
for (i in 1:length(case_names)) {
  evaluation_table <- rbind(
    evaluation_table,
    c(
      mean(fmsy_data_melt_median$catch[fmsy_data_melt_median$variable == case_names[i]]),
      tail(fmsy_data_melt_median$B_K[fmsy_data_melt_median$variable == case_names[i]], n = 1),
      tail(fmsy_data_melt_median$B_BMSY[fmsy_data_melt_median$variable == case_names[i]], n = 1),
      mean(fmsy_data_melt_median$Average_Biomass[fmsy_data_melt_median$variable == case_names[i]]),
      tail(fmsy_data_melt_median$Bonanza_Period, n = 1),
      tail(fmsy_data_melt_median$Collapse_Period, n = 1)
    )
  )
}

evaluation_table <- rbind(
  apply(evaluation_table, 2, max),
  rep(0, ncol(evaluation_table)),
  evaluation_table
)

row.names(evaluation_table) <- c("Max", "Min",
                                 "OM+OM FMSY",
                                 "OM+SS3 FMSY", 
                                 "OM+AMO Fadj",
                                 "OM+PDSI Fadj",
                                 "OM+Bass Biomass Fadj",
                                 "OM+CPUE Fadj",
                                 "OM+Mean Age Fadj",
                                 "SS3 EM+SS3 FMSY",
                                 "SS3 EM+AMO Fadj",
                                 "SS3 EM+PDSI Fadj",
                                 "SS3 EM+Bass Biomass Fadj",
                                 "SS3 EM+CPUE Fadj", 
                                 "SS3 EM+Mean Age Fadj")

evaluation_table["Max", c("Bonanza_Period", "Collapse_Period")] <- c(length(projection_year), length(projection_year))
evaluation_table[c("Max", "Min"), c("Collapse_Period")] <- rev(evaluation_table[c("Max", "Min"), c("Collapse_Period")])

case_num <- 5
# jpeg(filename = file.path(figure_path, paste0("radar_mediumF_", terminal_year, ".jpeg")), width = 200, height = 200, units = "mm", res = 1800)
par(mfrow=c(3,3), mar=c(0,0,0,0))
colors <- c("gray", brewer.pal(12,"Paired"))
# colors <- brewer.pal(12,"Paired")

variable_label <- c("Mean Catch", paste0("B", tail(projection_year, n=1), "/K"), paste0("B", tail(projection_year, n=1), "/BMSY"), "Mean Biomass", "Bonanza \n Length", "Minimize \n Collapse \n Length")

for (i in 1:case_num){
  colors_border <- colors[c(1:2, 2+i, case_num+3, case_num+3+i)]
  radarchart(evaluation_table[c(1:4, 4+i, case_num+5, case_num+5+i), ],
             seg=5,
             pcol=colors_border, plwd=2, plty=1,
             axistype = 0, axislabcol="black", 
             paxislabels = round(evaluation_table["Max",],2), palcex = 1,
             vlabels = variable_label, vlcex = 0.8)
  # colors_border <- colors[c(1, 1+i, case_num+2, case_num+2+i)]
  # radarchart(evaluation_table[c(1:3, 3+i, case_num+4, case_num+4+i), ],
  #            seg=5,
  #            pcol=colors_border, plwd=2, plty=1,
  #            axistype = 0, axislabcol="black", 
  #            paxislabels = round(evaluation_table["Max",],2), palcex = 1,
  #            vlabels = variable_label, vlcex = 0.8)
}
colors_border <- colors[c(1:2, (case_num+3):length(colors))]
radarchart(evaluation_table[c(1:4, (case_num+5):nrow(evaluation_table)),],
           seg=5,
           pcol=colors_border, plwd=2 , plty=1,
           axistype = 2, axislabcol="black", 
           paxislabels = round(evaluation_table["Max",],2), palcex = 1,
           vlabels = variable_label, vlcex = 0.8)
colors_border <- colors[1:length(colors)]
plot(1, type = "n", axes=FALSE, xlab="", ylab="")
legend("center", legend = rownames(evaluation_table[-c(1,2),]), bty = "n", pch=20 , col=colors_border, text.col = "black", cex=0.9, pt.cex=3)

format(evaluation_table, digits=3)
```
